### 2016-12-25 Java/java.tex
Adding all folders

\documentclass[a4paper,11pt]{article}

\renewcommand\thesection{\arabic{section}.}

\usepackage{tocloft}
\cftsetindents{section}{0em}{2em}
\cftsetindents{subsection}{0em}{2em}
\renewcommand\cfttoctitlefont{\hfill\Large\bfseries}
\renewcommand\cftaftertoctitle{\hfill\mbox{}}
\setcounter{tocdepth}{2}

\usepackage{listings}
\usepackage{xcolor}

\usepackage{fullpage}

\usepackage{float}

\usepackage{amsfonts}

\usepackage{sectsty}
\sectionfont{\fontsize{14}{15}\selectfont}

\usepackage{graphicx}
\usepackage[margin=0.6in,includefoot,headsep=0.1in]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\cfoot{\thepage}
\rfoot{P. T. O.}
\lfoot{ROHIT DAS 30000114022}

\usepackage{booktabs}
\usepackage{tabularx}

%\usepackage{array}
%\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

\lstset { %
    language=Java,
    backgroundcolor=\color{black!5}, % set backgroundcolor
    basicstyle=\large,% basic font setting
}

\begin{document}
\title{\textbf{\Huge Maulana Abul Kalam Azad University of\\[10pt] Technology}}
\date{\vspace{-5ex}}
\maketitle
\begin{center}
\textbf{\LARGE{(Java Assignment)}}
\end{center}
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/Pictures/makaut.jpg}
\end{figure}
.
\begin{flushright}
\underline{\textbf{\author{\Huge Rohit Das}}}\\
\textbf{\LARGE{
B. Tech(CSE),5th Year\\
Roll No.: 30000114022\\
Regn. No.: 143000110023\\
Taught by: Prof. Kaushik Majumdar/ Prof. Debashis De\\
}}
\end{flushright}
%\tableofcontents
%\begin{table}[htbp]
%\centering
.
\\
\\
\\
\\
\\
\\
\\
\begin{center}
\LARGE\textbf{\underline{INDEX}}
\end{center}

\begin{tabular}{|c|p{0.48\linewidth}|c|c|c|}
\textbf{Sl. No.}&\textbf{Particulars}&\textbf{Date}&\textbf{Page No.}&\textbf{Signature}\\[5pt] \hline
\\1.&Program to calculate average of cricket players.& 28/9/16 & 3 &\\ \hline
\\2.&Program to calculate cost for consumer.& 28/9/16 & 4 &\\ \hline
\\3.&Program to display votes received in election.& 28/9/16 & 5 &\\ \hline
\\4.&Program for operation on array elements.& 19/10/16 & 6 &\\ \hline
\\5.&Program to calculate factorial of a number.& 19/10/16 & 7 &\\ \hline
\\6.&Program to calculate sum of series$1+22+32+42+...$.& 19/10/16 & 7 &\\ \hline
\\7.&Program to add values of Complex no. objects.& 9/11/16 & 8 &\\ \hline
\\8.&Program to convert distances to inches and add.& 28/9/16 & 9 &\\ \hline
\\9.&Program for String class with different costructors.& 9/11/16 & 10 &\\ \hline
\\10.&Program to display unique roll of Student objects.& 9/11/16 & 10 &\\ \hline
11.&Program to swap values of objects using 'friend' function.& 9/11/16 & 11 &\\ \hline
\\12.&Program for operation on matrices.& 16/11/16 & 12 &\\ \hline
13.&Program to use overloaded operators on float numbers.& 16/11/16 & 14 &\\ \hline
\\14.&Program to compare two strings by '==' operator.& 16/11/16 & 15 &\\ \hline
\\15.&Program to implement current and savings a/c.& 23/11/16 & 16 &\\ \hline
\\16.&Previous program rewritten using constructors.& 23/11/16 & 18 &\\ \hline
\\17.&Program for an educational institution.& 23/11/16 & 20 &\\ \hline
\\18.&Program to implement a network.& 23/11/16 & 23 &\\ \hline
\\19.&Program to show overriding using 'virtual'.& 30/11/16 & 24 &\\ \hline
\\20.&Program to implement Shape class using 'virtual'.& 30/11/16 & 25 &\\ \hline
\\21.&Previous program rewritten without using 'virtual'.& 30/11/16 & 26 &\\ \hline
\\22.&Program to use template for an array.& 7/12/16 & 27 &\\ \hline
23.&Program to implement exception handling with multiple catch.& 7/12/16 & 28 &\\ \hline
\\24.&Program to implement rethrowing an exception.& 7/12/16 & 29 &\\ \hline
\\25.&Program to implement a generic vector.& 27/12/16 & 29 &\\ \hline
\end{tabular}
%\end{table}

\section{Write a program to print the patterns below:\\
1. *   2.  * 3.* 4.* 5.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
class Patterns{
	void pattern1(int n){
		for(int i=1;i<=n;i++){
			int j=1;
			while(j<=i){
				System.out.print(" * ");	j++;
			}
			System.out.println();
		}
	}
	void pattern2(int n){
		for(int i=1;i<=n;i++){
			for(int j=n-i;j>=0;j--)System.out.print("   ");
			for(int j=1;j<=i;j++)System.out.print(" * ");
			for(int j=i;j<i;j++)System.out.print(" * ");
			System.out.println();
		}
	}
	void pattern3(int n){
		for(int i=1;i<=n;i++){
			for(int j=n-i;j>=0;j--)System.out.print("   ");
			for(int j=1;j<=i;j++)System.out.print(" * ");
			for(int j=1;j<i;j++)System.out.print(" * ");
			System.out.println();
		}
	}
	void pattern4(int n){	
		for(int i=n;i>0;i--){
			for(int j=n-i;j>=0;j--)System.out.print("   ");
			for(int j=1;j<=i;j++)System.out.print(" * ");
			for(int j=1;j<i;j++)System.out.print(" * ");	
			System.out.println();
		}
	}
	void pattern5(int n){
		for(int i=n-1;i>0;i--){
			for(int j=n-i-1;j>=0;j--)System.out.print(" * ");
			for(int j=1;j<=i;j++)System.out.print("   ");
			for(int j=1;j<i;j++)System.out.print("   ");
			for(int j=n-i-1;j>=0;j--)System.out.print(" * ");
			System.out.println();
		}
		for(int j=1;j<=(2*n-1);j++)System.out.print(" * ");
		System.out.println();
	}
	public static void main(String[]args){
		Patterns obj=new Patterns();
		obj.pattern1(5);	obj.pattern2(5);
		obj.pattern3(5);	obj.pattern5(5);
		obj.pattern4(5);
	}
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/java_files/9-27/Patterns.png}
\end{figure}

\section{Write a program to print all prime numbers between 1 and 100.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
class Prime{
	boolean isPrime(int n){
		int d=n/2;
		if(n==0 || n==1)return false;
		for(int i=2;i<=d;i++)	if(n%i==0)   return false;
		return true;
	}
	public static void main(String[]args){
		Prime obj=new Prime();
		System.out.println("The prime nos are:");
		for(int i=1;i<=100;i++)if(obj.isPrime(i))
			System.out.print(i+" ");
		System.out.println();
	}
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=200pt,height=\textheight,keepaspectratio]{/home/mouri/java_files/9-27/Prime.png}
\end{figure}
.

\section{Write a program to print the reverse of a number.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
class Reverse{
	int rev(int n){
		int s=0;
		while(n!=0){
			int r=n%10;
			s=s*10+r;
			n/=10;
		}
		return s;
	}
	public static void main(String[]args){
		Reverse obj=new Reverse();
		System.out.println("The reverse of 1234567 is:");
		System.out.println(obj.rev(1234567));
	}
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/java_files/9-27/Reverse.png}
\end{figure}
.

\section{Write a program to print the sum of digits of a number.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
class SumOfDigits{
	int sum(int n){
		int sum=0;
		while(n!=0){
			int r=n%10;
			sum+=r;
			n/=10;
		}
		return sum;
	}
	public static void main(String[]args){
		SumOfDigits obj=new SumOfDigits();
		System.out.println("The sum of digits for 1234567 is::");
		System.out.println(obj.sum(1234567));
	}
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/java_files/9-27/SumOfDigits.png}
\end{figure}
.

\section{Write a program to calculate the area of a circle, square, rectangle and triangle using function overloading.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
import java.util.*;
class Area1{
	private float area(float l,float b){
		return l*b;
	}
	private double area(double p,double base){
		return ((1/2.0)*base*p);
	}	
	private double area(double r){
		return (Math.PI*r*r);
	}	
	private float area(float a){
		return a*a;
	}
	public static void main(String[]args){
		Area1 obj=new Area1();
		Scanner sc=new Scanner(System.in);
		double p,base,r;
		float l,b,a;
		System.out.println("Enter sides of rectangle:");
		l=sc.nextFloat();
		b=sc.nextFloat();
		System.out.println("Area of rectangle is "+
		obj.area(l,b));
		System.out.println("Enter base and height of triangle:");
		p=sc.nextDouble();
		base=sc.nextDouble();
		System.out.println("Area of triangle is "+
		obj.area(p,base));
		System.out.println("Enter radius of circle:");
		r=sc.nextDouble();
		System.out.println("Area of circle is "+obj.area(r));
		System.out.println("Enter side of square:");
		a=sc.nextFloat();
		System.out.println("Area of square is "+obj.area(a));
	}
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/java_files/10-18/Area1.png}
\end{figure}
.

\section{Write the previous program using constructor overloading.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
import java.util.*;
class Area2{
	static Scanner sc=new Scanner(System.in);
	static double p,base,r;
	static float l,b,a;
	Area2(float l,float b){	this.l=l;  this.b=b; }
	Area2(float a){	this.a=a; }
	Area2(double p,double base){	this.p=p; this.base=base; }
	Area2(double r){	this.r=r;	}
	private double area1(){	return l*b;	}
	private double area2(){	return a*a;	}
	private double area3(){	return (1/2.0)*base*p;	}
	private double area4(){	return Math.PI*r*r;	}
	public static void main(String[]args){
		System.out.println("Enter sides of rectangle:");
		l=sc.nextFloat();	b=sc.nextFloat();
		Area2 obj1=new Area2(l,b);
		System.out.println("Area of rectangle is "+obj1.area1());
		System.out.println("Enter sides of square:");
		a=sc.nextFloat();
		Area2 obj2=new Area2(a);
		System.out.println("Area of square is "+obj2.area2());
		System.out.println("Enter sides of triangle:");
		p=sc.nextDouble();	base=sc.nextDouble();
		Area2 obj3=new Area2(p,base);
		System.out.println("Area of triangle is "+obj3.area3());
		System.out.println("Enter radius of circle:");
		r=sc.nextDouble();
		Area2 obj4=new Area2(r);
		System.out.println("Area of circle is "+obj4.area4());
	}
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/java_files/10-18/Area2.png}
\end{figure}
.

\section{Write a program to design a class representing a bank account. The class should have the following data members:\\$*$ a/c no.	$*$ customer id	$*$ balance amount\\The class should have member methods with the following functions:\\$*$  initialize initial value\\$*$  to deposit amount\\$*$  to withdraw amount\\$*$  to display customer id, a/c no. and current balance.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
import java.util.*;
class Bank{
	static Scanner sc=new Scanner(System.in);
	static long acno;	static double amt;
	static String id;
	private void init(){  acno=0;	amt=0.0;  id="";  }
	private double deposit(double d){  return amt+=d;  }
	private double withdraw(double d)
	{
		if(d<amt&&amt!=0)return amt-=d;
		else {
		    System.out.println("Not Enough Balance!!");
		    return amt;
		}
	}
	private void print(){
		System.out.println("Customer ID \t A/c No. \t Current 
		Balance");
		System.out.println(id+"\t \t "+acno+"\t \t "+amt);
	}
	public static void main(String[]args){
		Bank obj=new Bank();
		obj.init();
		System.out.println("Enter account no and current balance
		:");
		id="3000114022";
		acno=sc.nextLong();  amt=sc.nextDouble();
		double d=0.0;	int choice=0;
		do{
			System.out.println("Main Menu");
			System.out.println("0. Deposit");
			System.out.println("1. Withdrawal");
			System.out.println("2. Print Statement");
			System.out.println("3. Exit");
			System.out.println("Enter choice:");
			choice=sc.nextInt();
			switch(choice){
			case 0:d=0.0;
				System.out.println("Enter amount to 
				deposit:");
		       		d=sc.nextDouble();
		       		System.out.println("The deposit is "+d+
		       		". The current balance is "+
			        (double)obj.deposit(d));
				break;
			case 1:d=0.0;
				System.out.println("Enter amount to
				 withdraw:");
				d=sc.nextDouble();
				System.out.println("The withdrawal is 
				"+d+". The current balance is "+
				(double)obj.withdraw(d));
	  		        break;
			case 2:obj.print();
				break;
			default:System.out.println("Thank you");
				break;		
			}
		}while(choice<3);
	}
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/java_files/10-18/Bank.png}
\end{figure}
.

\section{Write a program to add two complex numbers. Print the result in $(x+iy)$ form. Use objects as arguments to a method which will perform the addition and use function overloading.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
class Complex{
    double x;   int y;
    Complex(double a,int b){
    	x=a;	y=b;
    }
    void print(){  System.out.println(x+"+ i"+y);  }	
}
class Test
{
    double real;    int imag;
    private double sum(double a,double b){
        real=a+b;	   return real;
    }
    private int sum(int a,int b){
    	imag=a+b;   return imag;
    }
    public static void main(String[]args){
    	Complex obj=new Complex(4,6);
    	obj.print();
    	Complex obj1=new Complex(1,9);
    	obj1.print();
    	Test t1=new Test();
	System.out.println("The sum is: "+t1.sum(obj.x,obj1.x)+"+ i"+
	t1.sum(obj.y,obj1.y));
    }
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/java_files/10-18/Complex.png}
\end{figure}
.

\section{Write a program to design a class Student. The class should have the following data members:\\ $*$ name    $*$ roll		$*$ sub-marks	$*$ sports-marks	$*$ grades.\\The class should have the following functions:\\$*$ initialize values for data members,\\$*$ calculate total marks,\\$*$ display total marks\\$*$ display grade}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
import java.util.*;
class Student{
	private static String name;
	private static long roll;
	private static int submarks,sportsmarks;
	private void init(){
		roll=submarks=sportsmarks=0;
		name="";
	}
	private long total(){	return submarks+sportsmarks;	}
	private void print(){
		System.out.println("Subject Marks: "+submarks+" out of 
		50.");
		System.out.println("Sports Marks: "+sportsmarks+" out of 
		50.");
		System.out.println("Total Marks: "+(submarks+sportsmarks)
		+" out of 100.");
	}
	private char grade(){
		long total=submarks+sportsmarks;
		if(total>90)return 'A';
		else if(total<=90 && total >=80)return 'B';
		else if(total<80 && total>=70)return 'C';
		else return 'D';
	}
	public static void main(String[]args){
		Scanner sc=new Scanner(System.in);
		Student obj=new Student();  obj.init();
		System.out.println("Enter name of student:");
		name=sc.nextLine();
		System.out.println("Enter roll no., subject marks(out of 
		50) and sports marks(out of 50):");
		roll=sc.nextLong();	submarks=sc.nextInt();
		sportsmarks=sc.nextInt();
		System.out.println("The total is "+obj.total());
		System.out.println("The grade of the student is: "+
		obj.grade());
	}
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-9/string.png}
\end{figure}
.
\section{Write a program to create a student class and create 10 objects and display the roll no. of the students. Use static data member and array to create objects. Do not use constructors.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
using namespace std;
class Student{
	int roll;
	public:	
		static int count;
		Student(){}
		void init(){	roll=++count;		}
		void display(){	printf("%d ",roll);	}
};
int Student::count;
int main(){
	Student arr[10];
	for(int i=0;i<10;i++){
		int x=Student::count;
		arr[i].init();
	}
	printf("The rolls are: \n");
	for(int i=0;i<10;i++){
		printf("Student %d: ",i);
		arr[i].display();
		printf("\n");
	}
	return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-9/student.png}
\end{figure}
.

\section{Write a program to values of objects using 'friend' functions.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
using namespace std;
class Swap
{
	int n;
	public:	
		Swap(){}
		Swap(int n){	this->n=n;	}
		void show(){	printf("%d \n",n);	}
		friend void swap(Swap,Swap);
};
class Swap2{
	public:
		friend void swap(Swap a,Swap b){
			Swap temp;
			printf("\na=");	a.show();
			printf("\nb=");	b.show();
			printf("\nAfter swap:\n");
			temp.n=a.n;  a.n=b.n;  b.n=temp.n;
			printf("\na=");	a.show();
			printf("\nb=");	b.show();
		}

};
int main(){
	Swap a(10);	Swap b(20);
	Swap2 s;	swap(a,b);
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-9/swap.png}
\end{figure}
.

\section{Write a program to create a class Matrix of size m x n. Define all possible matrix operations for Matrix type objects.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
using namespace std;
class Matrix{
	int r,c;
	public:
	int a[100][100];
	Matrix(){}
	Matrix(int row,int col){	r=row;c=col;	}
	Matrix operator+(Matrix);
	Matrix operator-(Matrix);
	Matrix operator*(Matrix);
	void input(void);
	void display(void);
};
Matrix Matrix::operator+(Matrix c){
	Matrix temp(2,2);
	for(int i=0;i<c.r;i++){
		for(int j=0;j<c.c;j++){
			temp.a[i][j]=a[i][j]+c.a[i][j];	
		}	
	}
	return (temp);
}
Matrix Matrix::operator-(Matrix c){
	Matrix temp(2,2);
	for(int i=0;i<c.r;i++){
		for(int j=0;j<c.c;j++){
			temp.a[i][j]=a[i][j]-c.a[i][j];	
		}	
	}
	return (temp);
}
Matrix Matrix::operator*(Matrix c){
	Matrix temp(2,2);
	for(int i=0;i<r;i++){
		for(int j=0;j<c.c;j++){
			for(int k=0;k<c.r;k++){
				temp.a[i][j]=a[i][k]*c.a[k][j];
			}
		}	
	}
	return (temp);
}
void Matrix::input(void){
	printf("Enter data for matrix(%d x %d):",r,c);
	for(int i=0;i<r;i++){
		for(int j=0;j<c;j++){
			scanf("%d",&a[i][j]);
		}
	}
}
void Matrix::display(void){
	printf("The data for matrix \n");
	for(int i=0;i<r;i++){
		for(int j=0;j<c;j++)printf("%d ",a[i][j]);
		printf("\n");
	}
}
int main(){
	Matrix m1,m2,m3;
	m1=Matrix(2,2);	m1.input();
	m2=Matrix(2,2);	m2.input();
	m3=m1+m2;
	printf("Matrix 1=");	m1.display();
	printf("Matrix 2=");	m2.display();
	cout<<"Sum is:"<<endl;
	printf("Matrix 3=");	m3.display();
	m3=m1-m2;
	cout<<"DIfference is:"<<endl;
	printf("Matrix 3=");	m3.display();
	m3=m1*m2;
	cout<<"Product is:"<<endl;
	printf("Matrix 3=");	m3.display();
	return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-16/matrix.png}
\end{figure}
.

\section{Write a program to create a class FLOAT that contains one float data member. Overload all the four arithmetic operators so that they operate on the objects of FLOAT.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
using namespace std;
class Float{
	float x;
	public:
		Float(){}
		Float(float a){	x=a;	}
		Float operator+(Float);
		Float operator-(Float);
		Float operator*(Float);
		Float operator/(Float);
		void display(void);
};
Float Float::operator+(Float c){	return Float(x+c.x);	}
Float Float::operator-(Float c){	return Float(x-c.x);	}
Float Float::operator*(Float c){	return Float(x*c.x);	}
Float Float::operator/(Float c){	return Float(x/c.x);	}
void Float::display(void){	printf("%f \n",x);	}
int main(){
	Float f1,f2,f3;
	f1=Float(1.5);	f2=Float(2.5);
	f3=f1+f2;
	printf("f1=");	f1.display();
	printf("f2=");	f2.display();
	cout<<"Sum is:"<<endl;
	printf("f3=");	f3.display();
	cout<<"Difference is:"<<endl;
	f3=f1-f2;
	printf("f3=");	f3.display();
	cout<<"Product is:"<<endl;
	f3=f1*f2;	
	printf("f3=");	f3.display();
	cout<<"Quotient is:"<<endl;
	f3=f1/f2;
	printf("f3=");	f3.display();
	return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-16/opload1.png}
\end{figure}
.

\section{Write a program to compare two strings by overloading the '==' operator.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
#include<string>
using namespace std;
class String{
	string s;
	public:
	String(){	s="";	}
	String(string _s){	s=_s;	}
	string operator==(String);
};
string String::operator==(String str){
	if(s==str.s)return "Equals\n";
	else return "Not equals\n";
}
int main(){
	String s1("Hello"),s2("Hola"),s3("Hello");
	cout<<"Comparing Hello and Hola:"<<endl;
	cout<<(s1==s2);
	cout<<"Comparing Hello and Hello:"<<endl;
	cout<<(s1==s3);
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-16/string.png}
\end{figure}
.

\section{Write a program to create a class account that stores customer name, account number and type of account. Create two more classes for current a/c and savings a/c. The current a/c will have:\\$*$ cheque facility, \\$*$ minimum balance and deduction for balance below that,\\$*$ deposit and withdrawal. The saving a/c will have similar member methods, except for cheque and minimum balance, it will have an interest calculation. Do not use constructors.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
#include<string>
#include<stdlib.h>
#include<cmath>
#define ll long long int
using namespace std;
class Account{
    string customer_name,acct_type;
    ll acct;
};
class Cur_acct:public Account{
    double balance,minBal;
    public:
	void setbal(double a,double b)	{
	    balance=a;
	    minBal=b;
	}
	void withdrawal(int n)	{
	    if(balance<minBal)balance-=(balance*0.10);
	    else if(n>balance)printf("Insufficient balance.\n");
	    else balance-=n;
	}
	void deposit(int n){    balance+=n;	}
	void cheque(){ cout<<"Deposited by cheque..."<<endl;	}
	void show(){
	    printf("Current balance=%.2f\n",balance);
	}
};
class Sav_acct:public Account{
    double balance;
    public:
	void setbal(double a){    balance=a;	}
	void withdrawal(int n){
	    if(n>balance)printf("Insufficient balance.\n");
	    else balance-=n;
	}
	void deposit(int n){    balance+=n;	}
	void interest(){    balance+=(balance*0.20);	}
	void show(){
	    printf("Current balance:%.2f\n",balance);
	}
};
int main(){
    cout<<"Enter type of account(s for savings, c for current):"<<endl;
    char c;    cin>>c;
    cout<<"Enter balance:"<<endl;
    int bal;    cin>>bal;
    if(c=='c'){
		cout<<"Enter minimum balance:"<<endl;
		int minbal;	cin>>minbal;
		Cur_acct c1;
		c1.setbal(bal,minbal);
		cout<<"Enter amount to deposit:"<<endl;
		int n;	cin>>n;
		cout<<"Do you want to use cheque or cash?(c for cheque)..
		"<<endl;
		char c;	cin>>c;
		if(c=='c')c1.cheque();
		c1.deposit(n);	cout<<"Deposited: Rs."<<n<<"\n";
		c1.show();
		cout<<"Enter amount to withdraw:"<<endl;
		cin>>n;	c1.withdrawal(n);
		cout<<"Withdrawal: Rs."<<n<<"\n";	c1.show();
		cout<<"Enter amount to withdraw:"<<endl;
		cin>>n;	c1.withdrawal(n);
		cout<<"Withdrawal: Rs."<<n<<"\n";	c1.show();
   	 }
    else{
		Sav_acct s1;
		s1.setbal(bal);
		cout<<"Enter amount to deposit:"<<endl;
		int n;	cin>>n;
		s1.deposit(n);
		cout<<"Deposited: Rs."<<n<<"\n";	s1.show();
		cout<<"Enter amount to withdraw:"<<endl;
        cin>>n;	s1.withdrawal(n);
		cout<<"Withdrawal: Rs."<<n<<"\n";
		s1.show();
    	cout<<"Enter amount to withdraw:"<<endl;
        cin>>n;	s1.withdrawal(n);
		cout<<"Withdrawal: Rs."<<n<<"\n";	s1.show();
		cout<<"Adding interest of 0.20 to current balance:"
		<<endl;
		s1.interest();	s1.show();
    }
    return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=250pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-23/bank.png}
\includegraphics[width=250pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-23/bank2.png}
\end{figure}
.

\section{Rewrite the above program using constructors.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
#include<string>
#include<stdlib.h>
#include<cmath>
#define ll long long int
using namespace std;
using namespace std;
class Account{
    string customer_name,acct_type;
    ll acct;
    public:
    Account(){}
    Account(string a,string b,ll c){
	customer_name=a;
	acct_type=b;
	acct=c;
    }
};
class Cur_acct:public Account{
    double balance,minBal;
    public:
	Cur_acct(double a,double b){
	    balance=a;
	    minBal=b;
	}
	void withdrawal(int n){
	    if(balance<minBal)balance-=(balance*0.10);
	    else if(n>balance)printf("Insufficient balance.\n");
	    else balance-=n;
	}
	void deposit(int n){    balance+=n;	}
	void cheque(){
	    cout<<"Deposited by cheque..."<<endl;
	}
	void show(){
	    printf("Current balance=%.2f\n",balance);
	}
};
class Sav_acct:public Account
{
    double balance;
    public:
	Sav_acct(int a){    balance=a;	}
	void withdrawal(int n){
	    if(n>balance)printf("Insufficient balance.\n");
	    else balance-=n;
	}
	void deposit(int n){    balance+=n;	}
	void interest(){    balance+=(balance*0.20);	}
	void show(){
	    printf("Current balance:%.2f\n",balance);
	}
};
int main(){
    cout<<"Enter type of account(s for savings, c for current):"<<endl;
    char c;    cin>>c;
    cout<<"Enter balance:"<<endl;
    int bal;    cin>>bal;
    if(c=='c'){
	cout<<"Enter minimum balance:"<<endl;
	int minbal;	cin>>minbal;
	Cur_acct c1(bal,minbal);
	cout<<"Enter amount to deposit:"<<endl;
	int n;	cin>>n;
	cout<<"Do you want to use cheque or cash?(c for cheque).."<<endl;
	char c;	cin>>c;
	if(c=='c')c1.cheque();
	c1.deposit(n);
	cout<<"Deposited: Rs."<<n<<"\n";	c1.show();
	cout<<"Enter amount to withdraw:"<<endl;
	cin>>n;	c1.withdrawal(n);
	cout<<"Withdrawal: Rs."<<n<<"\n";
	c1.show();
	cout<<"Enter amount to withdraw:"<<endl;	cin>>n;
	c1.withdrawal(n);
	cout<<"Withdrawal: Rs."<<n<<"\n";	c1.show();
    }
    else{
	Sav_acct s1(bal);
	cout<<"Enter amount to deposit:"<<endl;
	int n;	cin>>n;
	s1.deposit(n);
	cout<<"Deposited: Rs."<<n<<"\n";	s1.show();
	cout<<"Enter amount to withdraw:"<<endl;
    cin>>n;	s1.withdrawal(n);
	cout<<"Withdrawal: Rs."<<n<<"\n";
	s1.show();
	cout<<"Enter amount to withdraw:"<<endl;	cin>>n;
	s1.withdrawal(n);
	cout<<"Withdrawal: Rs."<<n<<"\n";	s1.show();	
	cout<<"Adding interest of 0.20 to current balance:"<<endl;
	s1.interest();	s1.show();
    }
    return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=250pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-23/bank.png}
\includegraphics[width=250pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-23/bank2.png}
\end{figure}
.

\section{ An educational institution wishes to maintain a database of its employees. The database is divided into a number of classes whose hierarchical relationships are shown in figure below. The figure also shows the minimum information required for each class. Specify all the classes and define functions to create the database and retrieve individual information as and when required.}
\begin{figure}[H]
\centering
\includegraphics[width=220pt,height=\textheight,keepaspectratio]{/home/mouri/Pictures/educate.png}
\end{figure}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
#include<string>
#include<stdlib.h>
#include<cmath>
#define ll long long int
using namespace std;
using namespace std;
class Account{
    string customer_name,acct_type;
    ll acct;
    public:
    Account(){}
    Account(string a,string b,ll c){
	customer_name=a;
	acct_type=b;
	acct=c;
    }
};
class Cur_acct:public Account{
    double balance,minBal;
    public:
	Cur_acct(double a,double b){
	    balance=a;
	    minBal=b;
	}
	void withdrawal(int n){
	    if(balance<minBal)balance-=(balance*0.10);
	    else if(n>balance)printf("Insufficient balance.\n");
	    else balance-=n;
	}
	void deposit(int n){    balance+=n;	}
	void cheque(){
	    cout<<"Deposited by cheque..."<<endl;
	}
	void show(){
	    printf("Current balance=%.2f\n",balance);
	}
};
class Sav_acct:public Account
{
    double balance;
    public:
	Sav_acct(int a){    balance=a;	}
	void withdrawal(int n){
	    if(n>balance)printf("Insufficient balance.\n");
	    else balance-=n;
	}
	void deposit(int n){    balance+=n;	}
	void interest(){    balance+=(balance*0.20);	}
	void show(){
	    printf("Current balance:%.2f\n",balance);
	}
};
int main(){
    cout<<"Enter type of account(s for savings, c for current):"<<endl;
    char c;    cin>>c;
    cout<<"Enter balance:"<<endl;
    int bal;    cin>>bal;
    if(c=='c'){
	cout<<"Enter minimum balance:"<<endl;
	int minbal;	cin>>minbal;
	Cur_acct c1(bal,minbal);
	cout<<"Enter amount to deposit:"<<endl;
	int n;	cin>>n;
	cout<<"Do you want to use cheque or cash?(c for cheque).."<<endl;
	char c;	cin>>c;
	if(c=='c')c1.cheque();
	c1.deposit(n);
	cout<<"Deposited: Rs."<<n<<"\n";	c1.show();
	cout<<"Enter amount to withdraw:"<<endl;
	cin>>n;	c1.withdrawal(n);
	cout<<"Withdrawal: Rs."<<n<<"\n";
	c1.show();
	cout<<"Enter amount to withdraw:"<<endl;	cin>>n;
	c1.withdrawal(n);
	cout<<"Withdrawal: Rs."<<n<<"\n";	c1.show();
    }
    else{
	Sav_acct s1(bal);
	cout<<"Enter amount to deposit:"<<endl;
	int n;	cin>>n;
	s1.deposit(n);
	cout<<"Deposited: Rs."<<n<<"\n";	s1.show();
	cout<<"Enter amount to withdraw:"<<endl;
    cin>>n;	s1.withdrawal(n);
	cout<<"Withdrawal: Rs."<<n<<"\n";
	s1.show();
	cout<<"Enter amount to withdraw:"<<endl;	cin>>n;
	s1.withdrawal(n);
	cout<<"Withdrawal: Rs."<<n<<"\n";	s1.show();	
	cout<<"Adding interest of 0.20 to current balance:"<<endl;
	s1.interest();	s1.show();
    }
    return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-23/educate.png}
\end{figure}
.

\section{Consider a class network as shown below. Define all four classes and write a program to create, update and display the information contained in master objects.}
\begin{figure}[H]
\centering
\includegraphics[width=240pt,height=\textheight,keepaspectratio]{/home/mouri/Pictures/network.png}
\end{figure}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
#include<string>
#include<stdlib.h>
#include<cmath>
#define ll long long int
using namespace std;
class Person{
    public:
    string name,code;
    void init(string a,string b){
	name=a;	code=b;
    }
    virtual void display()=0;
};
class Account:virtual public Person{
    public:
    int pay;
    void init1(string a,string b,int c){
	init(a,b);	pay=c;
    }
    void display(){
	cout<<"Name= "<<name<<endl;	cout<<"Code= "<<code<<endl;
	cout<<"Pay= "<<pay<<endl;
    }
};
class Admin:virtual public Person{
    public:
    string exp;
    void init2(string a,string b,string c){
	init(a,b);	exp=c;
    }
    void display(){
	cout<<"Name= "<<name<<endl;	cout<<"Code= "<<code<<endl;
	cout<<"Experience= "<<exp<<endl;
    }
};
class Master:public Account,public Admin{
    public:
    void init3(string a,string b,string c,int d){
	init1(a,b,d);	init2(a,b,c);
    }
    void display(){
	cout<<"Name= "<<name<<endl;	cout<<"Code= "<<code<<endl;
	cout<<"Experience= "<<exp<<endl;  cout<<"Pay= "<<pay<<endl;
    }
};
int main(){
    Master p;
    p.init3("A","0001","2 years",10000);    p.display();
    return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-23/network.png}
\end{figure}
.

\section{Write a program demonstrating overriding using 'virtual'.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
#include<string>
#include<stdlib.h>
#include<cmath>
#define ll long long int
using namespace std;
class Base{
    public:
	void display(){    cout<<"Display Base"<<endl;	}
	virtual void show(){    cout<<"Show Base"<<endl;	}
};
class Derived:public Base{
    public:
	void display(){    cout<<"Display Derived"<<endl;	}
	void show(){    cout<<"Show Derived"<<endl;	}
};
int main(){
    Base b;
    Derived d;    Base *bptr;
    bptr=&b;
    bptr->display();    bptr->show();
    bptr=&d;
    bptr->display();    bptr->show();
    return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-30/poly.png}
\end{figure}
.

\section{Write a program implementing Shape class, from which Triangle and Rectangle inherit. Use 'virtual'}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
#include<string>
#include<stdlib.h>
#include<cmath>
#define ll long long int
using namespace std;
class Shape{
    public:
    double l,b;
    void getData(double _l,double _b){
	l=_l;	b=_b;
    }
    virtual void display(){
	cout<<"Area ="<<(l*b)<<"\n";
    }
};
class Triangle:public Shape{
    public:
    void display(){
	cout<<"Area of triangle="<<(0.5*b*l)<<"\n";
    }
};
class Rectangle:public Shape{
    public:
    void display(){
		cout<<"Area of triangle="<<(l*b)<<"\n";
    }
};
class Circle:public Shape{
    public:
    void getData(int _l,int _b=0){
	l=_l;	b=_b;
    }
    void display(){
	cout<<"Area of circle="<<(3.1412*l*l)<<"\n";
  	}
};
int main()
{
    Triangle t;	Rectangle r;
    Circle c;
    double l,b;
    t.getData(4,5);	t.display();
    r.getData(4,5);	r.display();
    c.getData(5);	c.display();
    return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-30/shape2.png}
\end{figure}
.

\section{Rewrite the previous program without using 'virtual'.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
#include<string>
#include<stdlib.h>
#include<cmath>
#define ll long long int
using namespace std;
class Shape{
    public:
    double l,b;
    void getData(double _l,double _b){
	l=_l;	b=_b;
    }
    void display(){
	cout<<"Area ="<<(l*b)<<"\n";
    }
};
class Triangle:public Shape{
    public:
    void display(){
	cout<<"Area of triangle="<<(0.5*b*l)<<"\n";
    }
};
class Rectangle:public Shape{
    public:
    void display(){
	cout<<"Area of rectangle="<<(l*b)<<"\n";
    }
};
class Circle:public Shape{
    public:
    void getData(int _l,int _b=0){
	l=_l;	b=_b;
    }
};
int main()
{
    Triangle t;	Rectangle r;
    Circle c;
    t.getData(4,5);	t.display();
    r.getData(4,5);	r.display();
    c.getData(5);	c.display();
    return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/11-30/shape3.png}
\end{figure}
.

\section{Write a function template for finding the minimum value contained in an array.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
#include<string>
#include<stdlib.h>
#include<cmath>
#define ll long long int
using namespace std;
template<class R>
R minimum(R a[],int n){
    R m;    m=a[0];
    for(int i=1;i<3;i++)if(m>a[i])m=a[i];
    return m;
}
int main(){
    int x[3]={10,21,3};
    cout<<minimum(x,3)<<"\n";
    return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/12-7/min.png}
\end{figure}
.

\section{Write a program containing a possible exception. Perform exception handling with multiple catch.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
#include<string>
#include<stdlib.h>
#include<cmath>
#define ll long long int
using namespace std;
void excp(){
    int x=4;    int y=4;
    if(x==y)throw(x-y);
    else cout<<"Its fine"<<endl;
}
int main(){
    try{	excp();    }
    catch(int i){
	cout<<"Both are equal."<<endl;
    }
    catch(char c){
	cout<<"Character is found."<<endl;
    }
    return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/12-7/multcatch.png}
\end{figure}
.
\\
\section{Write a program to demonstrate the concept of rethrowing an exception.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
#include<string>
#include<stdlib.h>
#include<cmath>
#define ll long long int
using namespace std;
void excp1(){
    int x=9;    int y=7;
    if(x-y==2)throw('A');
    else cout<<"Its fine."<<endl;
}
int main(){
    try{	excp1();    }
    catch(char c){
	if(c=='B')cout<<"The diff is 2."<<endl;
	else throw;
    }
    return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/12-7/rethrow.png}
\end{figure}
.

\section{Write a class template to represent a generic vector. Include member functions to perform the following taks:\\$*$ to create a vector\\$*$ to modify the value of a given element\\$*$ to multiply by a scalar.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
#include<iostream>
#include<cstdio>
#include<string>
#include<stdlib.h>
#include<cmath>
#define ll long long int
using namespace std;
template<class T>
class vector
{
    T *v;
    public:
	void init(int size){
	    v=new int[size];
	    cout<<"Enter values"<<endl;
	    for(int i=0;i<size;i++)cin>>v[i];
	}
	T multiply(vector &a,vector &b){
	    T sum=0;
	    for(int i=0;i<3;i++)sum+=a.v[i]*b.v[i];
	    return sum;
	}
};
int main(){
    vector<int> v1;	vector<int> v2;
    vector<int> v;
    cout<<"Enter 3 values for v1:"<<endl;	v1.init(3);
    cout<<"Enter 3 values for v2:"<<endl;	v2.init(3);
    cout<<"Product="<<v.multiply(v1,v2)<<"\n";
    return 0;
}
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/c++-files/12-7/vect.png}
\end{figure}
.

\end{document}

### 2016-12-25 Letters/Letter1.tex
Adding all folders

\documentclass[11pt]{article}

%\usepackage{fullpage}
\usepackage[top=5cm, bottom=1cm, left=2.5cm, right=2.5cm]{geometry}

\begin{document}
\begin{Large}

\begin{flushleft}
The Manager,\\
State Bank of India,\\
Serampore Branch,\\
Serampore,\\
Hooghly-712201.\\
\bigbreak
Dear Sir,\\
\end{flushleft}
\begin{center}
\underline{Sub:Request to marry your daughter.}
\end{center}

%\justify
This is to inform you that, I, Rohit Das, of 108, Netaji Subhas Avenue, Serampore, Hooghly-712201, would like to marry your daughter.\\
\newline
\ \ \ We have been in a romantic relationship for the last 5 years, and now that I am earning for myself, I would like to take the responsibility of happiness and well-being of your elder daughter, Ms. Sukanya Saha. I am earning a decent amount of Rs. 7lpa at a reputed company, the likes of which your daughter can describe to you.
\ \ \

\end{Large} 
\end{document}

### 2017-03-23 Project Proposal/Proposal.tex
Draft 2

\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}

\usepackage{booktabs}
\usepackage{tabu}
\usepackage[T1]{fontenc}

%For bullets
\usepackage{tikz}

\newcommand{\colouredcircle}{%
\tikz{\useasboundingbox (-0.2em,-0.32em) rectangle(0.2em,0.32em);
    \draw[ball color=blue,shading=ball,line width=0.03em] (0,0) circle(0.18em);}}
\renewcommand{\labelitemi}{\colouredcircle}

%% Sets page size and margins
\usepackage[a4paper,includefoot,top=1.5cm,bottom=0.5cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
%\usepackage{apacite}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

%For footer
\textheight=10in
\footskip=25pt
\usepackage{fancyhdr}
\fancyhf{}
\fancypagestyle{plain}{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{GSoC LibreOffice 2017}
\cfoot{--\thepage--}
\pagestyle{fancy}

%Have bulleted subsections
\makeatletter
\newcommand{\heading}[1]% #1 = text
{\par\vskip 1.5ex \@plus .2ex
 \hangindent=1em
 \noindent\makebox[1em][l]{$\,\bullet$}\textbf{\large #1}%
\par\vskip 1.5ex \@plus .2ex
\@afterheading}
\makeatother

\usepackage{xspace}
\newcommand\nth{\textsuperscript{th}\xspace}%shortening nth
\newcommand\nrd{\textsuperscript{rd}\xspace}

{\title{\textbf{Debugging LibreOffice for Android}}
\author{ Difficulty:Medium\\\\\large{Rohit Das} \\ Freenode IRC nick: rohit\\+918961452125 | rohit.das950@gmail.com\\ Serampore, Hooghly, West Bengal, India. GMT+5:30}
\date{}

\parindent30pt
\setlength{\parindent}{20pt}
%\setlength{\parskip}{1em}
%\renewcommand{\baselinestretch}{1.5}

\begin{document}
\maketitle
\Large{\section*{Overview}
%\input{paper}

\hspace{20pt}\textbf{LibreOffice}, a free and open-source office suite, a project of \textbf{The Document Foundation}, has been succesfully working since 2011 to make word-processing and other related jobs free and feasible. By 2015, LibreOffice had released its Android version with basic editing capabilities. Developers around the world contribute to this organisation and its endeavours to keep making it better for users of all fields, with all kinds of purposes.

I believe in what LibreOffice stands for and would like to offer a helping hand for improving open-source word processors to the best of my capabilities.

\section*{Project Goals}

\hspace{20pt}By the end of the time period for GSoC(Google Summer of Code), I intend to make an effort and be successful in debugging some of the most annoying bugs LibreOffice for Android(bug $84726$, as listed \href{https://bugs.documentfoundation.org/showdependencytree.cgi?id=84726}{here}). Some of the bugs mentioned here, which I am especially interested in, are:
\begin{description}
\item[$\bullet$ Bug $106318$]: Android: optimize the UI for tablets.
\item[$\bullet$ Bug $106326$]:  Android: Change font / background color.
\item[$\bullet$ Bug \hspace{5pt}$88389$]: Android document browser: there is no way to access external storage.
\end{description}

\section*{Mentors}
Miklos Vajna, IRC: vmiklos mail: vmiklos @ collabora.co.uk\\
Tomaž Vajngerl, IRC: quikee mail: tomaz.vajngerl @ collabora.co.uk

\section*{EasyHacks}

\section*{Implementation}
\hspace{20pt} Having used Android Studio to a certain extent for most of my Android apps, I will be much more flexible in debugging LibreOffice for Android in the same. Below is the timeline which I am presenting to show how I will divide my work along with my studies:
\heading{Timeline}
\hspace{20pt}\textbf{5\nth May, 2017 - 15\nth May,2017 :-}
\begin{itemize}
\item Speak to mentors and chalk out a path of progress,
\item Acquaint myself with the code and make a rough sketch of where the bugs might be, and
\item Set up my devices and software for debugging.\\\\
\end{itemize}}

\textbf{16\nth May, 2017 - 15\nth July, 2017 :-}
\begin{itemize}
\item Work on the bugs and take occasional help from mentors,
\item Submit patches and fixes for evaluation, 
\item Take reviews from mentors and work accordingly.\\\\
\end{itemize}

\textbf{16\nth July, 2017 - 15\nth August, 2017 :-}
\begin{itemize}
\item Go through other unresolved bugs and work on them,
\item Submit patches and fixes for reviews,\\
\end{itemize}

\section*{Shortcomings}
\hspace{20pt} Since I am currently studying in college, I will be able to commit 2-3 hours of my time on weekdays and 6-7 hours on weekends. Also, I will be having my exams during June-July(exact dates may vary), so I might slow a bit.

\section*{About Me}
\hspace{20pt}I am currently in my 3\nrd year pursuing B. Tech in Computer Science and Engineering from Maulana Abul Kalam Azad University of Technology, West Bengal. You can chck out my blog \href{https://mouri11.github.io/}{here}(work under progress). Check out my projects \href{https://github.com/mouri11}{here}.
\bibliographystyle{plain}
\bibliography{refs}
\end{document}

### 2017-05-27 SQL/SQL.tex
Modified SQL.tex
Signed-off-by: mouri11 <rohit.das950@gmail.com>

\documentclass[a4paper,11pt]{article}

\renewcommand\thesection{\arabic{section}.}

\usepackage[english]{babel}

\usepackage{tocloft}
\cftsetindents{section}{0em}{2em}
\cftsetindents{subsection}{0em}{2em}
\renewcommand\cfttoctitlefont{\hfill\Large\bfseries}
\renewcommand\cftaftertoctitle{\hfill\mbox{}}
\setcounter{tocdepth}{2}

\usepackage{listings}
\usepackage{xcolor}

\usepackage{fullpage}

\usepackage{float}

\usepackage{amsfonts}

\usepackage{sectsty}
\sectionfont{\fontsize{14}{15}\selectfont}

\usepackage{graphicx}
\usepackage[margin=0.6in,includefoot,headsep=0.1in]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\cfoot{\thepage}
\rfoot{P. T. O.}
\lfoot{ROHIT DAS 30000114022}

\usepackage{booktabs}
\usepackage{tabularx}

\usepackage{verbatim}

%\usepackage{array}
%\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

\usepackage{courier}
\usepackage{pdflscape}
\lstdefinestyle{SQL-Michalstyle}
{%
  language   = SQL,
  %caption    = {SQL query explained},
  basicstyle = \footnotesize ,
  columns    = fixed,
}

\lstset{
	style=SQL-Michalstyle,
	backgroundcolor=\color{black!5}, % set backgroundcolor
}

\usepackage{csvsimple, filecontents}

\newcommand*{\plogo}{\fbox{$\mathcal{PL}$}} % Generic publisher logo

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\newcommand*{\titleGM}{\begingroup % Create the command for including the title page in the document
\hbox{ % Horizontal box
\hspace*{0.18\textwidth} % Whitespace to the left of the title page
\rule{1pt}{\textheight} % Vertical line
\rule{1pt}{\textheight}
\hspace*{0.05\textwidth} % Whitespace between the vertical line and title page text
\parbox[b]{0.75\textwidth}{ % Paragraph box which restricts text to less than the width of the page

{\noindent\Huge\bfseries Database Management \\[0.5\baselineskip] System.}\\[2\baselineskip] % Title
{\large \textit{-supervised by:}\\\\\Large \textsc Prof. Kaushik Majumdar, \\\\ Prof. Mihir Singh, and\\\\Prof. Subhanjan Sarkar}\\[4\baselineskip] % Tagline or further description

{\huge \textsc{Rohit Das}} % Author name
{\\\\\Large{B. Tech(Computer Sc. and Engg)}\\\\\Large{Roll: 30000114022\\\\\Large{Regn. No.:143000110023}\\\\\Large{6th Semester,2016}}}
\vspace{120pt} % Whitespace between the title block and the publisher
\begin{figure}[H]
\hspace*{100pt}
\includegraphics[width=90pt,height=\textheight,keepaspectratio]{/home/mouri/Pictures/makaut.jpg}
\end{figure}
{\noindent \textit{\large{Maulana Abul Kalam Azad University of Technology,\\\\West Bengal.\\\\}}{\large \LaTeX} \hspace{5pt}2017}\\[\baselineskip] % Publisher and logo
}}
\endgroup}

\begin{document}
%\pagestyle{empty} % Removes page numbers
\thispagestyle{empty}
\titleGM % This command includes the title page

\iffalse
\title{\textbf{\Huge Maulana Abul Kalam Azad University of\\[10pt] Technology}}
\date{\vspace{-5ex}}
\maketitle
\begin{center}
\textbf{\LARGE{(DBMS Assignment)}}
\end{center}
\begin{figure}[H]
\centering
\includegraphics[width=350pt,height=\textheight,keepaspectratio]{/home/mouri/Pictures/makaut.jpg}
\end{figure}
\bigskip

\begin{flushright}
\underline{\textbf{\author{\Huge Rohit Das}}}\\
\textbf{\LARGE{
B. Tech(CSE),5th Year\\
Roll No.: 3000114022\\
Regn. No.: 143000110023\\
Taught by: Prof. Kaushik Majumdar/ Prof. Mihir Singh\\
}}
\end{flushright}
%\tableofcontents
%\begin{table}[htbp]
%\centering
\fi

\begin{center}
\LARGE\textbf{\underline{INDEX}}
\end{center}
\thispagestyle{empty}
\begin{tabular}{|c|p{0.48\linewidth}|c|c|c|}
\textbf{Sl. No.}&\textbf{Particulars}&\textbf{Date}&\textbf{Page No.}&\textbf{Signature}\\[5pt] \hline
\\1.&Program to calculate average of cricket players.& 28/9/16 & 3 &\\ \hline
\\2.&Program to calculate cost for consumer.& 28/9/16 & 4 &\\ \hline
\\3.&Program to display votes received in election.& 28/9/16 & 5 &\\ \hline
\\4.&Program for operation on array elements.& 19/10/16 & 6 &\\ \hline
\\5.&Program to calculate factorial of a number.& 19/10/16 & 7 &\\ \hline
\\6.&Program to calculate sum of series$1+22+32+42+...$.& 19/10/16 & 7 &\\ \hline
\\7.&Program to add values of Complex no. objects.& 9/11/16 & 8 &\\ \hline
\\8.&Program to convert distances to inches and add.& 28/9/16 & 9 &\\ \hline
\\9.&Program for String class with different costructors.& 9/11/16 & 10 &\\ \hline
\\10.&Program to display unique roll of Student objects.& 9/11/16 & 10 &\\ \hline
11.&Program to swap values of objects using 'friend' function.& 9/11/16 & 11 &\\ \hline
\\12.&Program for operation on matrices.& 16/11/16 & 12 &\\ \hline
13.&Program to use overloaded operators on float numbers.& 16/11/16 & 14 &\\ \hline
\\14.&Program to compare two strings by '==' operator.& 16/11/16 & 15 &\\ \hline
\\15.&Program to implement current and savings a/c.& 23/11/16 & 16 &\\ \hline
\\16.&Previous program rewritten using constructors.& 23/11/16 & 18 &\\ \hline
\\17.&Program for an educational institution.& 23/11/16 & 20 &\\ \hline
\\18.&Program to implement a network.& 23/11/16 & 23 &\\ \hline
\\19.&Program to show overriding using 'virtual'.& 30/11/16 & 24 &\\ \hline
\\20.&Program to implement Shape class using 'virtual'.& 30/11/16 & 25 &\\ \hline
\\21.&Previous program rewritten without using 'virtual'.& 30/11/16 & 26 &\\ \hline
\\22.&Program to use template for an array.& 7/12/16 & 27 &\\ \hline
23.&Program to implement exception handling with multiple catch.& 7/12/16 & 28 &\\ \hline
\\24.&Program to implement rethrowing an exception.& 7/12/16 & 29 &\\ \hline
\\25.&Program to implement a generic vector.& 27/12/16 & 29 &\\ \hline
\end{tabular}
%\end{table}

\section{Date: 20/4/2017}

\csvautotabular{/home/mouri/DBMS2/DBMS/Week3/ETeam.csv}
\LARGE{ETeam (PK: ID)}

\bigskip

\bigskip

\large{\csvautotabular{/home/mouri/DBMS2/DBMS/Week3/Game.csv}}
\LARGE{Game(PK:ID)}

\large{\csvautotabular{/home/mouri/DBMS2/DBMS/Week3/Goal.csv}}
\LARGE{Goal (FK: MATCHID)}

\subsection{Show player name, team id,stadium and 		mdate for every german player.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select Goal.Player,Goal.TeamID,Game.Stadium,Game.MDate
from Goal join Game on Goal.MATCHID=Game.ID
where goal.teamid='GER'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week3/q1.csv}
\end{figure}

\subsection{Show team1,team2, and player for every goal scored by a player called 'Mario'.}
\underline{Program:}
\begin{lstlisting}[showstringspaces=false]
select Game.team1, Game.team2, Goal.Player 
from Goal join Game on Goal.MATCHID=Game.ID
where goal.matchid=game.id and goal.player like 'Mario%'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week3/q2.csv}
\end{figure}
\bigskip

\subsection{Show player, teamid, coach, gtime for all goals scored in the first 10 minutes.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select Goal.Player, Goal.TeamID,eteam.coach,goal.gtime 
from Goal join eteam on Goal.teamID=ETeam.ID
where goal.gtime <= 10
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week3/q3.csv}
\end{figure}
.

\subsection{List the dates of the matches and the name of the team in which 'Fernando Santos' was the team1 coach.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select Game.mdate, ETeam.teamname 
from Game join eteam on Game.Team1=ETeam.ID
where coach='Fernando Santos'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week3/q4.csv}
\end{figure}
\bigskip

\subsection{List the player for every goal scored in a game  whre the stadium was 'National Stadium, Warsaw'.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select Goal.player
from Game join goal on Goal.matchid=game.ID
where stadium='National Stadium, Warsaw'

\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week3/q5.csv}
\end{figure}
\bigskip

\subsection{Show the name of the player who scored a goal against Germany('GER').}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select goal.player from goal
join game on goal.matchid=game.id
where (game.team2='GER' or game.team1='GER') and goal.teamid!='GER'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week3/q6.csv}
\end{figure}

\subsection{Show the stadium and the number of goals scored in each stadium. Use count().}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select game.stadium,count(*) as goal_count from game
join goal on goal.matchid=game.id
group by game.stadium
order by count(*) asc
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week3/q7.csv}
\end{figure}
.

\section{Date: 27/4/2017}

\large{\csvautotabular{/home/mouri/DBMS2/DBMS/Week4/ETeam.csv}}
\LARGE{ETeam (PK: ID)}

.

.

\large{\csvautotabular[filter={\value{csvrow}<5}]{/home/mouri/DBMS2/DBMS/Week4/Game.csv}}
\LARGE{Game(PK:ID)}

% count rows
\csvreader{/home/mouri/DBMS2/DBMS/Week4/Game.csv}{}{}%
\edef\totalrows{\thecsvrow}
\large{\csvautotabular[filter={
      \(\thecsvinputline>6\)
 \and \(\thecsvinputline<\numexpr\totalrows-1\relax\)
}]
{/home/mouri/DBMS2/DBMS/Week4/Game.csv}}

.

.

\large{\csvautotabular[filter={\value{csvrow}<23}]{/home/mouri/DBMS2/DBMS/Week4/Goal.csv}}
\LARGE{Goal (FK: MATCHID)}

\csvreader{/home/mouri/DBMS2/DBMS/Week4/Goal.csv}{}{}%
\edef\totalrows{\thecsvrow}
\large{\csvautotabular[filter={
      \(\thecsvinputline>24\)
 \and \(\thecsvinputline<\numexpr\totalrows-1\relax\)
}]
{/home/mouri/DBMS2/DBMS/Week4/Goal.csv}}

\subsection{Show the matchdate,stadium,player name,goal time for match ids 1019 and 1021.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select game.mdate,game.stadium,goal.player, goal.gtime 
from Game left join goal 
on Goal.matchid=game.id
where game.id=1019 or game.id=1021
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week4/q1.csv}
\end{figure}
.

\subsection{Show all the goal time,player, stadium where first team was Germany.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select goal.gtime,goal.player,game.stadium  
from Game left join goal 
on Goal.matchid=game.id
where game.team1='GER'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week4/q2.csv}
\end{figure}
.
\subsection{Show the matchdate,stadium,teamname where Diego Maradona was the coach. Use right join.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select game.mdate,game.stadium,eteam.teamname
from Game right join eteam 
on game.team1=eteam.id or game.team2=eteam.id
where eteam.coach='Diego Maradona'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week4/q3.csv}
\end{figure}
.

\subsection{Show id,matchdate,stadium,coach and team name for all team2. Use full outer join.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select distinct game.id,game.mdate,game.stadium,eteam.coach,eteam.teamname
from Game full outer join eteam 
on game.team2=eteam.id
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular[filter={\value{csvrow}<5}]{/home/mouri/DBMS2/DBMS/Week4/q4.csv}
\end{figure}

\bigskip
\bigskip

\section{Date: 27/4/2017}
\csvautotabular{/home/mouri/DBMS2/DBMS/Week4/order.csv}
\bigskip

\LARGE{Order (PK:ORDER-ID, FK:CUSTOMER-ID)}

\bigskip

\large{\csvautotabular{/home/mouri/DBMS2/DBMS/Week4/customer.csv}}
\bigskip

\LARGE{Game(PK:CUSTOMER-ID)}

\bigskip
\bigskip

\large{\csvautotabular{/home/mouri/DBMS2/DBMS/Week4/employee.csv}}
\LARGE{Employee (PK: EMPID)}

\subsection{Show employee name and Manager name for Employee ID 4 and 6.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select b.name as Employee, a.name as Manager 
from employee a,employee b
where a.empid=b.manager and (b.empid=4 or b.empid=6)
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week4/q5.csv}
\end{figure}
.

\subsection{Show the entire list of employee name and employee id under manager "Palash Roy".}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select distinct emp.name as Employee, man.name as Manager 
from employee emp,employee man
where emp.manager=man.empid and man.empid=4
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week4/q6.csv}
\end{figure}

\bigskip
\bigskip
\section{Date: 4/5/2017}
\large{\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/clnt-mast.csv}}
\bigskip

\LARGE{Client\_Master (PK:Client-No)}

\bigskip

\bigskip

\footnotesize{\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/prod-mast.csv}}

\bigskip
\LARGE{Product\_Master  (PK:Product-No)}

\bigskip
\large{\csvautotabular[filter={\value{csvrow}<32}]{/home/mouri/DBMS2/DBMS/Week5/sal-ord.csv}}

\bigskip
\LARGE{Sales\_Order (PK: Order-No, FK: Client-No)}

\bigskip

\bigskip
\subsection{Retrieve the list of names, city and the states of all the clients.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select name, city, state from client_master
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q1.csv}
\end{figure}
\bigskip

\subsection{List all the clients who are located in Mumbai.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select name from client_master
where city='Mumbai'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
%\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q2.csv}
\end{figure}
\bigskip

\subsection{List the various products available from the PRODUCT-MASTER table.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select description from product_master
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q3.csv}
\end{figure}
\bigskip

\subsection{Change the city of Client\_No 'C00005' to Bangalore.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
update client_master
set city='Bangalore'
where client_no='C00005'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q4.csv}
\end{figure}
\bigskip

\subsection{Add a column called 'Telephone' of datatype 'number' and size='10' to the Client\_Master table.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
alter table client_master
add Telephone number(10)
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\verbatiminput{/home/mouri/DBMS2/DBMS/Week5/q5.txt}
\end{figure}

\subsection{Delete the column 'Telephone'.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
alter table client_master
drop column Telephone
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\verbatiminput{/home/mouri/DBMS2/DBMS/Week5/q6.txt}
\end{figure}

\subsection{Change the name of Client\_Master to Clnt\_Mast.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
rename client_master to clnt_mast
\end{lstlisting}
%Output:
\begin{figure}[H]
\centering
\end{figure}
\subsection{List the names of all clients having 'a' letter in their names.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select name from clnt_mast
where name like '%a%'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q9.csv}
\end{figure}
%\bigskip
%\smallskip

\subsection{List the names of the clients who stay in 'Bangalore' or 'Mangalore'.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select name from clnt_mast
where city like '_angalore'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q10.csv}
\end{figure}
\bigskip

\subsection{List the names of the clients having 'h' as the second letter in their names.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select name from clnt_mast
where name like '_h%'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q11.csv}
\end{figure}
%\bigskip
\smallskip

\subsection{List all the information from the Sales\_Order table for orders placed in the month of June.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select * from sales_order
where order_date like '%JUN%'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q12.csv}
\end{figure}
\bigskip

\subsection{List the information for Client\_No 'C00001' and 'C00002'.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select * from sales_order
where client_no='C00001' or client_no='C00002'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q13.csv}
\end{figure}
\bigskip

\subsection{List products whose selling price is greater than 500 and less than 700.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select * from product_master
where sell_price > 500 and sell_price < 700
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q14.csv}
\end{figure}
\bigskip

\subsection{List the names, city and states of clients who are not in the state of 'Maharashtra'.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select name,city,state from clnt_mast
where state <> 'Maharashtra'

\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q15.csv}
\end{figure}
\bigskip

\subsection{List the products whose selling price is more than 500. Calculate a new selling price as, original selling price * 15. Rename the new column in the output of the above query as New\_Price.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select description, sell_price*15 as new_price 
from product_master
where sell_price > 500
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\footnotesize{\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q16.csv}}
\end{figure}
\bigskip
\subsection{Count the number of products having sell\_price less than or equal to 500.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select count(sell_price) from product_master
where sell_price < = 500
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q18.csv}
\end{figure}
\bigskip
\subsection{List the order number and day on which clients placed their order.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select name,order_no,order_date,to_char(to_date(order_date,'dd/mm/yyyy'), 'DY') as day
from sales_order join clnt_mast on clnt_mast.client_no=sales_order.client_no
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q19.csv}
\end{figure}
\bigskip

\section{Date: 4/5/2017}

(Refer to tables on pages 7,8 and 9)

\subsection{Show the stadium and the number of goals scored in each stadium. For every match where 'GER' scored, show matchid, match date and the number of goals scored by 'GER'.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select matchid,mdate,count(*)
from game join goal 
on goal.matchid=game.id
where teamid='GER'
group by mdate,matchid
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q19.csv}
\end{figure}
\bigskip

\section{Date: 11/5/2017}
\large{\csvautotabular{/home/mouri/DBMS2/DBMS/Week6/teach.csv}}
\LARGE{Teacher (PK: ID)}

\bigskip

\bigskip

\large{\csvautotabular{/home/mouri/DBMS2/DBMS/Week6/dept.csv}}
\LARGE{Dept (PK: ID)}

\bigskip

\bigskip

\subsection{List the teachers who have NULL for their department.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select name from teacher
where dept is null
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week6/q1.csv}
\end{figure}
\bigskip

\subsection{Show teacher name and dept. name for teachers having not null in dept.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select teacher.name, dept.name as dept
from teacher join dept on teacher.dept=dept.id
where teacher.dept is not null
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week6/q2.csv}
\end{figure}
\bigskip

\subsection{Show teachers name, id, mobile and dept name.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select teacher.name, teacher.id, teacher.mobile, dept.name 
from dept full outer join teacher on teacher.dept=dept.id
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week6/q3.csv}
\end{figure}
%\bigskip
\medskip
\subsection{Use a different JOIN so that all teachers are listed.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select teacher.name, teacher.id, dept.name 
from dept right outer join teacher on teacher.dept=dept.id
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week6/q4.csv}
\end{figure}
%\bigskip
\medskip
\subsection{Use a different JOIN so that all departments are listed.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select teacher.name, teacher.id, dept.name 
from dept left outer join teacher on teacher.dept=dept.id
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week6/q5.csv}
\end{figure}
\bigskip

\subsection{Use COALESCE to print the mobile number. Use the number '07986 444 2266' if there is no number given. Show teacher name and mobile number or '07986 444 2266'}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select name,
coalesce (mobile,'07986 444 2266') as newmob
from teacher
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week6/q6.csv}
\end{figure}
\bigskip

\subsection{Use the COALESCE function and a LEFT JOIN to print the teacher name and department name. Use the string 'None' where there is no department.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select teacher.name, coalesce(dept.name,'None') as dept
from teacher left join dept on teacher.dept=dept.id
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week6/q7.csv}
\end{figure}
%\bigskip
\medskip
\subsection{Use COUNT to show the number of teachers and the number of mobile phones.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select count(name) as Total_Teachers,
count(mobile) as Total_Mobiles 
from teacher
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week6/q8.csv}
\end{figure}
%\bigskip
\medskip
\subsection{Use COUNT and GROUP BY dept.name to show each department and the number of staff. Use a RIGHT JOIN to ensure that the Engineering department is listed.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select dept.name, count(teacher.name) as Total_staff
from teacher right join dept on teacher.dept=dept.id
group by dept.name
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week6/q9.csv}
\end{figure}
\bigskip
\subsection{Use CASE to show the name of each teacher followed by 'Sci' if the teacher is in dept 1 or 2 and 'Art' otherwise.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select name,
case when dept=1 or dept=2 then 'Sci'
else 'Art'
end as Dept
from teacher
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week6/q10.csv}
\end{figure}
\smallskip

\subsection{Use CASE to show the name of each teacher followed by 'Sci' if the teacher is in dept 1 or 2, show 'Art' if the teacher's dept is 3 and 'None' otherwise.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select name,
case when dept=1 or dept=2 then 'Sci'
when dept=3 then 'Art'
else 'None'
end as Dept
from teacher
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week6/q11.csv}
\end{figure}

\end{document}

### 2017-05-27 SQL/SQL.tex
Modified SQL.tex
Signed-off-by: mouri11 <rohit.das950@gmail.com>

@@
 
-\usepackage{tocloft}
+\usepackage[titles]{tocloft}
 \cftsetindents{section}{0em}{2em}
 \cftsetindents{subsection}{0em}{2em}
-\renewcommand\cfttoctitlefont{\hfill\Large\bfseries}
+\renewcommand\cfttoctitlefont{\hfill\LARGE\bfseries}
 \renewcommand\cftaftertoctitle{\hfill\mbox{}}
-\setcounter{tocdepth}{2}
+\setcounter{tocdepth}{10}
+\setlength{\cftsubsecindent}{1cm}
+\setlength{\cftsubsecnumwidth}{3em}
+\addto\captionsenglish{%  
+  \centering\renewcommand{\contentsname}{INDEX}%
+}
 
@@
 
-\begin{center}
-\LARGE\textbf{\underline{INDEX}}
-\end{center}
-\thispagestyle{empty}
-\begin{tabular}{|c|p{0.48\linewidth}|c|c|c|}
-\textbf{Sl. No.}&\textbf{Particulars}&\textbf{Date}&\textbf{Page No.}&\textbf{Signature}\\[5pt] \hline
-\\1.&Program to calculate average of cricket players.& 28/9/16 & 3 &\\ \hline
-\\2.&Program to calculate cost for consumer.& 28/9/16 & 4 &\\ \hline
-\\3.&Program to display votes received in election.& 28/9/16 & 5 &\\ \hline
-\\4.&Program for operation on array elements.& 19/10/16 & 6 &\\ \hline
-\\5.&Program to calculate factorial of a number.& 19/10/16 & 7 &\\ \hline
-\\6.&Program to calculate sum of series$1+22+32+42+...$.& 19/10/16 & 7 &\\ \hline
-\\7.&Program to add values of Complex no. objects.& 9/11/16 & 8 &\\ \hline
-\\8.&Program to convert distances to inches and add.& 28/9/16 & 9 &\\ \hline
-\\9.&Program for String class with different costructors.& 9/11/16 & 10 &\\ \hline
-\\10.&Program to display unique roll of Student objects.& 9/11/16 & 10 &\\ \hline
-11.&Program to swap values of objects using 'friend' function.& 9/11/16 & 11 &\\ \hline
-\\12.&Program for operation on matrices.& 16/11/16 & 12 &\\ \hline
-13.&Program to use overloaded operators on float numbers.& 16/11/16 & 14 &\\ \hline
-\\14.&Program to compare two strings by '==' operator.& 16/11/16 & 15 &\\ \hline
-\\15.&Program to implement current and savings a/c.& 23/11/16 & 16 &\\ \hline
-\\16.&Previous program rewritten using constructors.& 23/11/16 & 18 &\\ \hline
-\\17.&Program for an educational institution.& 23/11/16 & 20 &\\ \hline
-\\18.&Program to implement a network.& 23/11/16 & 23 &\\ \hline
-\\19.&Program to show overriding using 'virtual'.& 30/11/16 & 24 &\\ \hline
-\\20.&Program to implement Shape class using 'virtual'.& 30/11/16 & 25 &\\ \hline
-\\21.&Previous program rewritten without using 'virtual'.& 30/11/16 & 26 &\\ \hline
-\\22.&Program to use template for an array.& 7/12/16 & 27 &\\ \hline
-23.&Program to implement exception handling with multiple catch.& 7/12/16 & 28 &\\ \hline
-\\24.&Program to implement rethrowing an exception.& 7/12/16 & 29 &\\ \hline
-\\25.&Program to implement a generic vector.& 27/12/16 & 29 &\\ \hline
-\end{tabular}
-%\end{table}
+\tableofcontents
+\break
 
@@
 \centering
-%\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q2.csv}
+\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q2.csv}
 \end{figure}

### 2017-08-03 cv/cv-sections/education.tex
Adding CV
Signed-off-by: mouri11 <rohit.das950@gmail.com>

%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Education}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{B. Tech.  in Computer Science and Engineering} % Degree
{MAKAUT, WB (Maulana Abul Kalam Azad University of Technology)\newline (formerly WBUT)} % Institution
{BF -142, Salt Lake Sector -I, \newline
Kolkata - 700064.} % Location
{Jul. 2014 - PRESENT} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Got cleared under TFW scheme (Tuition-Fee Waiver scheme) meant for students ranking well in WBJEE.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Higher Secondary Education} % Degree
{Holy Home School} % Institution
{Serampore - 712201.} % Location
{Apr. 2012 - Mar. 2014} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Indian School Certificate Examination (ISC) score - 95.25\%.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Secondary Education} % Degree
{Don Bosco School} % Institution
{Bandel, P. O. \& Dist. Hooghly - 712103.} % Location
{Apr. 2002 - Mar. 2012} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Indian Certificate of Secondary Education (ICSE) score - 94.4\%.}
\item {Qualified for Anant Scholarship, provided to meritorious students passing class 10 or equivalent.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}

### 2017-11-06 cv/cv-sections/education.tex
Resume: Minor Changes in details
Signed-off-by: Rohit Das <rohit.das950@gmail.com>

@@
 \begin{cvitems}
+\item {CGPA(till 6th Semester) - 7.89}
 \item {Got cleared under TFW scheme (Tuition-Fee Waiver scheme) meant for students ranking well in WBJEE.}
@@
 {Higher Secondary Education} % Degree
-{Holy Home School} % Institution
+{Holy Home School, Serampore} % Institution
 {Serampore - 712201.} % Location
@@
 \begin{cvitems}
-\item {Indian School Certificate Examination (ISC) score - 95.25\%.}
+\item {Indian School Certificate Examination (ISC) score(best of 4 subjects) - 96.25\%.}
 \end{cvitems}
@@
 {Secondary Education} % Degree
-{Don Bosco School} % Institution
+{Don Bosco School, Bandel} % Institution
 {Bandel, P. O. \& Dist. Hooghly - 712103.} % Location
@@
 \begin{cvitems}
-\item {Indian Certificate of Secondary Education (ICSE) score - 94.4\%.}
+\item {Indian Certificate of Secondary Education (ICSE) score (best of 5 subjects) - 94.4\%.}
 \item {Qualified for Anant Scholarship, provided to meritorious students passing class 10 or equivalent.}

### 2018-03-16 GSoC/GSoC.tex
GSoC: Added files for GSoC proposal 2018
Signed-off-by: Rohit Das <rohit.das950@gmail.com>

%% This is file `elsarticle-template-1-num.tex',
%%
%% Copyright 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%
%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%%
%% $Id: elsarticle-template-1-num.tex 149 2009-10-08 05:01:15Z rishi $
%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1-num.tex $
%%
\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb} %for stylish bullet points(math symbols)
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{amsmath, mathdots, paralist}
\usepackage{float}
\usepackage{graphicx} %for inserting images
\usepackage{tabularx} %for tables
\usepackage{ltablex}
\usepackage{array} %for changing row height
\usepackage{enumitem} %for changing spacing around itemize

\usepackage{xpatch}

% Patching the \hrule\vskip12pt out .. do it twice!!!
\makeatletter
\xpatchcmd{\pprintMaketitle}{%
  \hrule\vskip12pt%
}{}{\typeout{Success}}{}
\makeatother

% Customizing footer
%\makeatletter
%\def\ps@pprintTitle{%
% \let\@oddhead\@empty
% \let\@evenhead\@empty
% \def\@oddfoot{\leftline{GSoC KDE 2018}}%
% \let\@evenfoot\@oddfoot
% }
%\makeatother

\usepackage[left=2cm, right=2cm, top=2.5cm, bottom=2cm, footskip=1cm]{geometry}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

\biboptions{sort&compress}

\journal{GSoC KDE 2018}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{One Step Closer to Version 1.0}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author{Rohit Das}

\address{ \textbf{Email ID}: rohit.das950@gmail.com}
\address{ \textbf{Freenode IRC Nick}: mouri11}
\address{ \textbf{Location}: Serampore, West Bengal, India UTC+5:30}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
% \linenumbers

%% main text
\section{Motivation}
\label{S:1}

{GCompris is a software suite comprising educational software for children aged 2 to 10. Protected under the GNU General Public License, GCompris is free for developers to work with and contribute to. Having more than 137 activities, developers old and new can have their hands full with fun things to play around. Hence, GCompris is not only educational for the kids, but also for their creators.}

{Teaching kids and making them more imaginative is what GCompris aims at, and I intend to help with the process of its development. Since GCompris was originally written in GTK+, there are many activities to work with, from porting old ones, to completing and creating activities anew in Qt-Quick. The activity I intend to work on is: \textit{Analog Electricity}.}
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

\section{Project Goals}
\label{S:1}
{ I wish to opt for porting Analog Electricity from scratch from its Gtk+ version for my intended work as a student for Google Summer of Code. By the end of the period, I intend to achieve the following:
}
\begin{itemize}
\item \textbf{Analog Electricity activity:} This activity is to be started from scratch, and discussions on this can be found at:  \href{https://phabricator.kde.org/T5954}{https://phabricator.kde.org/T5954}.
\end{itemize}

\section{Implementation Details}
\label{S:1}

	\subsection{Analog Electricity}
	{\textit{Analog Electricity}, as the name suggests is aimed at teaching children the basics of analog electric circuits, the various components involved in a circuit, how electricity flows and the likes.}\\

		\textbf{Main Goals:}
		\begin{itemize}
			\item[$\blacksquare$] \textbf{Creating separate modes of learning and free play:}
			\begin{itemize}
			\item[$\square$] {The Gtk+ version simply has a free play mode, where children can simply play around with the components, make a circuit, and complete a level when the bulb glows. This could be a bit counter-intuitive, as a child wouldn’t know how to construct a basic circuit, what each newer components and their functions are and how to use them, etc.}

			\begin{figure}[H]
			\centering\includegraphics[width=0.9\linewidth]{./images/gsoc1}
			\caption{Mockup for possible layout}
			\end{figure}

			\item[$\square$] {So, two separate modes shall be created, where in one, i.e. the tutorial mode, the child can be guided through each tutorial, teaching him/her the basics of analog circuits and components. In the free play mode, the child can then use their new-found knowledge to construct circuits. Some ideas on the modes are:}

					\begin{itemize}
					\item {In the initial levels, children will be introduced to the two sources of current, and how can they observe and relate to it in real life. For a DC source, a simple dry cell will be used, and for AC, a plug analogous to ones in our homes can be used.}

					\item {They will use the above sources in a circuit and see how it works. Separate levels shall be dedicated initially to teaching how the sources work and how they differ. The arrows showing direction of current shall be very helpful in this case. In later levels, both sources shall be kept(in separate levels) to teach them how components work with each source.}

					\item {In higher levels, as components like capacitors, solenoids are introduced, they can be taught about what to expect when connected with the two sources. The ‘why’s’ and ‘how’s’ of it can be left out since it will need a lot more than primary school knowledge to understand.}

					\item {For components utilising magnetic properties of current like solenoids, children will be taught about the relation between current and magnetism(tutorial on magnetism explained later).}

					\item {The free mode will contain all of the components discussed here for free implementation, experimentation and learning of the child. Levels won’t be necessary here.}

					\item {For showing the resistance, current and voltage flowing across circuits, Kirchoff’s law will be used. Each component shall have separate functions to keep track of individual current flowing through it. Using that, the overall resistance, current and voltage in the circuit can be calculated. Details of the calculation will be beyond the comprehension of the children, and hence hidden from users.}

					\item {A resistor can be explained analogous to a water tap, which can  restrict/allow water flow.}

					\item {Capacitors can be explained as components having a “capacity” to hold current, and how they work with DC and AC. Capacitors shall be made to be used with a dry cell as well as an AC source(a plug) and a resistor in tutorial mode, and the child will be free to experiment in free play.}

					\item {For teaching magnetism and why it occurs in current-carrying components, a superficial explanation will be quite helpful. In the tutorials, a magnet can be depicted to be attracting iron nails kept nearby. Children will be encouraged to try out using small magnets and iron objects(under adult supervision of course).}

					\item {A solenoid shall be implemented in the same level as above-mentioned tutorial, and hence would need some graphical cues, like when a solenoid is switched on, some nearby iron nails will be animated to move(attracted) towards it, and stick to it, thus displaying magnetic behaviour. The solenoid is being introduced only to teach that current can produce magnetism, and its applications in real life.}

					\end{itemize}
			\end{itemize}

			\begin{figure}[H]
			\centering\includegraphics[width=0.9\linewidth]{./images/gsoc2}
			\caption{Mockup for modes}
			\end{figure}

			\begin{figure}[H]
			\centering\includegraphics[width=0.9\linewidth]{./images/gsoc3}
			\caption{Mockup for choice between modes}
			\end{figure}

			\item[$\blacksquare$] \textbf{Simulator for analog components and circuits:}
				\begin{itemize}
				\item[$\square$] {A sandbox for making circuits and testing out components will be created, which will enable adding/removing components, connecting various circuits and testing them out.}
				\item[$\square$] {Components will be modeled as closely as possible to represent how they actually look and work in real life. Unlike digital electronic components, which work on discrete values, analog components shall be modeled to work with any voltage values and give correct or close to correct results. Clicking on them will show their names, and tutorials shall show how they work.}

				\begin{figure}[H]
				\centering\includegraphics[width=0.9\linewidth]{./images/gsoc4}
				\caption{Mockup showing pinchArea and components}
				\end{figure}

				\item[$\square$] {The external library, available at \href{https://github.com/Aerlinger/maxwell}{https://github.com/Aerlinger/maxwell}, although implements various analog components, cannot be directly used here, as Qt Quick does not support js classes. So this library shall be solely used for technical lookups and taking ideas on how to better implement components. Most of the ideas below have been formulated after a thorough observation of the repository.}

					\begin{itemize}
					\item {Since js classes aren’t available in Qt, each component will be implemented with its own separate js file, and exported as a module to be used in circuits.}

					\item {A base circuit component file shall be shared among all other components, containing basic features like resistance, voltage, etc. and functions to calculate the values of the attributes, as well as rendering them on screen.}

					\item {The interface shall be similar to digital electricity, easy for children to interact and understand.}

					\item {For the oscilloscope, Qt Charts can be used(optional: may be configured to use OpenGL for rendering waveforms in OpenGL devices). The other options are:}

						\begin{itemize}
							\item {Using smoothie (\href{http://smoothiecharts.org/}{http://smoothiecharts.org/})(js charting library)}

							\item {Using d3.js (\href{https://d3js.org/}{https://d3js.org/}) along with Qml to render graphs(the external library uses d3.js and rickshaw (\href{https://www.npmjs.com/package/rickshaw}{https://www.npmjs.com/package/rickshaw}), relying on d3.js).}
						\end{itemize}

					\item {As in the external library, we can use marquee text to denote the direction of flow of current, with different colours for various directions of current flow, or determine the direction of current by the polarity of the source, and assign simple arrows at the ends of connections(later option looks better).}\\
					\end{itemize}

					\item[$\square$] {Lastly, all of the components(js files, including wires) shall be brought together using Qml.}			
				\end{itemize}

				\begin{figure}[H]
				\centering\includegraphics[width=0.9\linewidth]{./images/gsoc5}
				\caption{Mockup showing circuits with current direction and waveform}
				\end{figure}

		\item[$\blacksquare$] \textbf{Add more components:}

			\begin{itemize}
			\item[$\square$] {Components like capacitors and solenoids will be added for improved and advanced knowledge on important analog components.}

			\item[$\square$] {Addition of components like capacitors, etc. may also be made interesting by adding a simple pre-adjusted oscilloscope(since the children will need a separate tutorial to handle the controls) to show how the waves of an analog signal varies, and a speaker can be added for audio to show how waves sound, with a volume slider.}
			\end{itemize}

		\item[$\blacksquare$] \textbf{Improvements in UI:}
			\begin{itemize}
			\item[$\square$] {For the layout, keeping it similar to that of digital electricity will help children easily understand how both are or aren’t related and help them differentiate between them. The dark background will also help in clearer depiction of images and text.}
			\item[$\square$] {Displaying voltage, current in case of power source and bulbs, and resistance as well in case of resistors, etc. under the components rather than on them.}

			\item[$\square$] {Using a darker background to enable better legibility of text displayed.}

			\item[$\square$] {Wires to show arrows to display direction of current flow(helpful in case of capacitors, etc.)}

			\item[$\square$] {To prevent cluttering of various components as levels increase, pinchArea shall be implemented to enable navigation among various components in free mode.}\\
			\end{itemize}

		\item[$\blacksquare$] \textbf{Increasing difficulty with levels:}
			\begin{itemize}
			\item[$\square$] {Levels shall be presented in tutorial mode only, so that children can get help to progressively learn the various components and their functions. In free mode, all components shall be available for practice and experimentation.}

			\item[$\square$] {Components mentioned earlier will be introduced into the activity at a much later stage, since these will require a much thorough knowledge even for using in a basic circuit.}
			\end{itemize}
		\end{itemize}
\bigskip\bigskip

\section{Timeline}
\label{S:1}

\begin{center}
\setlength{\extrarowheight}{1.75pt}
\begin{tabularx}{\linewidth}{|l|X|}
\hline

\textbf{Time Period} & \textbf{Activity for the Period}\\
\hline

{April 24 - August 14, 2018} & {\textit{Analog Electricity}}\\
\hline

{April 24 - May 13} & {\textit{Community Bonding}}\\
\hline

 & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Bond with the mentors, go through further documentation and look up useful libraries.
	\item Take notes and suggestions from mentors and bond with other GSoC candidates.
\end{itemize}
}\\
\hline\hline

{May 14 - June 12} & {\textit{Development of Basic Layout and Simulator}}\\
\hline

{May 14 - May 20} & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Build the basic main layout and layouts for tutorial and free mode, similar to digital electricity, without components(generalize code between activities as much as possible)
\end{itemize}
}\\
\hline

{May 21 - May 24} & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Submit work for review
	\item Add improvements based on suggestions
\end{itemize}
}\\
\hline

{May 25 - June 10} & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Test out codes from external libraries, and start implementing basic components without classes

	\begin{itemize}[noitemsep, topsep=2pt]
		\item Using json files to depict various features of components like voltage, resistance,etc will make it easier to handle and change while development and testing(much like in the external library)

		\item Functioning of components will be better handled by separate js files for each type of component(initially implementing simple ones like resistors)

		\item Basic components like bulbs, small resistors, switches, potentiometers and DC sources shall be implemented, using simple circuits.
	\end{itemize}
\end{itemize}
}\\
\hline

{June 11 - June 12} & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Submit work for possible improvements before final submission for phase 1 review
\end{itemize}
}\\
\hline\hline

{June 13 - June 15} & {\textit{Submission and Review - Phase I
}}\\
\hline

 & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Submit work for review by mentors
	\item Make changes as suggested in reviews
	\item Submit work for final evaluation of Phase I
\end{itemize}
}\\
\hline\hline

{June 16 - July 10} & {\textit{Addition of tutorials and advanced components
}}\\
\hline

{June 16 - June 25} & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Work on developing tutorials easy enough to be understood by children. The tutorials shall be built first so as to give an insight on how to proceed to make future components next.

	\begin{itemize}[noitemsep, topsep=2pt]
		\item Tutorials for resistors shall consist of pictures depicting what and why of a resistor, followed by how to use them, and analogies to taps being used to restrict water flow similar to resistors restricting current flow.

		\item Concepts of serial and parallel circuits shall be introduced next. Levels shall be particularly allotted for this purpose.

		\item For capacitors, children shall be taught what a capacitor does, i.e. store electricity, and hence how it is different from  a battery. A simple circuit can be depicted in images, consisting of a bulb which will slowly dim out on disconnecting from a DC cell, as it will be connected to a capacitor in parallel.

		%\item For solenoids, a tutorial level will be included where magnetism will be exhibited as follows: a solenoid connected with a battery will be shown. An image of iron nails kept nearby shall be animated to move nearer the solenoid, depicting attraction. In the tutorial, a brief description of a magnet and why it attracts only certain materials.
	\end{itemize}
\end{itemize}
}\\
\hline

%{June 16 - June 25} & \par
%\parbox{12cm}{
%\begin{itemize}[noitemsep, topsep=2pt]
	%\begin{itemize}[noitemsep, topsep=2pt]
		%\item For solenoids, a tutorial level will be included where magnetism will be exhibited as follows: a solenoid connected with a battery will be shown. An image of iron nails kept nearby shall be animated to move nearer the solenoid, depicting attraction. In the tutorial, a brief description of a magnet and why it attracts only certain materials.
	%\end{itemize}
%\end{itemize}
%}\\
%\hline

 & \par
 \parbox{12cm}{
	\begin{itemize}[noitemsep, topsep=2pt]
		\item 
		\begin{itemize}[noitemsep, topsep=2pt]
			\item For solenoids, a tutorial level will be included where magnetism will be exhibited as follows: a solenoid connected with a battery will be shown. An image of iron nails kept nearby shall be animated to move nearer the solenoid, depicting attraction. In the tutorial, a brief description of a magnet and why it attracts only certain materials.
		\end{itemize}
	\end{itemize}	 
 }\\
 \hline

{June 26 - July 1} & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Submit above work for review
	\item Discuss possible improvements and fixes
\end{itemize}
}\\
\hline

{July 2 - July 9} & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Work on modelling additional components like capacitors as well as increase levels and their difficulty.

	\begin{itemize}
		\item Start working on AC source and capacitors(partial implementation)
	\end{itemize}
\end{itemize}
}\\
\hline\hline

{July 10  - July 13} & {\textit{Submission and Review - Phase II
}}\\
\hline

 & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Submit work for review by mentors
	\item Make changes as suggested and submit for evaluation in Phase II.
\end{itemize}
}\\
\hline\hline

{July 14 - August 7} & {\textit{Final touches to Analog activity
}}\\
\hline

 & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Complete implementing capacitors.
	\item Implement solenoids(and possibly, oscilloscope and speaker).
	\item Occasional submission of code for review and suggested improvements.
	\item Fixing further issues and implementing final suggestions
\end{itemize}
}\\
\hline\hline

{August 8 - August 14} & {\textit{Submission for final evaluation
}}\\
\hline

 & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Submission of entire work for final review and suggestions
	\item Handing over final works for evaluation
\end{itemize}
}\\
\hline\hline

\end{tabularx}
\end{center}
\bigskip\bigskip

\section{About Me}
\label{S:1}
{I am currently in my final year at Maulana Abul Kalam Azad University of Technology (formerly WBUT), Kolkata, pursuing B. Tech. in Computer Science and Engineering. I have been contributing to the Qt version of GCompris since September 2017. Some of my contributions are:}
\begin{itemize}
\item {Removed dependency of ball direction on mouse buttons in Penalty activity:\\
\href{https://cgit.kde.org/gcompris.git/commit/?id=c94d7454c5a05364a1cbeae5b0bd1bed552ae5ed}{https://cgit.kde.org/gcompris.git/commit/?id=c94d7454c5a05364a1cbeae5b0bd1bed552ae5ed}}

\item {Progress bar corresponding to click zone only will be animated in Penalty activity:\\
 \href{https://cgit.kde.org/gcompris.git/commit/?id=e5b68f68657cf1ac25a6aa31924acfaf4a180f0b}{https://cgit.kde.org/gcompris.git/commit/?id=e5b68f68657cf1ac25a6aa31924acfaf4a180f0b}}

\item {Added easy mode in Letter-In-Word activity:\\
\href{https://cgit.kde.org/gcompris.git/commit/?id=c48f7057c27166edc6b8297bb3518a10ec2ee31b}{https://cgit.kde.org/gcompris.git/commit/?id=c48f7057c27166edc6b8297bb3518a10ec2ee31b}}

\item {Improved layout in Hangman activity:\\
\href{https://cgit.kde.org/gcompris.git/commit/?id=6a66cd44106015bd369616574d656a8dd19d15be}{https://cgit.kde.org/gcompris.git/commit/?id=6a66cd44106015bd369616574d656a8dd19d15be}}

\item {Fixed coding style issues for Ascending-Order activity:\\
\href{https://cgit.kde.org/gcompris.git/commit/?id=ade955e042ceb9774459a1181382159606a31502}{https://cgit.kde.org/gcompris.git/commit/?id=ade955e042ceb9774459a1181382159606a31502}}

\item {Added option to change case of letter to find in Letter-In-Word activity:\\
\href{https://commits.kde.org/gcompris/7c769594a5372e560904511404e2d1e156904050}{https://commits.kde.org/gcompris/7c769594a5372e560904511404e2d1e156904050}}
\end{itemize}
\bigskip
\textbf{Website: }\href{mouri11.github.io}{mouri11.github.io}\\
\textbf{Contact Info:}\\
\textbf{Email: }{rohit.das950@gmail.com}\\
\textbf{IRC Nick: } mouri11

\end{document}

%%
%% End of file `elsarticle-template-1-num.tex'.

### 2018-03-25 GSoC/GSoC.tex
GSoC: Edited files for GSoC proposal
Signed-off-by: Rohit Das <rohit.das950@gmail.com>
GSoC: Changed timeline a bit
Signed-off-by: Rohit Das <rohit.das950@gmail.com>

@@
 % Customizing footer
-%\makeatletter
-%\def\ps@pprintTitle{%
-% \let\@oddhead\@empty
-% \let\@evenhead\@empty
-% \def\@oddfoot{\leftline{GSoC KDE 2018}}%
-% \let\@evenfoot\@oddfoot
-% }
-%\makeatother
+\makeatletter
+\def\ps@pprintTitle{%
+ \let\@oddhead\@empty
+ \let\@evenhead\@empty
+ \def\@oddfoot{\leftline{\textit{GSoC KDE 2018 \hspace{115mm}\today}}}
+ \let\@evenfoot\@oddfoot
+ }
+\makeatother
 
@@
 					\item {They will use the above sources in a circuit and see how it works.
-Separate levels shall be dedicated initially to teaching how the sources work and how they differ.
+Separate levels shall be dedicated initially to teaching how the sources work and how they differ (explained in next point).
 The arrows showing direction of current shall be very helpful in this case.
 In later levels, both sources shall be kept(in separate levels) to teach them how components work with each source.}
+
+					\item {To teach the differences between the sources, waveforms will be helpful to show the physical difference.
+The arrows, as mentioned above, shall show how the direction changes with time in AC, but not in DC.
+The origin of the sources, i.e., dry cells for DC and power plugs for AC will also be helpful for children to distinguish between them.}
 
@@
 
-					\item {For showing the resistance, current and voltage flowing across circuits, Kirchoff’s law will be used.
-Each component shall have separate functions to keep track of individual current flowing through it.
-Using that, the overall resistance, current and voltage in the circuit can be calculated.
+					\item {In free mode, for showing the resistance, current and voltage flowing across circuits, Kirchoff’s law(for DC) will be used.
+All the components will be iterated through before calculating individual voltages and currents.
 Details of the calculation will be beyond the comprehension of the children, and hence hidden from users.}
+
+					\item {For solving complicated mathematical equations to obtain current and voltages across circuits(complex numbers for AC), QtMath (\href{http://doc.qt.io/qt-5/qtmath.html}{http://doc.qt.io/qt-5/qtmath.html}) header can be used for basic exponential, logarithmic and trigonometric calculations.
+For more complex calculations (and matrix manipulations if necessary), math.js (\href{http://mathjs.org/}{http://mathjs.org/}) is a good alternative.}
 
@@
 
-{May 25 - June 10} & \par
+{May 27 - June 10} & \par
 \parbox{12cm}{
@@
 
-		%\item For solenoids, a tutorial level will be included where magnetism will be exhibited as follows: a solenoid connected with a battery will be shown.
-An image of iron nails kept nearby shall be animated to move nearer the solenoid, depicting attraction.
-In the tutorial, a brief description of a magnet and why it attracts only certain materials.
 	\end{itemize}
@@
 
-%{June 16 - June 25} & \par
-%\parbox{12cm}{
-%\begin{itemize}[noitemsep, topsep=2pt]
-	%\begin{itemize}[noitemsep, topsep=2pt]
-		%\item For solenoids, a tutorial level will be included where magnetism will be exhibited as follows: a solenoid connected with a battery will be shown.
-An image of iron nails kept nearby shall be animated to move nearer the solenoid, depicting attraction.
-In the tutorial, a brief description of a magnet and why it attracts only certain materials.
-	%\end{itemize}
-%\end{itemize}
-%}\\
-%\hline
-
  & \par
@@
 	\begin{itemize}[noitemsep, topsep=2pt]
-		\item 
+		\item[] 
 		\begin{itemize}[noitemsep, topsep=2pt]
@@
 \end{center}
-\bigskip\bigskip
+\textbf{\underline{Note:} I will have to slow down my work during the month of May and/or June(mid May - End of May probably)} due to my final semester exams.
+\bigskip\bigskip\bigskip\bigskip
 
@@
 \textbf{Contact Info:}\\
-\textbf{Email: }{rohit.das950@gmail.com}\\
+\textbf{Email: }{Rohit Das $[$rohit.das950@gmail.com$]$}\\
 \textbf{IRC Nick: } mouri11

### 2018-03-27 GSoC/GSoC.tex
GSoC: Final Proposal
Signed-off-by: Rohit Das <rohit.das950@gmail.com>

@@
 					\begin{itemize}
-					\item {Since js classes aren’t available in Qt, each component will be implemented with its own separate js file, and exported as a module to be used in circuits.}
+					\item {Since js classes are not available in Qt, each component will be implemented with its own separate js file, and exported as a module to be used in circuits.}
 
@@
 			\item[$\square$] {Components mentioned earlier will be introduced into the activity at a much later stage, since these will require a much thorough knowledge even for using in a basic circuit.}
+			\end{itemize}
+
+		\item[$\blacksquare$] \textbf{Unit Testing and Documentation:}
+			\begin{itemize}
+			\item[$\square$] {The framework to automate unit testing will be developed in GSoC 18 most probably, so unit testing will be handled by that.}
+
+			\item[$\square$] {Comments mentioning the function of various methods and variables will be put in the code as necessary.}
 			\end{itemize}
@@
 	\item Work on developing tutorials easy enough to be understood by children. The tutorials shall be built first so as to give an insight on how to proceed to make future components next.
-
 	\begin{itemize}[noitemsep, topsep=2pt]
 		\item Tutorials for resistors shall consist of pictures depicting what and why of a resistor, followed by how to use them, and analogies to taps being used to restrict water flow similar to resistors restricting current flow.
-
-		\item Concepts of serial and parallel circuits shall be introduced next. Levels shall be particularly allotted for this purpose.
-
-		\item For capacitors, children shall be taught what a capacitor does, i.e.
-store electricity, and hence how it is different from  a battery.
-A simple circuit can be depicted in images, consisting of a bulb which will slowly dim out on disconnecting from a DC cell, as it will be connected to a capacitor in parallel.
-
 	\end{itemize}
@@
 	\begin{itemize}[noitemsep, topsep=2pt]
+
+		\item Concepts of serial and parallel circuits shall be introduced next. Levels shall be particularly allotted for this purpose.
+
+		\item For capacitors, children shall be taught what a capacitor does, i.e.
+store electricity, and hence how it is different from  a battery.
+A simple circuit can be depicted in images, consisting of a bulb which will slowly dim out on disconnecting from a DC cell, as it will be connected to a capacitor in parallel.
+
 		\item For solenoids, a tutorial level will be included where magnetism will be exhibited as follows: a solenoid connected with a battery will be shown.
@@
 \begin{itemize}
-\item {Removed dependency of ball direction on mouse buttons in Penalty activity:\\
+\item {Removed dependency of ball direction on mouse buttons in \textit{Penalty} activity:\\
 \href{https://cgit.kde.org/gcompris.git/commit/?id=c94d7454c5a05364a1cbeae5b0bd1bed552ae5ed}{https://cgit.kde.org/gcompris.git/commit/?id=c94d7454c5a05364a1cbeae5b0bd1bed552ae5ed}}
 
-\item {Progress bar corresponding to click zone only will be animated in Penalty activity:\\
+\item {Progress bar corresponding to click zone only will be animated in \textit{Penalty} activity:\\
  \href{https://cgit.kde.org/gcompris.git/commit/?id=e5b68f68657cf1ac25a6aa31924acfaf4a180f0b}{https://cgit.kde.org/gcompris.git/commit/?id=e5b68f68657cf1ac25a6aa31924acfaf4a180f0b}}
 
-\item {Added easy mode in Letter-In-Word activity:\\
+\item {Added easy mode in \textit{Letter-In-Word} activity:\\
 \href{https://cgit.kde.org/gcompris.git/commit/?id=c48f7057c27166edc6b8297bb3518a10ec2ee31b}{https://cgit.kde.org/gcompris.git/commit/?id=c48f7057c27166edc6b8297bb3518a10ec2ee31b}}
 
-\item {Improved layout in Hangman activity:\\
+\item {Improved layout in \textit{Hangman} activity:\\
 \href{https://cgit.kde.org/gcompris.git/commit/?id=6a66cd44106015bd369616574d656a8dd19d15be}{https://cgit.kde.org/gcompris.git/commit/?id=6a66cd44106015bd369616574d656a8dd19d15be}}
 
-\item {Fixed coding style issues for Ascending-Order activity:\\
+\item {Fixed coding style issues for \textit{Ascending-Order} activity:\\
 \href{https://cgit.kde.org/gcompris.git/commit/?id=ade955e042ceb9774459a1181382159606a31502}{https://cgit.kde.org/gcompris.git/commit/?id=ade955e042ceb9774459a1181382159606a31502}}
 
-\item {Added option to change case of letter to find in Letter-In-Word activity:\\
+\item {Added option to change case of letter to find in \textit{Letter-In-Word} activity:\\
 \href{https://commits.kde.org/gcompris/7c769594a5372e560904511404e2d1e156904050}{https://commits.kde.org/gcompris/7c769594a5372e560904511404e2d1e156904050}}
@@
 \bigskip
-\textbf{Website: }\href{mouri11.github.io}{mouri11.github.io}\\
+\textbf{Website: }\href{https://mouri11.github.io}{https://mouri11.github.io}\\
 \textbf{Contact Info:}\\

### 2018-06-07 cv/cv-sections/education.tex
resume_cv.latex: Updated CGPA,experience,skills
Signed-off-by: Rohit Das <rohit.das950@gmail.com>
education.tex: Changed marks for 10 and 12
Signed-off-by: Rohit Das <rohit.das950@gmail.com>

@@
 \begin{cvitems}
-\item {CGPA(till 6th Semester) - 7.89}
+\item {CGPA(till 7th Semester) - 7.93}
 \item {Got cleared under TFW scheme (Tuition-Fee Waiver scheme) meant for students ranking well in WBJEE.}
@@
 \begin{cvitems}
-\item {Indian School Certificate Examination (ISC) score(best of 4 subjects) - 96.25\%.}
+\item {Indian School Certificate Examination (ISC) score - 95.33\%.}
 \end{cvitems}
@@
 \begin{cvitems}
-\item {Indian Certificate of Secondary Education (ICSE) score (best of 5 subjects) - 94.4\%.}
+\item {Indian Certificate of Secondary Education (ICSE) score  - 93.71\%.}
 \item {Qualified for Anant Scholarship, provided to meritorious students passing class 10 or equivalent.}

### 2019-08-28 MTech/IC601/Assgnt2_Ppr_Rvw/Paper_Review.tex
Review: Adding Review for Adv ML paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Journal Article
% LaTeX Template
% Version 1.4 (15/5/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com) with extensive modifications by
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[twoside,twocolumn]{article}

\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.035} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics

\usepackage[english]{babel} % Language hyphenation and typographical rules

\usepackage[hmarginratio=1:1,top=18mm,bottom=18mm,left=12mm,
right=12mm,columnsep=15pt]{geometry} % Document margins

\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text

\usepackage{enumitem} % Customized lists
\setlist[itemize]{noitemsep} % Make itemize lists more compact

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\roman{subsection}} % roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

%\usepackage{fancyhdr} % Headers and footers
%\pagestyle{fancy} % All pages have headers and footers
%\fancyhead{} % Blank out the default header
%\fancyfoot{} % Blank out the default footer
%\fancyhead[C]{Running title $\bullet$ May 2016 $\bullet$ Vol. XXI, No. 1} % Custom header text
%\fancyfoot[RO,LE]{\thepage} % Custom footer text

\usepackage{titling} % Customizing the title section

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\setlength{\droptitle}{-4\baselineskip} % Move the title up

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{A Review of\\ Adversarial Machine Learning\\ 
\huge{(4th ACM Workshop on AISec, Oct. 2011,43-58)}} % Article title
\author{%
\Large \textsc{Rohit Das}\\ % Your name
\large ID No.: 11910230\\
\large M. Tech. (CSE)\\
Reviewers: Dr. Sk Subidh Ali, and Dr. Subhajit Sidhanta
}
\date{\today} % Leave empty to omit a date

%----------------------------------------------------------------------------------------

\begin{document}

% Print the title
\maketitle

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\section{Summary}

\lettrine[nindent=0em,lines=3]{T} he manuscript by Huang et. al. focuses primarily on the security fault lines in modern Machine Learning, how they can be utilized to break into secure learning systems, and manipulate data and users. It also sequentially outlines how such situations can be avoided by keeping some points in mind while designing a new or improving an existing learning algorithm or model, forming the crux of Adversarial Machine Learning.

%------------------------------------------------

\section{Outline}

Listed below are the milestones covered by the paper: 
\begin{itemize}
\item A very well-summarized overview of what Adversarial Machine Learning is, why it is necessary and relevant in this age, and how it can be accomplished.

\item Taxonomy of influence, security violations and specificity of attack by a potential adversary on a learning system.

\item Modeling secure learning systems as a game between an attacker and a defender, and how both can influence the learning algorithm, learning and evaluation of data, as well as the data itself. It also subtly creates the idea that a learning model can be made more robust by artificially creating an adversary and training the model with it.

\item An elaborate section on Causative attacks to learning systems, well-documented with graphs and data. It also contains case studies on two algorithms: SpamBayes and Principal Component Analysis (PCA)-based anomalous network traffic detector. The authors have highlighted the strengths of an attacker given certain degrees of freedom, and how they can be countered.

\item A section on Exploratory attacks, discussing various evasion techniques, theoretical and practical, and how the most optimum evasion techniques are not the ones generally implemented in real time.

\item Privacy violations, and advantages and roles of randomization of functions and parameters in learning models.
\end{itemize}

%------------------------------------------------

\section{Best Elements}
Below mentioned are the best elements of the paper:
\begin{itemize}
\item All conclusions, facts and experiments have been well-supported with relevant data and graphs. The graphs clearly highlight the differences between using a robust and a non-secure learning model.

\item The paper mainly focuses on causative attacks, the most malicious of attacks, and extensive research has been done into its types, variants and countermeasures.

\item The two algorithms used as case studies are very much used in real life situations, and hence makes the paper very relevant in this day and age, thereby easily underlining the need for the topic researched on.

\item Privacy, being a trending concept throughout history and a fundamental human right, is also a part of this paper, and makes it a must-read for researchers in this field.
\end{itemize}
%------------------------------------------------
%
\section{Limitations}
\begin{itemize}
\item A section on image and pattern recognition, and how adversaries can trick such models, could have been made a part of the research, as it is a budding novel area in Machine Learning, and specifically, Deep Learning.
\item The paper is a bit too textual. Adding more images would have helped better illustrate the various attacks and countermeasures presented here.
\end{itemize}
%
%-----------------------------------------------------------------------
%
\section{Opinion}
~~~~~The paper gives a good introduction and an elaborate explanation on Adversarial Machine Learning, and how to counter it. It aptly highlights the necessity and relevance of securing learning models, especially when they will be planned to be used in mission-critical situations. However, a more generous use of images would've helped illustrate the attacks and countermeasures better.
%
%-----------------------------------------------------------------------

\end{document}

### 2019-08-28 MTech/CS553/HW2/HW2_11910230.tex
HW2: Adding assignment 2 for CS553

\documentclass[12pt]{article}

\usepackage[a4paper, left = 2cm, right = 2cm, top = 2cm, bottom = 2cm]{geometry}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{graphicx}

\usepackage{listings}
\usepackage{xcolor}
\lstset{
	language = Python,
	backgroundcolor=\color{black!5}, % set backgroundcolor
}

\renewcommand{\baselinestretch}{1.5}

\renewcommand\thesection{\arabic{section}.}

\usepackage{tocloft}
\cftsetindents{section}{0em}{2em}
\cftsetindents{subsection}{0em}{2em}
\renewcommand\cfttoctitlefont{\hfill\Large\bfseries}
\renewcommand\cftaftertoctitle{\hfill\mbox{}}
\setcounter{tocdepth}{2}

%\title{CS553: Cryptography \\
%		Assignment 2 - Solutions\\\vspace{1cm}}
%\author{Rohit Das (11910230)}

\begin{document}
%\maketitle
%\newpage
\begin{titlepage}
\centering
\vspace*{\fill}
\huge CS553: Cryptography\\
\LARGE Assignment 2: Solutions\\
\Large Rohit Das (11910230)\\\vspace{0.8cm}
\today
\vspace*{\fill}
\end{titlepage}

\section{How Many Keys?}
\begin{large}
$r = 23$ (formed from $2nd$ and $3rd$ digits of roll number)\\
$\therefore \mathbb{Z}^{+}_{23} = \{0,1,...,22\}$\\
Let $K$ be the set of possible keys, such that $\forall	k \in K$, gcd($r,k$) $= 1$.\\
So, given $r = 23$, $K = \{1,2,...,22\}$.\\
$\mathbf{\therefore |K| = 22}$.
\end{large}

\section{Euler Phi Function}
\begin{large}
Euler Phi Function, also known as Euler's totient function, returns the count of integers less than and relatively prime to n. It is denoted by $\phi(n)$.\\
For prime positive integers, $\phi(n) = (n - 1)$. For other positive integers, if $n = pq$, where p,q $\in \mathbb{Z}^{+}$ and prime, $\phi(n) = (p - 1)(q - 1)$.\\
The number of keys, $|K|$, for an Affine Cipher defined over $\mathbb{Z}^{+}_{r}$ can be easily obtained by simply using Euler's totient function $\phi(r)$.\\
Since our $r$ is prime, $\phi(r) = (r - 1) = 22$.
\end{large}

\section{Bijection}
\begin{large}
Given $X = \{x_{1}, x_{2},..., x_{n}\}, Y = \{y_{1}, y_{2},..., y_{n}\}$ and $|X| = |Y|$.\\
Also given, $f: X \to Y$ is injective, i.e. $\forall$ $x \in X$, $f(x)$ is unique, or $f(x)$ is a one-to-one function. So naturally, $|X| \le |Y|$.\\
But, we know $|X| = |Y|$, meaning, $\forall$ $y \in Y$, $\exists$ $x \in X$, s.t. $f(x) = y$. Hence, $f$ is also surjective, i.e. onto.\\
\begin{figure}[h!]
\centering\includegraphics[width = 0.75\linewidth]{./images/HW2_1.png}
\end{figure}
$\therefore f$ is a bijection (Proved).
\end{large}

\section{Euclidean GCD}
Python code (Python3): Euclidean\textunderscore gcd.py
\lstinputlisting[language = Python, showstringspaces=false]{./python_code/Euclidean_gcd.py}

\section{Involutory Key}
\begin{large}
\subsection{Proof of involutory key}
Given an Affine Cipher over $\mathbb{Z}_{m}$ with $K = (a,b)$.\\
Let $e_{K}(x) = (ax + b)$ mod m, $d_{K}(x) = a^{-1}(x - b)$ mod m be the encryption and decryption function respectively.\\
\underline{Proof 1}: Assuming key K is involutory, i.e. $d_{K}(x) = e_{K}(x).......(1)$, to prove\\ $a^{-1}$ mod m $ = a$, and $b(a + 1) \equiv$ $0$ mod m.\\
From $(1)$, $(ax + b)$ mod m $=$ $a^{-1}(x - b)$ mod m,\\
$\implies$ $(ax + b)$ mod m = $(a^{-1}x - a^{-1}b)$ mod m\\
$\therefore$ $a$ $\equiv$ $a^{-1}$ mod m$....(2)$, and\\ $b$ $\equiv$ $-a^{-1}b$ mod m$....(3)$ $[\because$ two functions $ax + b$ and $cx + d$ are equal if their coefficients are equal, i.e. a = c and b = d].\\
From $(2)$, we get $a \equiv a^{-1}$ mod m (Proved).\\
From $(3)$, we get $ab \equiv -b$ mod m,\\
$\implies$ $b(a + 1) \equiv 0$ mod m (Proved)\\
\underline{Proof 2}: Assuming $a \equiv a^{-1}$ mod m$...(4)$, and $b(a+1) \equiv 0$ mod m, to prove K is involutory, i.e. $e_{K}(x) = d_{K}(x)$\\
$b(a + 1) \equiv 0$ mod m\\
$\implies ba \equiv -b$ mod m, $\implies b \equiv -a^{-1}b$ mod m$...(5)$\\
Putting $(4)$ and $(5)$ in $e_{K}(x)$, we get\\
$e_{K}(x) = (ax + b)$ mod m = $\{a^{-1}x$ mod m  + ($-a^{-1}b)$ mod m\} mod m\\
= $a^{-1}(x - b)$ mod m = $d_{K}(x)$ $\implies$ Key K is involutory\\
$\therefore$ The above two proofs prove that Key K is involutory iff $a \equiv a^{-1}$ mod m, and $b(a + 1) \equiv 0$ mod m.(Proved)
\subsection{Number of involutory keys}
For an Affine Cipher defined over $\mathbb{Z}_{15}$, possible values for a, such that $a = a^{-1}$ mod m are \{$1,4,11,14$\}(using $a^{2}$ mod $15$). For each value of a, possible values of b such that $b(a + 1) \equiv 0$ mod n follow:\\
For $a =  1$, $b$ (1 + 1) = $2b$, meaning, only possible value for b $\in$ $\mathbb{Z}_{15}$ is 0. $|b| = 1$\\
For $a = 4$, $b$ (4 + 1) = $5b$. So, $b = \{0,3,6,9,12\}$. $|b| = 5$.\\
For $a = 11$, $b$ (11 + 1) = $12b$. $b = \{0,5,10\}$. $|b| = 3$.\\
For $a = 14$, $b$ (14 + 1) = $15b$. $b$ can take any value from $\mathbb{Z}_{15}$. $|b| = 15$.\\
$\therefore$ Total no. of involutory keys = 1 + 5 + 3 + 15 = \textbf{24}.
\end{large}
\end{document}

### 2019-08-28 MTech/CS553/HW2/python_code/Euclidean_gcd.py

@@ -1,0 +1,18 @@
+def E_gcd(a,b): # function to calculate Euclidean GCD
+    a,b = (b,a) if a < b else (a,b) # swaps a and b if a < b
+    while True:
+        r = a % b
+        if (r == 0):
+            break
+        a = b
+        b = r
+    return b
+
+
+try: # to allow only integer input
+    a,b = [int(i)for i in(input("Enter two integers: ").split(" "))]
+except ValueError:
+    print("Please enter two integers!")
+    exit(0)
+
+print(E_gcd(a,b))

### 2019-08-28 MTech/CS553/HW3/HW3_11910230.tex
HW3: Adding assignment 3 for CS553

\documentclass[12pt]{article}

\usepackage[a4paper, left = 2cm, right = 2cm, top = 2cm, bottom = 2cm]{geometry}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{graphicx}

\usepackage{listings}
\usepackage{xcolor}
\lstset{
	language = Python,
	backgroundcolor=\color{black!5}, % set backgroundcolor
}

\renewcommand{\baselinestretch}{1.5}

\renewcommand\thesection{\arabic{section}.}

\usepackage{tocloft}
\cftsetindents{section}{0em}{2em}
\cftsetindents{subsection}{0em}{2em}
\renewcommand\cfttoctitlefont{\hfill\Large\bfseries}
\renewcommand\cftaftertoctitle{\hfill\mbox{}}
\setcounter{tocdepth}{2}

%\title{CS553: Cryptography \\
%		Assignment 3 - Solutions\\\vspace{1cm}}
%\author{Rohit Das (11910230)}

\begin{document}
%\maketitle
%\newpage
\begin{titlepage}
\centering
\vspace*{\fill}
\huge CS553: Cryptography\\
\LARGE Assignment 3: Solutions\\
\Large Rohit Das (11910230)\\\vspace{0.8cm}
\today
\vspace*{\fill}
\end{titlepage}

\section{CCA-Security}
\begin{large}

Formally, for any list of plaintexts $m_1,m_2,...,m_n \in \mathcal{P}$ and ciphertexts $c_1,c_2,...,c_n$ $\in \mathcal{C}$ chosen by adversary, even with knowledge of corresponding ciphertexts $e_K(m_1)$, $e_K(m_2),...,e_K(m_n)$ and corresponding plaintexts $d_K(c_1),d_K(c_2),...,d_K(c_n)$, it is very difficult to decrypt any ciphertext not present in the above list of ciphertexts without knowing the key.
\end{large}

\section{Hill Cipher}
\begin{large}
\subsection{Encryption}
Name: ROHIT DAS. First four letters = \{R,O,H,I\} = \{17,14,7,8\} [$\because$ taking A = 0, B = 1 and so on].
Then $x$ = 
$\begin{pmatrix}
17&14\\7&8
\end{pmatrix}$.
Given key K = $\begin{pmatrix}
11&8\\3&7
\end{pmatrix}$,\\ 
ciphertext $y$ = $xK$ = 
$\begin{pmatrix}
17&14\\7&8
\end{pmatrix}
\times
\begin{pmatrix}
11&8\\3&7
\end{pmatrix}$ mod 26\\
= $\begin{pmatrix}
17\times11+14\times3 & 17\times8+14\times7\\
7\times11+8\times3 & 7\times8+8\times7
\end{pmatrix}$ mod 26
= $\begin{pmatrix}
21&0\\23&8
\end{pmatrix}$
= \{V,A,X,I\}.\\
$\therefore y = e_K(x)$ = VAXI.

\subsection{Inverse Key}
$|K|$ = $11\times7-3\times8$ mod 26 = 53 mod 26 = 1.\\
Adjoint of K
= $\begin{pmatrix}
7&-8\\-3&11
\end{pmatrix}$.
$\therefore K^{-1}$
= $\dfrac{1}{|K|}\times$ Adjoint of K 
=$\begin{pmatrix}
7&-8\\-3&11
\end{pmatrix}$

\subsection{Invertible?}
K can be said to be invertible only if $|K| \ne$ 0. Since $|K|$ = 53 $\ne$ 0, K is invertible.

\subsection{Decryption}
We calculated y
= $\begin{pmatrix}
21&0\\23&8
\end{pmatrix}$. Now, $x$ = $d_K(y)$ = $yK^{-1}$.\\
$\therefore y$
=$\begin{pmatrix}
21&0\\23&8
\end{pmatrix}
\begin{pmatrix}
7&-8\\-3&11
\end{pmatrix}$
=$\begin{pmatrix}
21\times7+0\times(-3) & 21\times(-8)+0\times11\\
23\times7+8\times(-3) & 23\times(-8)+8\times11
\end{pmatrix}$mod 26\\
= $\begin{pmatrix}
147&-168\\137&-96
\end{pmatrix}$ mod 26
= $\begin{pmatrix}
17&14\\7&8
\end{pmatrix}$ = \{R,O,H,I\}.\\
$\therefore x$ = $d_K(y)$ = ROHI.

\end{large}

\section{Theorem(Perfect Secrecy): Proof}
\begin{large}
\subsection{Proof 1:}
Suppose the given cryptosystem provides perfect secrecy. If \textbf{Pr}$[x_0]$ = 0, for some $x_0 \in \mathcal{P}$, it trivially follows that \textbf{Pr}$[x_0|y]$ = \textbf{Pr}$[x_0]$ for all $y \in \mathcal{C}$. Hence, we will only consider those plaintext elements where \textbf{Pr}$[x_0] >$ 0. Hence, it follows, using Bayes' theorem, that \textbf{Pr}$[x|y]$ = \textbf{Pr}$[x]$ $\forall y \in \mathcal{C}$ is equivalent to \textbf{Pr}$[y|x]$ = \textbf{Pr}$[y]$ $\forall y \in \mathcal{C}$.

Assuming \textbf{Pr}$[y] >$ 0 $\forall y \in \mathcal{C}$ ($\because$ if \textbf{Pr}$[y]$ = 0, then y is never used and can be omitted here), if we fix any $x \in \mathcal{P}$, for each $y \in \mathcal{C}$, \textbf{Pr}$[y|x]$ = \textbf{Pr}$[y] >$ 0. Hence, there must be at least one key K such that $e_K(x)$ = $y$ . It follows that $|\mathcal{K}| > |\mathcal{C}|$. So we have the inequalities
\begin{center}
$|\mathcal{C}| = |\{e_K(x):K \in \mathcal{K}\}| \le$ $|\mathcal{K}|$.
\end{center}
But since we are assuming $|\mathcal{C}| = |\mathcal{K}|$ [$\because$ perfect secrecy],
\begin{center}
$|\{e_K(x):K \in \mathcal{K}\}|$ = $|\mathcal{K}|$.
\end{center}
This shows that there doesn't exist two keys $K_1$ and $K_2$ such that $e_{K_1}(x)$ = $e_{K_2}(x)$. Hence, there is only one unique key K such that $e_K(x)$ = $y$. \textbf{(Proved)}

\subsection{Proof 2:}
Let $n$ = $|\mathcal{K}|$. Let $\mathcal{P}$ = \{$x_i:1 \le i \le n$\} and fix a ciphertext element $y \in \mathcal{C}$. Then the keys will be $K_1, K_2,...,K_n$ such that $e_{K_i}(x_i)$ = $y$, $1 \le i \le n$. Using Bayes' theorem,

\begin{align*}
\textbf{Pr}[x_i|y] &= \dfrac{\textbf{Pr}[y|x_i]\textbf{Pr}[x_i]}{\textbf{Pr}[y]}\\
& = \dfrac{\textbf{Pr}[\textbf{K} = K_i]\textbf{Pr}[x_i]}{\textbf{Pr}[y]}
\end{align*}
[$\because$ probability of getting $y$ given $x_i$ is equal to probability of using $K_i$ as key]

Considering perfect secrecy, \textbf{Pr}$[x_i|y]$ = \textbf{Pr}$[x_i]$. From here, it follows that \textbf{Pr}$[K_i]$ = \textbf{Pr}$[y]$. for $1 \le i \le n$. This says that all keys are used with equal probability \textbf{Pr}$[y]$. But since number of keys is $|\mathcal{K}|$, we must have \textbf{Pr}$[K_i]$ = $\dfrac{1}{|\mathcal{K}|}$. \textbf{(Proved)}

\end{large}

\section{Perfect Secrecy?}
\begin{large}

One-time Pad, or OTP is a one-time key used to encrypt a message in Vernam Cipher. The problem with using an OTP more than once is as follows:\\
Suppose our OTP is $K$. Let $m_1,m_2$ and $m_3$ be our messages. Then $c_1 = m_1 \oplus K$, $c_2 = m_2 \oplus K$ and $c_2 = m_3 \oplus K$. Now, if our attacker obtains even one pair of plaintext and ciphertext, the encryption is broken. Lets assume that $c_2$ and $m_2$ is obtained by attacker. Then attacker can simply XOR both of them to obtain the OTP.
\begin{center}
$m_2 \oplus c_2$ = $m_2 \oplus (m_2 \oplus K)$ = $K$.
\end{center}
Thus, this cipher becomes KPA-vulnerable if OTP is used more than once. \textbf{(Proved)}

\end{large}

\section{Hill Vs Permutation}
\begin{large}
Permutation cipher is a special form of Hill Cipher, i.e. the permutations can be represented by a key matrix consisting of 0's and 1's, 1 representing the position of the symbol in permutation. E.g.:\\
Let message block size $m$ = 6, and a possible key is the permutation $\pi$:
\begin{center}
\begin{tabular}{c||c|c|c|c|c|c}
$x$ & 1 & 2 & 3 & 4 & 5 & 6\\[0.05ex]\hline
$\pi(x)$ & 3 & 5 & 1 & 6 & 4 & 2\\[0.05ex]
\end{tabular}
\end{center}
Thus, $\pi$(ROHITDASXXXX) = HXDXRATXOSIX.\\
This can be represented by a $6\times6$ key matrix $K$:\\
\begin{center}
\begingroup % keep the change local
\setlength\arraycolsep{10pt}
$K$ = $\begin{pmatrix}
0&0&1&0&0&0\\
0&0&0&0&1&0\\
1&0&0&0&0&0\\
0&0&0&0&0&1\\
0&0&0&1&0&0\\
0&1&0&0&0&0\\
\end{pmatrix}$ 
,i.e. $k_{i,j}$ 
= $\begin{cases}
1 \text{ if } j = \pi(i)\\
0 \text{ otherwise}
\end{cases}$\\
\endgroup
\end{center}
Encryption of message $m$ = ROHITDASXXXX (18,15,8,9,20,4,1,19,24,24,24,24):\\
$x$ = 
$\begin{pmatrix}
R&O&H&I&T&D\\
A&S&X&X&X&X
\end{pmatrix}$
 = $\begin{pmatrix}
18&15&8&9&20&4\\
1&19&24&24&24&24
\end{pmatrix}$ \\
cipher text $y$ = $xK$
= $\begin{pmatrix}
18&15&8&9&20&4\\
1&19&24&24&24&24
\end{pmatrix}
\begin{pmatrix}
0&0&1&0&0&0\\
0&0&0&0&1&0\\
1&0&0&0&0&0\\
0&0&0&0&0&1\\
0&0&0&1&0&0\\
0&1&0&0&0&0\\
\end{pmatrix}
\\=
\begin{pmatrix}
8&4&18&20&15&9\\
24&24&1&24&19&24
\end{pmatrix}$
= 
$\begin{pmatrix}
H&D&R&T&O&I\\
X&X&A&X&S&X
\end{pmatrix}$ = HXDXRATXOSIX.

\end{large}
\end{document}

### 2019-08-28 MTech/CS553/HW4/python_code/Random_s-box_gen.py
hw2.pdf: Added questions for assignment 2

@@ -1,0 +1,24 @@
+import numpy as np
+
+def rn_box(n): # random permutation of input symbols
+    arr = [hex(int(i)) for i in np.arange(n)]# hex symbols
+    # mapping each symbol to its random substitute
+    return {i:j for i,j in zip(arr,
+                               np.random.permutation(arr))}
+
+def main(sbox): # takes plaintext and performs confusion
+    p = input("Enter your plaintext:")
+    if not all(x in [format(i,'x') for i in sbox] 
+               for x in p):# checking if in range [0-f]
+        exit("Enter valid characters[0-f]!")
+    str1 = {format(i,'x'):format(j,'x') for i,j 
+    in sbox.items()}
+    return "".join([str1[i] for i in p])
+
+sbox = {0x0: 0x5, 0x1: 0x4, 0x2: 0xd, 0x3: 0x1, 0x4: 0x2, 
+        0x5: 0xf, 0x6: 0x6, 0x7: 0x0, 0x8: 0x8, 0x9: 0xc, 
+        0xa: 0xb, 0xb: 0x9, 0xc: 0x7, 0xd: 0xe, 0xe: 0xa, 
+        0xf: 0x3} # generated using rn_box(int)
+        
+# print(rn_box(16)) # to generate a random s-box
+print(main(sbox))

### 2019-09-20 MTech/CS553/HW4/python_code/DDT_s-box2.py
DDT_s-box2.py: Added code for testing

@@ -1,0 +1,48 @@
+from collections import Counter
+
+sbox1 = {0x0: 0x8, 0x1: 0x6, 0x2: 0x7, 0x3: 0x9, 0x4: 0x3, 
+        0x5: 0xc, 0x6: 0xa, 0x7: 0xf, 0x8: 0xd, 0x9: 0x1, 
+        0xa: 0xe, 0xb: 0x4, 0xc: 0x0, 0xd: 0xb, 0xe: 0x5, 
+        0xf: 0x2} # S-Box produced earlier
+
+sbox2 = {0x0: 0xc, 0x1: 0x6, 0x2: 0x7, 0x3: 0x9, 0x4: 0x4, 
+        0x5: 0x8, 0x6: 0xa, 0x7: 0xf, 0x8: 0x5, 0x9: 0x1, 
+        0xa: 0xe, 0xb: 0x3, 0xc: 0x0, 0xd: 0xb, 0xe: 0xd, 
+        0xf: 0x2}
+
+sbox3 = {0x0: 0xc, 0x1: 0x6, 0x2: 0x7, 0x3: 0x9, 0x4: 0x3, 
+        0x5: 0x8, 0x6: 0xa, 0x7: 0xf, 0x8: 0x5, 0x9: 0x1, 
+        0xa: 0xe, 0xb: 0x4, 0xc: 0x0, 0xd: 0xb, 0xe: 0xd, 
+        0xf: 0x2}
+
+def ddt(sbox):
+    # lst1 = [format(i,'x') for i,j in sbox.items()]
+    # print("in\\out|", ("{:>3}"*len(lst1)).format(*lst1)) 
+    # print('-'*56)
+    countlist = {}
+    for diff in sbox:
+        u1 = [hex(i^diff) for i in sbox]
+        S_u0 = [hex(j) for i,j in sbox.items()] # S[u0]
+        S_u1 = [hex(sbox[(int(i,0))]) for i in u1] # S[u1]
+        S_u0_x_S_u1 = [hex(int(i,0)^int(j,0)) for i,j 
+        in zip(S_u0,S_u1)] # S[u0] xor S[u1]
+        # counting occurences and replacing 0 with '-'
+        count = {hex(i):'-' if S_u0_x_S_u1.count(hex(i)) 
+        == 0 else S_u0_x_S_u1.count(hex(i)) for i in sbox}        
+        # format output as a table
+        lst = [str(i) for j,i in count.items()]
[…]

### 2019-09-20 MTech/CS553/HW5/python_code/DDT_s-box2.py
HW5: Added files for hw5

@@ -1,0 +1,53 @@
+from collections import Counter
+
+sbox1 = {0x0: 0x8, 0x1: 0x6, 0x2: 0x7, 0x3: 0x9, 0x4: 0x3, 
+        0x5: 0xc, 0x6: 0xa, 0x7: 0xf, 0x8: 0xd, 0x9: 0x1, 
+        0xa: 0xe, 0xb: 0x4, 0xc: 0x0, 0xd: 0xb, 0xe: 0x5, 
+        0xf: 0x2} # S-Box produced earlier
+
+sbox2 = {0x0: 0xc, 0x1: 0x6, 0x2: 0x7, 0x3: 0x9, 0x4: 0x4, 
+        0x5: 0x8, 0x6: 0xa, 0x7: 0xf, 0x8: 0x5, 0x9: 0x1, 
+        0xa: 0xe, 0xb: 0x3, 0xc: 0x0, 0xd: 0xb, 0xe: 0xd, 
+        0xf: 0x2}
+
+# sbox3 = {0x0: 0xc, 0x1: 0x6, 0x2: 0x7, 0x3: 0x9, 0x4: 0x3, 
+#         0x5: 0x8, 0x6: 0xa, 0x7: 0xf, 0x8: 0x5, 0x9: 0x1, 
+#         0xa: 0xe, 0xb: 0x4, 0xc: 0x0, 0xd: 0xb, 0xe: 0xd, 
+#         0xf: 0x2}
+
+# sbox1 = {0x0: 0x6, 0x1: 0x4, 0x2: 0xc, 0x3: 0x5, 0x4: 0x0, 
+#         0x5: 0x7, 0x6: 0x2, 0x7: 0xe, 0x8: 0x1, 0x9: 0xf, 
+#         0xa: 0x3, 0xb: 0xd, 0xc: 0x8, 0xd: 0xa, 0xe: 0x9, 
+#         0xf: 0xb}
+
+def ddt(sbox):
+    lst1 = [format(i,'x') for i,j in sbox.items()]
+    print("in\\out|", ("{:>3} &"*len(lst1)).format(*lst1)) 
+    print('-'*56)
+    countlist = {}
+    for diff in sbox:
+        u1 = [hex(i^diff) for i in sbox]
+        S_u0 = [hex(j) for i,j in sbox.items()] # S[u0]
+        S_u1 = [hex(sbox[(int(i,0))]) for i in u1] # S[u1]
+        S_u0_x_S_u1 = [hex(int(i,0)^int(j,0)) for i,j 
[…]

### 2019-09-20 MTech/CS553/HW5/python_code/conform_msg.py

@@ -1,0 +1,75 @@
+# messages taken as input from input.txt
+import numpy as np
+import sys
+
+# orig_stdout = sys.stdout
+# f = open('output_cnfrm.txt','w')
+# sys.stdout = f
+
+sbox1 ={0x0: 0x6, 0x1: 0x4, 0x2: 0xc, 0x3: 0x5, 0x4: 0x0, 
+        0x5: 0x7, 0x6: 0x2, 0x7: 0xe, 0x8: 0x1, 0x9: 0xf, 
+        0xa: 0x3, 0xb: 0xd, 0xc: 0x8, 0xd: 0xa, 0xe: 0x9, 
+        0xf: 0xb}
+
+def sbox_4x(msg, bits): # 4-input sbox
+    if len(msg) != int(bits,0):# check for message length 
+        exit("Plaintext size should be of " + bits + " bits")
+    subs = []
+    for m in msg: # check for invalid literal
+        if m not in [format(i,'x') for i in sbox1]:
+            exit("Invalid literal")
+        subs.append(format(sbox1[int(m,16)],'x'))
+    return subs
+
+def pbox(sbox_out,bits):
+    if len(sbox_out) != int(bits,0):
+        exit("Too small sbox output!!")
+    perm = [b for a in sbox_out # changing hex to binary
+            for b in list("{0:04b}".format(int(a,16)))]
+    # pbox = sbox output in numpy array and transposing
+    perm = np.asarray(perm)
+    perm = np.reshape(perm,(4,4)).transpose()
+    return "".join([format(int("".join(a),2),'x') 
+                   for a in perm])
+
+def sypher004(msg, bits): 
+    # uncomment below lines for more verbose output
+    # keys = ['c253','0466','affe','645e','0509','fff2'] # keys
+    keys = ['340b','3ffc','edfd','8c7d','0696','ffff']
+    if len(msg) != int(bits,0):
+        exit("Plaintext size should be of " 
+             + bits + " bits")
+    #print("Round 0:",msg)
+    msg = "{:04x}".format(int(msg,16) ^ int(keys[0],16),'x')
+    #print("Round 0 (XOR) :","{0:016b}".format(int(msg,16)))
+
+    for i in range(1,len(keys) - 1):
+        msg = "".join(sbox_4x(msg,bits))
+        # print("Round",str(i),"(Sbox):","{0:016b}"
+        # .format(int(msg,16)))
+        msg = pbox(msg,bits)
+        # print("Round",str(i),"(Perm):","{0:016b}"
[…]

### 2019-09-20 MTech/CS553/HW5/python_code/sample_prog.py

@@ -1,0 +1,15 @@
+perm = []
+for x in range(2 ** 16):
+    strx = "{:04x}".format(x,'x')
+    # if strx not in perm:
+    #     perm.append(strx)
+    xored = "{:04x}".format(int(strx,16)^int('8000',16),'x')
+        # if xored not in perm:
+            #perm.append(xored)
+    print(strx,xored)
+# print(perm)
+
+# with open("./output_cnfrm.txt") as file:
+#     for i,l in enumerate(file):
+#         pass
+# print(i + 1)

### 2019-09-20 MTech/CS553/HW5/python_code/sypher002.py

@@ -1,0 +1,55 @@
+sbox1 = {0x0: 0x6, 0x1: 0x4, 0x2: 0xc, 0x3: 0x5, 0x4: 0x0, 
+        0x5: 0x7, 0x6: 0x2, 0x7: 0xe, 0x8: 0x1, 0x9: 0xf, 
+        0xa: 0x3, 0xb: 0xd, 0xc: 0x8, 0xd: 0xa, 0xe: 0x9, 
+        0xf: 0xb}
+
+k0 = 0x4
+k1 = 0xe
+k2 = 0x6
+
+def sbox(p):
+    if p not in [format(i,'x') for i in sbox1]:
+        exit("Invalid literal")
+    return sbox1[int(p,16)]
+
+def sbox_inv(c):
+    for i,j in sbox1.items():
+        if c == j:
+            return format(i,'x')
+
+def sypher002(p):
+    return sbox1[sbox1[p^k0]^k1]^k2
+
+def diff_crypt():
+    k2_list = []
+    for i in range(8):
+        c0 = sypher002(i)
+        c1 = sypher002(i^int('f',16))
+        # print(c0,c1)
+        temp = []
+        for k2_ in sbox1:
+            x0 = c0^k2_
+            x1 = c1^k2_
+            w0 = sbox_inv(x0)
+            w1 = sbox_inv(x1)
+            temp.append(1 if format(int(w0,16)^int(w1,16),'x') == 'd' else 0)
+        k2_list.append(temp)
+        print(temp)    
+    
+    return k2_list
+
+#p = input("Enter plaintext:")
+#print(format(sbox(input("Enter plaintext:")),'x'))
+#print(sypher002('f'))
+#print(sbox_inv(p))
+k = diff_crypt()
+
+lst = [0] * 16
+for i in k:
+    for j in range(len(i)):
+        lst[j] += i[j]
+
+print(lst)
+# print(type(p))
+# for i in sbox1:
+#     print(hex(i))

### 2019-09-20 MTech/IC601/Assgnt2_Ppr_Rvw/Paper_Review.tex
Modified Review

@@
 \begin{itemize}
-\item A very well-summarized overview of what Adversarial Machine Learning is, why it is necessary and relevant in this age, and how it can be accomplished.
+\item A good overview of Adversarial Machine Learning and its impact in the field of modern Artificial Intelligence.
 
@@
 
-\item The two algorithms used as case studies are very much used in real life situations, and hence makes the paper very relevant in this day and age, thereby easily underlining the need for the topic researched on.
+\item The two algorithms used as case studies are very much used in real life situations, and hence makes the paper very relevant in today's new age of Artificial Intelligence, thereby easily underlining the need for the topic researched on.
 
@@
 It aptly highlights the necessity and relevance of securing learning models, especially when they will be planned to be used in mission-critical situations.
-However, a more generous use of images would've helped illustrate the attacks and countermeasures better.
+However, the organization of the paper could be improved by including more references in the analyses.
 %

### 2019-09-20 MTech/CS553/HW2/HW2_11910230.tex
HW2: Made corrections to answers

@@
 $\therefore \mathbb{Z}^{+}_{23} = \{0,1,...,22\}$\\
-Let $K$ be the set of possible keys, such that $\forall	k \in K$, gcd($r,k$) $= 1$.\\
-So, given $r = 23$, $K = \{1,2,...,22\}$.\\
-$\mathbf{\therefore |K| = 22}$.
+Let $K = (a,b)$ be the set of possible keys, such that $\forall	k \in K$, gcd($r,a$) $= 1$.\\
+So, given $r = 23$, $a = \{1,2,...,22\}$. $\therefore |a| = 22$. Similarly, $b = \{0,1,...,22\}$. $\therefore |b| = 23$. $\mathbf{\therefore |K| = 22\times 23 = 506}$.
 \end{large}
@@
 Euler Phi Function, also known as Euler's totient function, returns the count of integers less than and relatively prime to n. It is denoted by $\phi(n)$.\\
-For prime positive integers, $\phi(n) = (n - 1)$. For other positive integers, if $n = pq$, where p,q $\in \mathbb{Z}^{+}$ and prime, $\phi(n) = (p - 1)(q - 1)$.\\
+For prime positive integers, $\phi(n) = (n - 1)$.
+For other positive integers, if $n = pq$, where p,q $\in \mathbb{Z}^{+}$ and prime, $\phi(n) = (p - 1)(q - 1)$.
+In general, Euler's phi function can be written as:
+\begin{center}
+$\phi(n) = n\displaystyle\prod_{p|n}\left(1 - \dfrac{1}{p}\right)$
+\end{center}
+
 The number of keys, $|K|$, for an Affine Cipher defined over $\mathbb{Z}^{+}_{r}$ can be easily obtained by simply using Euler's totient function $\phi(r)$.\\
-Since our $r$ is prime, $\phi(r) = (r - 1) = 22$.
+Since our $r$ is prime, $\phi(r) = (r - 1) = 22$. Given $|b| = 23$, $\mathbf{|K| = 22 \times 23 = 506}$.
 \end{large}

### 2019-09-23 MTech/CS553/HW3/HW3_11910230.tex
HW3: Made corrections in Q2

@@
 \subsection{Inverse Key}
-$|K|$ = $11\times7-3\times8$ mod 26 = 53 mod 26 = 1.\\
+$|K|$ = $(11\times7-3\times8)$ mod 26 = 53 mod 26 = 1.\\
 Adjoint of K
@@
 $\therefore K^{-1}$
-= $\dfrac{1}{|K|}\times$ Adjoint of K 
+= $\left( \dfrac{1}{|K|}\times \text{Adjoint of K} \right)$ mod 26
+
 =$\begin{pmatrix}
 7&-8\\-3&11
+\end{pmatrix}$ mod 26
+=$\begin{pmatrix}
+7&18\\23&11
 \end{pmatrix}$
@@
 \subsection{Invertible?}
-K can be said to be invertible only if $|K| \ne$ 0. Since $|K|$ = 53 $\ne$ 0, K is invertible.
+K can be said to be invertible only if $|K| \ne$ 0 and $gcd(|K|,26) = 1$. Since $|K|$ = 53 $\ne$ 0 and $gcd(53,26) = 1$, K is invertible.
 
@@
 \begin{pmatrix}
-7&-8\\-3&11
+7&18\\23&11
 \end{pmatrix}$
 =$\begin{pmatrix}
-21\times7+0\times(-3) & 21\times(-8)+0\times11\\
-23\times7+8\times(-3) & 23\times(-8)+8\times11
+21\times7+0\times23 & 21\times18+0\times11\\
+23\times7+8\times23 & 23\times18+8\times11
 \end{pmatrix}$mod 26\\
 = $\begin{pmatrix}
-147&-168\\137&-96
+147&378\\137&502
 \end{pmatrix}$ mod 26

### 2019-09-24 MTech/CS553/HW6/python_code/LAT_s-box.py
HW6: Added .tex and .py files

@@ -1,0 +1,37 @@
+from functools import reduce
+from operator import xor
+import numpy as np
+
+sbox = {0x0: 0x5, 0x1: 0x4, 0x2: 0xd, 0x3: 0x1, 0x4: 0x2, 
+       0x5: 0xf, 0x6: 0x6, 0x7: 0x0, 0x8: 0x8, 0x9: 0xc, 
+       0xa: 0xb, 0xb: 0x9, 0xc: 0x7, 0xd: 0xe, 0xe: 0xa, 
+       0xf: 0x3}
+
+def lat(sbox):
+    lst1 = [format(i,'x') for i,j in sbox.items()]
+    print("in\\out|",("{:>3}"*len(lst1[1:])).format(*lst1[1:])) 
+    print('-'*56)
+
+    lat_dict = {} # to store count for each mask
+    for alpha in range(1,16):
+        for beta in range(1,16):
+            lat_dict[beta] = 0
+
+            for x,sx in sbox.items():
+                x_arr = np.array([int(i) for i in # x . alpha
+                        list('{:04b}'.format(x & alpha,'b'))])
+                sx_arr = np.array([int(i) for i in # sx . beta
+                        list('{:04b}'.format(sx & beta,'b'))])
+                if reduce(xor,x_arr) == reduce(xor,sx_arr):
+                    lat_dict[beta] += 1
+        
+        lst2 = [str(int((j/16-0.5)*16)) for i,j in 
+        lat_dict.items()] # eps = p - 1/2
+        lst2 = list(map(lambda b:b.replace('0','.'),lst2))
+        
+        # formatting table
+        frmt = "{:>3}"*len(lst2)
+        print(str(format(alpha,'x')+'  |').rjust(7),
+              frmt.format(*lst2))
+
+lat(sbox)

### 2019-09-24 MTech/CS553/HW6/python_code/LC_Sypher00C.py

@@ -1,0 +1,101 @@
+from functools import reduce
+from operator import xor
+import numpy as np
+
+sbox1 = {0x0: 0xf, 0x1: 0xe, 0x2: 0xb, 0x3: 0xc, 0x4: 0x6, 
+       0x5: 0xd, 0x6: 0x7, 0x7: 0x8, 0x8: 0x0, 0x9: 0x3, 
+       0xa: 0x9, 0xb: 0xa, 0xc: 0x4, 0xd: 0x2, 0xe: 0x1, 
+       0xf: 0x5}
+
+keys = list('6fec') # generated using openssl rand -hex 2
+mask = int('d',16) # mask d has highest bias
+
+def sbox(p):
+    if format(p,'x') not in [format(i,'x') for i in sbox1]:
+        exit("Invalid literal")
+    return sbox1[p]
+
+def sbox_inv(c):
+    for i,j in sbox1.items():
+        if c == int(format(j,'x'),16):
+            return int(format(i,'x'),16)
+
+def Sypher00C(p,n):
+    for i in range(n):
+        p = sbox(p ^ int(keys[i],16))
+    return p ^ int(keys[-1],16)
+
+def lin_crypt_k3():
+    sum = [0]*16
+    print("k3 =",keys[-1])
+    frmt = "{:>3}"*len(sum)
+    print("Guesses",frmt.format(*[format(i,'x') 
+                                for i in range(16)]))
+
+    for p in range(16):
+        c = Sypher00C(p,3)
+        lst = []
+        for k in range(16):
+            y_ = sbox_inv(c ^ k)
+            # mask & p and then changing to binary list
+            p_ = np.array([int(i) 
+                for i in list('{:04b}'.format(p & mask,'b'))])
+            
+            # mask & y' and then changing to binary list
+            c_ = np.array([int(i) 
+                for i in list('{:04b}'.format(y_ & mask,'b'))])
+            
+            # (d.m) xor (d.y')
+            xored = reduce(xor,p_) ^ reduce(xor,c_)
+            lst.append(xored)
+        
+        sum = [i+j for i,j in zip(lst,sum)]
+        print((format(p,'x')+'-'+format(c,'x')).ljust(5),
+              '|'.rjust(1),frmt.format(*lst))
+
+    print("T0---> ",frmt.format(*[16-i for i in sum]))
+    print("T1---> ",frmt.format(*sum))
+    candidates = [i for i,j in enumerate(sum) if j == max(sum) 
+    or j == min(sum)]
+    candidates.sort()
[…]

### 2019-10-16 MTech/CS607/Paper Review/Paper_Review.tex
Paper Review: Added Paper Review for 1809.02077

--- 2019-09-20 MTech/IC601/Assgnt2_Ppr_Rvw/Paper_Review.tex
@@
 \usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
-\linespread{1.035} % Line spacing - Palatino needs more space between lines
+\linespread{0.96} % Line spacing - Palatino needs more space between lines
 \usepackage{microtype} % Slightly tweak font spacing for aesthetics
@@
 
-\usepackage[hmarginratio=1:1,top=18mm,bottom=18mm,left=12mm,
-right=12mm,columnsep=15pt]{geometry} % Document margins
+\usepackage[hmarginratio=1:1,top=15.5mm,bottom=18mm,left=12mm,
+right=12mm,columnsep=14pt]{geometry} % Document margins
 
@@
 \posttitle{\end{center}} % Article title closing formatting
-\title{A Review of\\ Adversarial Machine Learning\\ 
-\huge{(4th ACM Workshop on AISec, Oct. 2011,43-58)}} % Article title
+\title{A Review of\\ IDSGAN: Generative Adversarial Networks for Attack Generation against Intrusion Detection} % Article title
 \author{%
@@
 \large M. Tech. (CSE)\\
-Reviewers: Dr. Sk Subidh Ali, and Dr. Subhajit Sidhanta
-}
+Reviewer: Dr. Sk Subidh Ali}
 \date{\today} % Leave empty to omit a date
@@
 
-\lettrine[nindent=0em,lines=3]{T} he manuscript by Huang et.
-al.
-focuses primarily on the security fault lines in modern Machine Learning, how they can be utilized to break into secure learning systems, and manipulate data and users.
-It also sequentially outlines how such situations can be avoided by keeping some points in mind while designing a new or improving an existing learning algorithm or model, forming the crux of Adversarial Machine Learning.
+\lettrine[nindent=0em,lines=3]{T} he manuscript by Lin, Shi and Xue outlines how a Generative Adversarial Network (GAN) was developed to generate adversarial malicious network data and successfully evade any black-box intrusion detection system (IDS).
+The manuscript aims to fill a void in research into attacks on IDS, and particularly the use of GANs in such attacks.
 
@@
 \begin{itemize}
-\item A good overview of Adversarial Machine Learning and its impact in the field of modern Artificial Intelligence.
 
-\item Taxonomy of influence, security violations and specificity of attack by a potential adversary on a learning system.
+\item An overview of why IDSGAN is necessary to build robust intrusion detection systems, and highlights on the lack of work done in IDS evasion, specifically using GANs.
 
-\item Modeling secure learning systems as a game between an attacker and a defender, and how both can influence the learning algorithm, learning and evaluation of data, as well as the data itself.
-It also subtly creates the idea that a learning model can be made more robust by artificially creating an adversary and training the model with it.
+\item A brief explanation of why Wasserstein GAN was preferred over other variants or the vanilla GAN, and outlines how the GAN architecture had been used to train the generator to generate adversarial data.
 
-\item An elaborate section on Causative attacks to learning systems, well-documented with graphs and data.
-It also contains case studies on two algorithms: SpamBayes and Principal Component Analysis (PCA)-based anomalous network traffic detector.
-The authors have highlighted the strengths of an attacker given certain degrees of freedom, and how they can be countered.
+\item Usage of a benchmark dataset, NSL-KDD, consisting of network data for both normal and malicious traffic, which had been divided to be separately fed into the black-box IDS and the GAN discriminator and generator.
 
-\item A section on Exploratory attacks, discussing various evasion techniques, theoretical and practical, and how the most optimum evasion techniques are not the ones generally implemented in real time.
+\item Visual representations of the modified architecture of Wasserstein GAN used for training the generator.
+It also specifies the layers used in the generator to add noise to the malicious data from the dataset.
 
-\item Privacy violations, and advantages and roles of randomization of functions and parameters in learning models.
+\item Detailed layout of the discriminator and generator, the role of a black-box IDS in helping to train the discriminator and eventually the generator to evade the black-box.
+Also provided are the training algorithms, pseudo code for the same, loss functions and formulae used.
+
+\item Extensive supporting data and graphs to throw light on how current IDSs are vulnerable to adversarial attacks and how the GAN framework developed was successful in evading most models used as a black-box.
+
 \end{itemize}
@@
 \begin{itemize}
+
+\item The paper has been aimed to contribute to the field of intrusion detection and evasion, and has successfully presented that current IDSs are nowhere near being secure against adversarial attacks.
+
 \item All conclusions, facts and experiments have been well-supported with relevant data and graphs.
-The graphs clearly highlight the differences between using a robust and a non-secure learning model.
+The graphs clearly highlight how the IDSGAN was successful in evading all the models used for the black-box.
 
-\item The paper mainly focuses on causative attacks, the most malicious of attacks, and extensive research has been done into its types, variants and countermeasures.
+\item Using the predicted output labels of the black-box as target labels for the discriminator in the Wasserstein GAN used was an innovative way to train the discriminator with parameters having values as close as possible to those of the black-box.
+This helped the generator to train and accordingly add noises to malicious examples that successfully evade the IDS.
 
-\item The two algorithms used as case studies are very much used in real life situations, and hence makes the paper very relevant in today's new age of Artificial Intelligence, thereby easily underlining the need for the topic researched on.
+\item All equations, formulae and algorithms mentioned have been lucidly presented such that even with basic knowledge, the paper can be understood and appreciated.
 
-\item Privacy, being a trending concept throughout history and a fundamental human right, is also a part of this paper, and makes it a must-read for researchers in this field.
 \end{itemize}
@@
 \section{Limitations}
+The limitations of the paper are listed below:
 \begin{itemize}
-\item A section on image and pattern recognition, and how adversaries can trick such models, could have been made a part of the research, as it is a budding novel area in Machine Learning, and specifically, Deep Learning.
-\item The paper is a bit too textual. Adding more images would have helped better illustrate the various attacks and countermeasures presented here.
+
+\item The paper has clearly not been proof-read adequately.
+It is filled with grammatical errors.
+Often the sentences are too garbled to make out the true meaning, and other times, some words have been morphed such that the actual meaning of the sentence changes.
+
+\item There are also informational errors, occurring while describing the values in NSL-KDD, errors in images and pseudo-code, which could have been avoided.
+Also, some parts of the text has been left in ambiguity.
+
+\item Since the dataset has less data under U2R and R2L categories of attacks, the paper's claim that the GAN has successfully evaded IDS with those attacks is trivial and weak.
+
 \end{itemize}
@@
 \section{Opinion}
-~~~~~The paper gives a good introduction and an elaborate explanation on Adversarial Machine Learning, and how to counter it.
-It aptly highlights the necessity and relevance of securing learning models, especially when they will be planned to be used in mission-critical situations.
-However, the organization of the paper could be improved by including more references in the analyses.
+~~~~~While the idea and solution presented here is novel and standard procedures for experiments and data representation have been used, the paper itself is of average quality filled with mistakes and errors, easily avoidable had it been proof-read properly.
 %

### 2020-01-20 cv/cv-sections/education.tex
resume_cv.tex: Removed position, changed grad years
cv.pdf: Added MTech Creds
Added marks for MTech at IIT Bhilai, and details of my project on
Edge computing.

@@
 \cventry
+{M. Tech.  in Computer Science and Engineering} % Degree
+{Indian Institute of Technology, Bhilai} % Institution
+{GEC Campus, Old Dhamtari Rd, Sejbahar, Chhattisgarh - 492015} % Location
+{Jul. 2019 - Present} % Date(s)
+{ % Description(s) bullet points
+\begin{cvitems}
+\item {CGPA (2019-20 S) - 9.75}
+\item {Currently working on Data Science using Edge Computing}
+\item {Outreach (Placement and Training) Cell Volunteer}
+\end{cvitems}
+}
+
+%------------------------------------------------
+
+\cventry
 {B. Tech.  in Computer Science and Engineering} % Degree
@@
 Kolkata - 700064.} % Location
-{Jul. 2014 - PRESENT} % Date(s)
+{Jul. 2014 - Jul. 2018} % Date(s)
 { % Description(s) bullet points
 \begin{cvitems}
-\item {CGPA(till 7th Semester) - 7.93}
+\item {DGPA - 8.11}
 \item {Got cleared under TFW scheme (Tuition-Fee Waiver scheme) meant for students ranking well in WBJEE.}
@@
 \item {Indian School Certificate Examination (ISC) score - 95.33\%.}
-\end{cvitems}
-}
-
-%------------------------------------------------
-
-\cventry
-{Secondary Education} % Degree
-{Don Bosco School, Bandel} % Institution
-{Bandel, P. O. \& Dist. Hooghly - 712103.} % Location
-{Apr. 2002 - Mar. 2012} % Date(s)
-{ % Description(s) bullet points
-\begin{cvitems}
-\item {Indian Certificate of Secondary Education (ICSE) score  - 93.71\%.}
 \item {Qualified for Anant Scholarship, provided to meritorious students passing class 10 or equivalent.}
@@
 
+%\cventry
+%{Secondary Education} % Degree
+%{Don Bosco School, Bandel} % Institution
+%{Bandel, P. O. \& Dist. Hooghly - 712103.} % Location
+%{Apr. 2002 - Mar. 2012} % Date(s)
+%{ % Description(s) bullet points
+%\begin{cvitems}
+%\item {Indian Certificate of Secondary Education (ICSE) score  - 93.71\%.}
+%\end{cvitems}
+%}
+
+%------------------------------------------------
+
 \end{cventries}

### 2020-08-12 MTech/CS553/HW7/HW7_11910230.tex
Adding HW7

\documentclass[12pt]{article}

\usepackage[a4paper, left = 1.5cm, right = 1.5cm, top = 1.5cm, bottom = 1.5cm]{geometry}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{pgfplots}
\usepackage{pgfplotstable}
\pgfplotsset{width=15cm,height=7cm,compat=newest}
\usepgfplotslibrary{fillbetween}

\usepackage{mathtools}

\usepackage{enumitem}

\usepackage{graphicx}

\usepackage{diagbox}

\usepackage{karnaugh-map}

\usepackage[T1]{fontenc}

\usepackage{listings}
\usepackage{xcolor}
\usepackage{colortbl}

\usepackage{tabu}

\lstset{
	language = Python,
	backgroundcolor=\color{black!5}, % set backgroundcolor
	breaklines=true,
	postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
}

\renewcommand{\baselinestretch}{1.5}

\renewcommand\thesection{\arabic{section}.}

\usepackage{tocloft}
\cftsetindents{section}{0em}{2em}
\cftsetindents{subsection}{0em}{2em}
\renewcommand\cfttoctitlefont{\hfill\Large\bfseries}
\renewcommand\cftaftertoctitle{\hfill\mbox{}}
\setcounter{tocdepth}{2}

\begin{document}
\begin{titlepage}
\centering
\vspace*{\fill}
\huge CS553: Cryptography\\
\LARGE Assignment 7: Solutions\\
\Large Rohit Das (11910230)\\\vspace{0.8cm}
\today
\vspace*{\fill}
\end{titlepage}

\section{Mix-Column Transitions}

Python Code (Python3): AES.py
\lstinputlisting[language=Python,showstringspaces=false]{./python_code/AES.py}
\vspace{0.05cm}

\newpage
\section{Integral Distinguisher}

Python Code (Python3): integral$\_$crypt.py
\lstinputlisting[language=Python,showstringspaces=false]{./python_code/integral_crypt.py}
\vspace{0.05cm}
\textbf{Output:}
Row: 1, Col: 1, Key: 1234
\lstinputlisting[showstringspaces=false]{./python_code/integral_output.txt}

\newpage
\section{Fault Tolerance: Sypher004}

Python Code (Python3): Sypher004.py
\lstinputlisting[language=Python,showstringspaces=false]{./python_code/Sypher004.py}
\vspace{0.05cm}
Output:
IV: 1234. Message: 1234abcd.
\lstinputlisting[showstringspaces=false]{./python_code/Sypher004output.txt}
\vspace{0.05cm}

\newpage
\section{Modes}

\subsection{ECB Encryption}
Bash Script File: enc$\_$pic.sh
\lstinputlisting[language=Bash,showstringspaces=false]{./ECB_Pic/enc_pic.sh}
\vspace{0.05cm}

\begin{figure}[h!]

\centering\includegraphics[width = 0.45\linewidth]{./ECB_Pic/IITBhilaiLogo.png}
\centering\includegraphics[width = 0.45\linewidth]{./ECB_Pic/IITBhilaiLogoEnc.png}

\caption{Left: Original IIT Bhilai Logo. Right: Encrypted using aes-256-cbc}

\end{figure}

\subsection{Need for Pre-IV}

In CBC and CFB modes of encryption, being able to predict the IV will lead to leaking the message itself. To make the IV unpredictable, a notion of Pre-IV is used. It can be a nonce generated from a counter, which is then encrypted to create the IV.

\begin{center}

$IV = ENC_k$(PRE-IV)

\end{center}
Other theoretical works suggest using some key k' derived from k that is used for encryption.
\begin{center}

$IV = ENC_{k'}$(PRE-IV)

\end{center}

\begin{large}

\end{large}

\end{document}

### 2020-08-12 MTech/CS553/HW7/ECB_Pic/enc_pic.sh

@@ -1,0 +1,7 @@
+identify IITBhilaiLogo.png
+convert -depth 32 IITBhilaiLogo.png IITBhilaiLogo.rgba
+openssl aes-256-ecb -nosalt -in IITBhilaiLogo.rgba -out 
+IITBhilaiLogoEnc.rgba
+pass: 'CS553'
+convert -size 400x400 -depth 32 IITBhilaiLogoEnc.rgba 
+IITBhilaiLogoEnc.png

### 2020-08-12 MTech/CS553/HW7/python_code/AES.py

@@ -1,0 +1,161 @@
+import numpy as np
+
+sbox =  [0x63, 0x7c, 0x77, 0x7b, 0xf2, 0x6b, 0x6f, 0xc5, 0x30, 0x01, 0x67,
+            0x2b, 0xfe, 0xd7, 0xab, 0x76, 0xca, 0x82, 0xc9, 0x7d, 0xfa, 0x59,
+            0x47, 0xf0, 0xad, 0xd4, 0xa2, 0xaf, 0x9c, 0xa4, 0x72, 0xc0, 0xb7,
+            0xfd, 0x93, 0x26, 0x36, 0x3f, 0xf7, 0xcc, 0x34, 0xa5, 0xe5, 0xf1,
+            0x71, 0xd8, 0x31, 0x15, 0x04, 0xc7, 0x23, 0xc3, 0x18, 0x96, 0x05,
+            0x9a, 0x07, 0x12, 0x80, 0xe2, 0xeb, 0x27, 0xb2, 0x75, 0x09, 0x83,
+            0x2c, 0x1a, 0x1b, 0x6e, 0x5a, 0xa0, 0x52, 0x3b, 0xd6, 0xb3, 0x29,
+            0xe3, 0x2f, 0x84, 0x53, 0xd1, 0x00, 0xed, 0x20, 0xfc, 0xb1, 0x5b,
+            0x6a, 0xcb, 0xbe, 0x39, 0x4a, 0x4c, 0x58, 0xcf, 0xd0, 0xef, 0xaa,
+            0xfb, 0x43, 0x4d, 0x33, 0x85, 0x45, 0xf9, 0x02, 0x7f, 0x50, 0x3c,
+            0x9f, 0xa8, 0x51, 0xa3, 0x40, 0x8f, 0x92, 0x9d, 0x38, 0xf5, 0xbc,
+            0xb6, 0xda, 0x21, 0x10, 0xff, 0xf3, 0xd2, 0xcd, 0x0c, 0x13, 0xec,
+            0x5f, 0x97, 0x44, 0x17, 0xc4, 0xa7, 0x7e, 0x3d, 0x64, 0x5d, 0x19,
+            0x73, 0x60, 0x81, 0x4f, 0xdc, 0x22, 0x2a, 0x90, 0x88, 0x46, 0xee,
[…]

### 2020-08-12 MTech/CS553/HW7/python_code/Sypher004.py

@@ -1,0 +1,146 @@
+import numpy as np
+
+sbox1 ={0x0: 0x6, 0x1: 0x4, 0x2: 0xc, 0x3: 0x5, 0x4: 0x0, 
+        0x5: 0x7, 0x6: 0x2, 0x7: 0xe, 0x8: 0x1, 0x9: 0xf, 
+        0xa: 0x3, 0xb: 0xd, 0xc: 0x8, 0xd: 0xa, 0xe: 0x9, 
+        0xf: 0xb}
+
+def sbox_4x(msg, bits): # 4-input sbox
+    if len(msg) != bits:# check for message length 
+        exit("Input size should be of " + format(4*bits) + " bits")
+    subs = []
+    for m in msg: # check for invalid literal
+        if m not in [format(i,'x') for i in sbox1]:
+            exit("Invalid literal")
+        subs.append(format(sbox1[int(m,16)],'x'))
+    return subs
+
+def sbox_4x_inv(cipher, bits):
+    if len(cipher) != bits:# check for message length 
+        exit("Input size should be of " + format(4*bits) + " bits")
+    subs = []
+    for c in cipher:
+        if c not in [format(i,'x') for i in sbox1.values()]:
+            exit("Invalid literal")
+        for _c,m in sbox1.items():
+            if c == format(m,'x'):
+                subs.append(format(_c,'x'))
+    return subs
+
+def pbox(sbox_out,bits):
+    if len(sbox_out) != bits:
+        exit("Too small sbox output!!")
+    perm = [b for a in sbox_out # changing hex to binary
+            for b in list("{0:04b}".format(int(a,16)))]
+    # pbox = sbox output in numpy array and transposing
+    perm = np.asarray(perm)
+    perm = np.reshape(perm,(4,4)).transpose()
+    return "".join([format(int("".join(a),2),'x') 
+                   for a in perm])
+
+def sypher004(msg, bits):
+    if len(msg) != bits:# check for message length 
+        exit("Plaintext size should be of " + format(4*bits) + " bits")
+
+    keys = ['340b','3ffc','edfd','8c7d','0696','ffff']
+    msg = "{:04x}".format(int(msg,16) ^ int(keys[0],16),'x')
+
+    for i in range(1,len(keys) - 1):
+        msg = "".join(sbox_4x(msg,bits))
[…]

### 2020-08-12 MTech/CS553/HW7/python_code/integral_crypt.py

@@ -1,0 +1,104 @@
+import numpy as np
+import AES # imports from AES.py
+
+def makeIntegral(r,c): # creates an integral 3D list
+    integral_state = np.arange(16*256,dtype=object).reshape(256,4,4)
+    random = np.random.randint(0,256,16)
+
+    for i in range(256):
+        l = 0
+        for j in range(4):
+            for k in range(4):
+                if j == r + 1 and k == c + 1:
+                    integral_state[i][j - 1][k - 1] = "{:02x}".format(i,'x')
+# filling other bytes with random constants, same for all 256 states
+                else:
+                    integral_state[i][j - 1][k - 1] = "{:02x}".format(random[l],'x')
+                    l += 1
+    return integral_state
+
+def isAll(a): # prints 2D list with All bytes marked
+    isAllList = np.empty([4,4],dtype=str)
+    for j in range(4):
+        for k in range(4):
+            isAllFlag = True
+            n = [i for i in range(256)]
+            for i in range(256):
+                if int(a[i][j][k],16) not in n:
+                    isAllFlag = False
+                else:
+                    n[int(a[i][j][k],16)] = -1
+                    isAllFlag = True
+            
+            if isAllFlag == True:
+                isAllList[j][k] = 'A'
+            else:
+                isAllList[j][k] = ''
+
+    return isAllList
+
+def isConst(a): # prints 2D list with Constant bytes marked
+    isConstList = np.empty([4,4],dtype=str)
+    for j in range(4):
+        for k in range(4):
+            isConstFlag = True
+            for i in range(256):
+                # checks if all bytes are same
+                if a[i][j][k] != a[0][j][k]:
+                    isConstFlag = False
+                else:
+                    isConstFlag = True
+            
+            if isConstFlag == True:
+                isConstList[j][k] = 'C'
+            else:
+                isConstList[j][k] = ''
+
+    return isConstList
+
+def isBalanced(a): # prints 2D list with Balanced bytes marked
+    isBalancedList = np.empty([4,4],dtype=str)
+    for j in range(4):
+        for k in range(4):
+            isBalancedFlag = 0
+            for i in range(256):
+                isBalancedFlag = isBalancedFlag ^ int(a[i][j][k],16)
+            
+            if isBalancedFlag == 0:
+                isBalancedList[j][k] = 'B'
+            else:
+                isBalancedList[j][k] = ''
+
[…]

### 2020-08-12 MTech/CS553/HW8/HW8_11910230.tex
Adding HW8

\documentclass[12pt]{article}

\usepackage[a4paper, left = 1.5cm, right = 1.5cm, top = 1.5cm, bottom = 1.5cm]{geometry}

\usepackage{tikz}
\usetikzlibrary{positioning,fit,calc}
\tikzset{block/.style={draw,thick,text width=2cm,minimum height=1cm,align=center},
         line/.style={-latex}
}
\tikzstyle{arrow} = [thick,->,>=stealth]

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{hyperref}
\hypersetup {
	colorlinks=true,
	urlcolor=blue
}

\usepackage{pgfplots}
\usepackage{pgfplotstable}
\pgfplotsset{width=15cm,height=7cm,compat=newest}
\usepgfplotslibrary{fillbetween}

\usepackage{mathtools}

\usepackage{enumitem}

\usepackage{graphicx}
\usepackage{float}

\usepackage{diagbox}

\usepackage{karnaugh-map}

\usepackage[T1]{fontenc}

\usepackage{listings}
\usepackage{xcolor}
\usepackage{colortbl}

\usepackage{tabu}

\lstset{
	language = Python,
	backgroundcolor=\color{black!5}, % set backgroundcolor
	breaklines=true,
	postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
}

\renewcommand{\baselinestretch}{1.5}

\renewcommand\thesection{\arabic{section}.}

\usepackage{tocloft}
\cftsetindents{section}{0em}{2em}
\cftsetindents{subsection}{0em}{2em}
\renewcommand\cfttoctitlefont{\hfill\Large\bfseries}
\renewcommand\cftaftertoctitle{\hfill\mbox{}}
\setcounter{tocdepth}{2}

\begin{document}
\begin{titlepage}
\centering
\vspace*{\fill}
\huge CS553: Cryptography\\
\LARGE Assignment 8: Solutions\\
\Large Rohit Das (11910230)\\\vspace{0.8cm}
\today
\vspace*{\fill}
\end{titlepage}

\begin{large}

\section{Authenticated Encryption Schemes}

\begin{enumerate}

\item \textbf{Nyberg and Rueppel Scheme}: It is an application of their signature scheme, which was the first discrete logarithm based scheme with message recovery.

\item \textbf{Keyak}: It is a scheme based on Keccak-p. It takes as input a secret and unique value (SUV), then some associated data (or metadata) that are authenticated but not encrypted and finally some plaintext.

\item \textbf{Wu and Hsu's Convertible Scheme}: A new authenticated encryption scheme with (t,n) shared verification based on discrete logarithms was proposed.

\item \textbf{Hwang's AE Scheme with Message Linkage}: To reduce costs for redundancies in message blocks, the scheme is divided into two parts, generation of signature and encryption phase, and recovery message and verification phase.

\item \textbf{Galois/Counter Mode (GCM) for Block Ciphers}: It is an authenticated encryption algorithm designed to provide both data authenticity and integrity.

\item \textbf{Carter-Wegman Counter Mode (CWC)}: It combines the use of CTR mode for encryption with an efficient polynomial Carter-Wegman MAC.

\item \textbf{Tiaoxin-346}: It is a nonce-based scheme, taking 4 inputs: Key K (128 bits), public nonce IV (128 bits), plaintext M (0 to $2 ^ {128}$ - 1 bits) and associated data AD (0 to $2 ^ {128}$ - 1 bits).

\item \textbf{Offset Codebook Mode (OCB)}: It is essentially a scheme to integrate a MAC into the operation of a block cipher.

\item \textbf{EAX}: It is an AEAD scheme designed to simultaneously provide both authenticity and privacy with a two-pass scheme.

\item \textbf{Sophie Germain Counter Mode (SGCM)}: Instead of the binary field $GF(2^{128})$, it used modular arithmetic in $GF(p)$, where $p$ is a safe prime $2^{128} + 12451$ with corresponding Sophie Germain prime $\dfrac{p-1}{2} = 2^{127} + 6225$.

\end{enumerate}

\section{Hash: Mode-of-operation + collision}

\subsection{Pg. 315, Problem 11.3}

%\includegraphics[width = 0.45\linewidth]{./images/img1.jpg}
%\hspace{0.05\linewidth} \includegraphics[width = 0.45\linewidth]{./images/img2.jpg}\\
%
%\includegraphics[scale=•]{•} = 0.45\linewidth]{./images/img3.jpg}\\

\begin{tikzpicture}

\node[block] (block) {$e$};
\node[draw=none,above=of block] (msg) {$x_i$};
\node[draw=none,left=0.5cm of block] (prevhash) {$H_{i - 1}$};
\node[draw=none,below=0.5cm of block] (xor) {$\oplus$};
\node[draw=none,below=0.5cm of xor] (hash) {$H_i$};
\node[draw=none,below=1cm of hash] (caption) {$1.$ $ e(H_{i-1},x_i)\oplus x_i$};
\draw[arrow] (msg)--(block);
\draw[arrow] (prevhash)--(block);
\draw[arrow] (block)--(xor);
\draw[arrow] (xor)--(hash);
\draw[arrow] (0,1)-|(1.5,0)|-(xor);

\end{tikzpicture}
\hspace{0.25\linewidth}
\begin{tikzpicture}

\node[block] (block) {$e$};
\node[draw=none,above=0.5cm of block] (xora) {$\oplus$};
\node[draw=none,above=0.5cm of xora] (msg) {$x_i$};
\node[draw=none,left=0.75cm of block] (prevhash) {$H_{i - 1}$};
\node[draw=none,below=0.5cm of block] (xor) {$\oplus$};
\node[draw=none,below=0.5cm of xor] (hash) {$H_i$};
\node[draw=none,below=1cm of hash] (caption) {$2.$ $ e(H_{i-1},x_i \oplus H_{i-1})\oplus x_i \oplus H_{i-1}$};
\draw[arrow] (msg)--(xora);
\draw[arrow] (xora)--(block);
\draw[arrow] (prevhash)--(block);
\draw[arrow] (block)--(xor);
\draw[arrow] (xor)--(hash);
\draw[arrow] (0,2)-|(1.5,0)|-(xor);
\draw[arrow] (-1.5,0)|-(xora);
\draw[arrow] (-1.5,0)|-(xor);

\end{tikzpicture}

\vspace{0.75cm}
\begin{tikzpicture}

\node[block] (block) {$e$};
\node[draw=none,above=of block] (msg) {$x_i$};
\node[draw=none,left=0.75cm of block] (prevhash) {$H_{i - 1}$};
\node[draw=none,below=0.5cm of block] (xor) {$\oplus$};
\node[draw=none,below=0.5cm of xor] (hash) {$H_i$};
\node[draw=none,below=0.75cm of hash] (caption) {$3.$ $ e(H_{i-1},x_i)\oplus x_i \oplus H_{i-1}$};
\draw[arrow] (msg)--(block);
\draw[arrow] (prevhash)--(block);
\draw[arrow] (block)--(xor);
\draw[arrow] (xor)--(hash);
\draw[arrow] (0,1)-|(1.5,0)|-(xor);
\draw[arrow] (-1.5,0)|-(xor);

\end{tikzpicture}
\hspace{0.15\linewidth}
\begin{tikzpicture}

\node[block] (block) {$e$};
\node[draw=none,above=0.5cm of block] (xora) {$\oplus$};
\node[draw=none,above=0.5cm of xora] (msg) {$x_i$};\node[draw=none,left=0.75cm of block] (prevhash) {$H_{i - 1}$};
\node[draw=none,below=0.5cm of block] (xor) {$\oplus$};
\node[draw=none,below=0.5cm of xor] (hash) {$H_i$};
\node[draw=none,below=0.75cm of hash] (caption) {$4.$ $ e(H_{i-1},x_i \oplus H_{i-1})\oplus x_i$};
\draw[arrow] (msg)--(xora);
\draw[arrow] (xora)--(block);
\draw[arrow] (prevhash)--(block);
\draw[arrow] (block)--(xor);
\draw[arrow] (xor)--(hash);
\draw[arrow] (-1.5,0)|-(xora);
\draw[arrow] (0,2)-|(1.5,0)|-(xor);

\end{tikzpicture}

\vspace{0.75cm}
\begin{tikzpicture}

\node[block] (block) {$e$};
\node[draw=none,left=0.5cm of block] (msg) {$x_i$};
\node[draw=none,above=0.75cm of block] (prevhash) {$H_{i - 1}$};
\node[draw=none,below=0.5cm of block] (xor) {$\oplus$};
\node[draw=none,below=0.5cm of xor] (hash) {$H_i$};
\node[draw=none,below=0.75cm of hash] (caption) {$5.$ $ e(x_i,H_{i-1})\oplus H_{i-1}$};
\draw[arrow] (msg)--(block);
\draw[arrow] (prevhash)--(block);
\draw[arrow] (block)--(xor);
\draw[arrow] (xor)--(hash);
\draw[arrow] (0,1)-|(1.5,0)|-(xor);

\end{tikzpicture}
\hspace{0.25\linewidth}
\begin{tikzpicture}

\node[block] (block) {$e$};
\node[draw=none,left=of block] (msg) {$x_i$};
\node[draw=none,above=0.5cm of block] (xora) {$\oplus$};
\node[draw=none,above=0.5cm of xora] (prevhash) {$H_{i - 1}$};
\node[draw=none,below=0.5cm of block] (xor) {$\oplus$};
\node[draw=none,below=0.5cm of xor] (hash) {$H_i$};
\node[draw=none,below=0.75cm of hash] (caption) {$6.$ $ e(x_i,x_i \oplus H_{i-1})\oplus x_i \oplus H_{i-1}$};
\draw[arrow] (prevhash)--(xora);
\draw[arrow] (xora)--(block);
\draw[arrow] (msg)--(block);
\draw[arrow] (block)--(xor);
\draw[arrow] (xor)--(hash);
\draw[arrow] (0,2)-|(1.5,0)|-(xor);
\draw[arrow] (-1.5,0)|-(xora);
\draw[arrow] (-1.5,0)|-(xor);

\end{tikzpicture}

\vspace{0.75cm}
\begin{tikzpicture}

\node[block] (block) {$e$};
\node[draw=none,left=0.75cm of block] (msg) {$x_i$};
\node[draw=none,above=0.75cm of block] (prevhash) {$H_{i - 1}$};
\node[draw=none,below=0.5cm of block] (xor) {$\oplus$};
\node[draw=none,below=0.5cm of xor] (hash) {$H_i$};
\node[draw=none,below=0.75cm of hash] (caption) {$7.$ $ e(x_i,H_{i-1})\oplus x_i \oplus H_{i-1}$};
\draw[arrow] (msg)--(block);
\draw[arrow] (prevhash)--(block);
\draw[arrow] (block)--(xor);
\draw[arrow] (xor)--(hash);
\draw[arrow] (0,1)-|(1.5,0)|-(xor);
\draw[arrow] (-1.5,0)|-(xor);

\end{tikzpicture}
\hspace{0.20\linewidth}
\begin{tikzpicture}

\node[block] (block) {$e$};
\node[draw=none,above=0.5cm of block] (xora) {$\oplus$};
\node[draw=none,left=0.75cm of block] (msg) {$x_i$};
\node[draw=none,above=0.5cm of xora] (prevhash) {$H_{i - 1}$};
\node[draw=none,below=0.5cm of block] (xor) {$\oplus$};
\node[draw=none,below=0.5cm of xor] (hash) {$H_i$};
\node[draw=none,below=0.75cm of hash] (caption) {$8.$ $ e(x_i,x_i \oplus H_{i-1})\oplus H_{i-1}$};
\draw[arrow] (prevhash)--(xora);
\draw[arrow] (xora)--(block);
\draw[arrow] (msg)--(block);
\draw[arrow] (block)--(xor);
\draw[arrow] (xor)--(hash);
\draw[arrow] (0,2)-|(1.5,0)|-(xor);
\draw[arrow] (-1.5,0)|-(xora);

\end{tikzpicture}

\vspace{0.75cm}
\begin{tikzpicture}

\node[block] (block) {$e$};
\node[draw=none,left=0.5cm of block] (xora) {$\oplus$};
\node[draw=none,above=of block] (msg) {$x_i$};
\node[draw=none,left=0.5cm of xora] (prevhash) {$H_{i - 1}$};
\node[draw=none,below=0.5cm of block] (xor) {$\oplus$};
\node[draw=none,below=0.5cm of xor] (hash) {$H_i$};
\node[draw=none,below=0.75cm of hash] (caption) {$9.$ $ e(x_i \oplus H_{i-1},x_i)\oplus x_i$};
\draw[arrow] (msg)--(block);
\draw[arrow] (prevhash)--(xora);
\draw[arrow] (xora)--(block);
\draw[arrow] (block)--(xor);
\draw[arrow] (xor)--(hash);
\draw[arrow] (0,1)-|(1.5,0)|-(xor);
\draw[arrow] (0,1)-|(xora);

\end{tikzpicture}
\hspace{0.10\linewidth}
\begin{tikzpicture}

\node[block] (block) {$e$};
\node[draw=none,left=0.5cm of block] (xora) {$\oplus$};
\node[draw=none,left=0.5cm of xora] (msg) {$x_i$};
\node[draw=none,above=0.75cm of block] (prevhash) {$H_{i - 1}$};
\node[draw=none,below=0.5cm of block] (xor) {$\oplus$};
\node[draw=none,below=0.5cm of xor] (hash) {$H_i$};
\node[draw=none,below=0.75cm of hash] (caption) {$10.$ $ e(x_i \oplus H_{i-1},H_{i-1})\oplus H_{i-1}$};
\draw[arrow] (msg)--(xora);
\draw[arrow] (xora)--(block);
\draw[arrow] (prevhash)--(block);
\draw[arrow] (block)--(xor);
\draw[arrow] (xor)--(hash);
\draw[arrow] (0,1)-|(1.5,0)|-(xor);
\draw[arrow] (0,1)-|(xora);

\end{tikzpicture}

\vspace{0.75cm}
\begin{tikzpicture}

\node[block] (block) {$e$};
\node[draw=none,left=0.5cm of block] (xora) {$\oplus$};
\node[draw=none,above=0.75cm of block] (msg) {$x_i$};
\node[draw=none,left=0.65cm of xora] (prevhash) {$H_{i - 1}$};
\node[draw=none,below=0.5cm of block] (xor) {$\oplus$};
\node[draw=none,below=0.5cm of xor] (hash) {$H_i$};
\node[draw=none,below=0.75cm of hash] (caption) {$11.$ $ e(x_i \oplus H_{i-1},x_i)\oplus H_{i-1}$};
\draw[arrow] (prevhash)--(xora);
\draw[arrow] (xora)--(block);
\draw[arrow] (msg)--(block);
\draw[arrow] (block)--(xor);
\draw[arrow] (xor)--(hash);
\draw[arrow] (0,1)-|(xora);
\draw[arrow] (-2.75,0)|-(xor);

\end{tikzpicture}
\hspace{0.075\linewidth}
\begin{tikzpicture}

\node[block] (block) {$e$};
\node[draw=none,left=0.5cm of block] (xora) {$\oplus$};
\node[draw=none,left=0.75cm of xora] (msg) {$x_i$};
\node[draw=none,above=0.75cm of block] (prevhash) {$H_{i - 1}$};
\node[draw=none,below=0.5cm of block] (xor) {$\oplus$};
\node[draw=none,below=0.5cm of xor] (hash) {$H_i$};
\node[draw=none,below=0.75cm of hash] (caption) {$12.$ $ e(x_i \oplus H_{i-1},H_{i-1})\oplus x_i$};
\draw[arrow] (msg)--(xora);
\draw[arrow] (xora)--(block);
\draw[arrow] (prevhash)--(block);
\draw[arrow] (block)--(xor);
\draw[arrow] (xor)--(hash);
\draw[arrow] (0,1)-|(xora);
\draw[arrow] (-2.75,0)|-(xor);

\end{tikzpicture}

\newpage
\subsection{Pg. 316, Problem 11.8}

Python Code (Python3): hashing.py
\lstinputlisting[language=Python,showstringspaces=false]{./python_code/hashing.py}
Output: The hash function can be broken by choosing such characters whose bits will XOR out to be the XOR of bits of the target character. E.g., "CRYPTO" hashes to 110011, which is the same for "FINALE". The crucial property missing in this hash function is the second-preimage resistance,i.e., given a message $M_1$, we are easily able to find another message $M_2$ hashing to the same value as $M_1$.
\begin{lstlisting}
String: CRYPTO
Binary: 01000011 01010010 01011001 01010000 01010100 01001111 
Hash: 110011
String: FINALE
Binary: 01000110 01001001 01001110 01000001 01001100 01000101 
Hash: 110011
\end{lstlisting}

\section{Partial Collision: md5}

The list of $2^{16}$ pairs of strings and their corresponding hashes was generated 4 times to find collision in the first and last 16 bits of the hash. Hence, the total number of trials stands at $2^{18}$ = 262144. The strings have been generated randomly and hence may not form meaningful sentences.\\
Python Code (Python3): md5hash.py
\lstinputlisting[language=Python,showstringspaces=false]{./python_code/md5hash.py}
Output:\\
\includegraphics[width=\linewidth]{./images/img3.png}

\section{SSL Certificates: X509 Format}

\subsection{About X.509}

X.509 is a standard defining the format of public key certificates. An X.509 certificate contains a public key and an identity, and is either signed by a certificate authority, or self-signed.

In this system, an organization that wants a signed certificate requests one via a certificate signing request (CSR). To do this, it first generates a key pair, keeping the private key secret and using it to sign the CSR. This contains information identifying the applicant and the applicant's public key that is used to verify the signature of the CSR - and the Distinguished Name (DN) that the certificate is for. The CSR may be accompanied by other credentials or proofs of identity required by the certificate authority.

There are several commonly used filename extensions for X.509 certificates. Some of these extensions are also used for other data such as private keys.

\begin{itemize}

\item .pem - (Privacy-enhanced Electronic Mail) Base64 encoded DER certificate, enclosed between "-----BEGIN CERTIFICATE-----" and "-----END CERTIFICATE-----"

\item .cer, .crt, .der - usually in binary DER form, but Base64-encoded certificates are common too (see .pem above)

\item .p7b, .p7c - PKCS\# 7 SignedData structure without data, just certificate(s) or CRL(s)

\item .p12 - PKCS\# 12, may contain certificate(s) (public) and private keys (password protected)

\item .pfx - PFX, predecessor of PKCS\# 12 (usually contains data in PKCS\# 12 format, e.g., with PFX files generated in IIS)

\end{itemize}

\subsection{SSL verification}

Command to download SSL certificate from www.facebook.com:
\begin{lstlisting}
openssl s_client -connect www.facebook.com:443 2>/dev/null </dev/null |  openssl x509 -outform PEM > fb_cert.pem
\end{lstlisting}
\vspace{0.25cm}
Command to verify SHA-1 fingerprint of above certificate:
\begin{lstlisting}
openssl x509 -noout -in fb_cert.pem -fingerprint -sha1
\end{lstlisting}
\vspace{0.25cm}
Generated Fingerprint:\\
SHA1 Fingerprint=A4:27:D4:9C:21:BD:B6:E4:52:B3:F8:D6:DE:25:79:3A:8C:0E:45:2A\\

\begin{figure}[H]
\centering
\includegraphics[width = 0.70\linewidth]{./images/img2.png}
\caption{Screenshot from Google Chrome browser of actual fingerprint}
\end{figure}

\section{MAC: Timing Attacks}

Python Code (Python3): timing$\_$attack.py
\lstinputlisting[language=Python,showstringspaces=false]{./python_code/timing_attack.py}
Output:

\begin{figure}[H]
\centering
\includegraphics[width = 0.62\linewidth]{./images/img1.png}

\caption{As evident from the screenshot, for compare$\_$mac(), comparing identical strings takes more time than for different strings. However, it is not so distinguishable in const$\_$compare$\_$mac().}

\end{figure}

\end{large}

\end{document}

### 2020-08-12 MTech/CS553/HW8/python_code/hashing.py

@@ -1,0 +1,12 @@
+from functools import reduce
+
+def hashing(msg): 
+    print("String:",msg)
+    print("Binary:",''.join(['{:08b}'.format(ord(m),'b') + ' ' for m in msg]))
+    hashed = ''
+    for m in msg:
+        hashed += str(reduce(lambda i,j: int(i) ^ int(j), format(ord(m),'b')))
+    print("Hash:",hashed)
+
+hashing('CRYPTO') # 110011
+hashing('FINALE')

### 2020-08-12 MTech/CS553/HW8/python_code/md5hash.py

@@ -1,0 +1,41 @@
+# please run the code more than once to generate the collision
+
+import string
+import random
+import hashlib
+import os
+
+def random_string(n): # to generate random string having letters and digits
+    return ''.join(random.choices(string.ascii_letters + string.digits + ' ', k = n))
+
+def hash_list(n,t): # to create a list of string and its hash
+    ctr = 0
+    str_hash = []
+    for i in range(2 ** 16):
+        str1 = random_string(n)
+        hash1 = hashlib.md5(str1.encode()).hexdigest()
+        list1 = []
+        list1.append(str1)
+        list1.append(hash1)
+        str_hash.append(list1)
+    return str_hash
+
+def find_collision(n,t): # looking for collision in hash_list
+    str_hash = hash_list(n,t)
+
+    str_hash.sort(key = lambda x: x[1])
+
+    file1 = open('string1.txt','w')
+    file2 = open('string2.txt','w')
+
+    for i in range(len(str_hash) - 1):
+        if str_hash[i][1][:4] == str_hash[i + 1][1][:4] and str_hash[i][1][-4:] == str_hash[i + 1][1][-4:]:
+            print(str_hash[i][0],str_hash[i][1])
+            file1.write(str_hash[i][0])
+
+            print(str_hash[i + 1][0],str_hash[i + 1][1])
+            file2.write(str_hash[i + 1][0])
+    file1.close()
+    file2.close()
+
+find_collision(100,4)

### 2020-08-12 MTech/CS553/HW8/python_code/timing_attack.py

@@ -1,0 +1,32 @@
+from time import time
+
+def compare_mac(x, y, n):
+    for i in range(n):
+        if x[i] != y[i]:
+            return False
+    return True
+
+def const_compare_mac(x,y,n):
+    result = 0
+    for i in range(n):
+        result |= ord(x[i]) ^ ord(y[i])
+    return result
+
+def timing_measure(mac1,mac2,trials,compare_mac):
+    # each call checks the whole string 
+    print("Using ",compare_mac.__name__,":")
+    start = time()
+    for i in range(trials):
+        compare_mac(mac1,mac1,len(mac1))
+    end = time()
+    print('For same string: %0.5fs' % (end - start))
+
+    # each call checks only till mismatch appears    
+    start = time()
+    for i in range(trials):
+        compare_mac(mac1,mac2,len(mac1))
+    end = time()
+    print('For different string: %0.5fs' % (end - start))
+
+timing_measure('0123456789abcdef','01X3456789abcdef',100000,compare_mac)
+timing_measure('0123456789abcdef','01X3456789abcdef',100000,const_compare_mac)

### 2020-08-12 MTech/CS525/Project/CS525_Proj.tex
Adding Project Report

\documentclass[a4paper,12pt]{article}

\renewcommand\thesection{\arabic{section}.}

\usepackage{tocloft}
\cftsetindents{section}{0em}{2em}
\cftsetindents{subsection}{0em}{2em}
\renewcommand\cfttoctitlefont{\hfill\Large\bfseries}
\renewcommand\cftaftertoctitle{\hfill\mbox{}}
\setcounter{tocdepth}{2}

\usepackage{listings}
\usepackage{xcolor}

\usepackage{fullpage}

\usepackage{float}

\usepackage{amsfonts}

\usepackage{titlesec}
\titlelabel{\thetitle.\quad}

\usepackage{sectsty}
\sectionfont{\fontsize{14}{15}\selectfont}

% to remove numbering in section, but not in subsections
\renewcommand{\thesection}{}
\renewcommand{\thesubsection}{\arabic{section}.\arabic{subsection}}
\makeatletter
\def\@seccntformat#1{\csname #1ignore\expandafter\endcsname\csname the#1\endcsname\quad}
\let\sectionignore\@gobbletwo
\let\latex@numberline\numberline
\def\numberline#1{\if\relax#1\relax\else\latex@numberline{#1}\fi}
\makeatother

\setcounter{tocdepth}{4}
\setcounter{secnumdepth}{4}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[left=1.75cm,right=1.75cm,top=2cm,bottom=1cm,includefoot,headsep=0.1in]{geometry}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\cfoot{\thepage}

\usepackage{booktabs}
\usepackage{tabularx}

\usepackage[hidelinks]{hyperref}
\renewcommand{\refname}{\large CHAPTER 6: REFERENCES}
\usepackage[nottoc,numbib]{tocbibind}

%\usepackage{array}
%\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

\lstset { %
	% basicstyle=\ttfamily,
  	% columns=fullflexible,
  	% frame=single,
  	breaklines=true,
  	postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
    language=python,
    backgroundcolor=\color{black!5}, % set backgroundcolor
    basicstyle=\large,% basic font setting
}

\newcommand*{\plogo}{\fbox{$\mathcal{PL}$}} % Generic publisher logo

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\newcommand*{\titleGM}{\begingroup % Create the command for including the title page in the document
\hbox{ % Horizontal box
\hspace*{0.15\textwidth} % Whitespace to the left of the title page
\rule{1pt}{\textheight} % Vertical line
\rule{1pt}{\textheight}
\hspace*{0.03\textwidth} % Whitespace between the vertical line and title page text
\parbox[b]{0.75\textwidth}{ % Paragraph box which restricts text to less than the width of the page

{\noindent\Huge\bfseries Project Report}\\[2\baselineskip] % Title
{\large \textit{-supervised by:}\\\\\Large \textsc Dr. Ratan K. Ghosh\\\\Dr. Subhajit Sidhanta}\\[4\baselineskip] % Tagline or further description

{\large \textit{-submitted by:}\\\\\Large \textsc{Rohit Das \large{(11910230), and}}} % Author name
{\\\\\Large \textsc{Shoumik Ghosal \large{(11910300)}}} % Author name
\vspace{15em} % Whitespace between the title block and the publisher
\begin{figure}[H]
\hspace*{100pt}
\includegraphics[width=10em,height=\textheight,keepaspectratio]{./img/iitbhilai.png}
\end{figure}

\vspace{2em}
{\noindent \textbf {\Large{Indian Institute of Technology, Bhilai\\\\CS525\\\\}March \hspace{5pt}2020}}\\[\baselineskip] % Publisher and logo
}}
\endgroup}

\begin{document}
\thispagestyle{empty}
\titleGM % This command includes the title page

\large \tableofcontents

\clearpage
\section*{\large Declaration}
\label{sec:declaration}
\addcontentsline{toc}{section}{\nameref{sec:declaration}}

{\Large We declare that this written submission represents our ideas in our own words and where others' ideas or words have been included, we have adequately cited and referenced the original sources. We also declare that we have adhered to all principles of academic honesty and integrity and have not misrepresented or fabricated or falsified any idea/data/fact/source our submission. We understand that any violation of the above will be cause for disciplinary action by the Institute and can also evoke penal action from the sources which have thus not been properly cited or from whom proper permission has not been taken when needed.}

\vspace{7.5em}

\hspace{4em} \textsc{Rohit Das \hspace{10em} Shoumik Ghoshal}

\hspace{4em} \textsc{(11910230) \hspace{11.5em} (11910300)}

\clearpage
\section*{\large ABSTRACT}
\label{sec:abstract}
\addcontentsline{toc}{section}{\nameref{sec:abstract}}

{\large P2P file sharing is the process of sharing digital content like electronic books, multimedia (music, movies, video clips) through a direct connection between two peers or nodes over the P2P network. This is done with the help of a P2P client software which allows a computer to get connected to a P2P network. The peer which hosts the file is called a seed and the one which downloads it is called a leech. With the introduction of the BitTorrent\cite{bittorrent} protocol, files can be easily shared between peers via seeders, without overloading a single file server. DHT, or distributed hash tables, are a unique way of keeping track of file-owners, or their neighbours. Kademlia\cite{kademlia} is a routing algorithm which optimizes this search for the nearest neighbour using DHTs.

Here we present a peer-to-peer file-sharing system using DHTs instead of trackers,i.e. servers where information of nodes, seeders, etc. are stored. Kademlia is used to optimize the search in DHTs for nodes having the full or partial file(s), and efficiently get the IP and Port of such nodes.}

\clearpage
\section{\large CHAPTER 1: INTRODUCTION}

\subsection{P2P File-Sharing:}

\subsubsection{What is P2P File-Sharing?}
Peer-to-peer\cite{p2p} file sharing is the distribution and sharing of digital media using peer-to-peer (P2P) networking technology. P2P file sharing allows users to access media files such as books, music, movies, and games using a P2P software program that searches for other connected computers on a P2P network to locate the desired content.

A peer-to-peer network allows computer hardware and software to communicate without the need for a server. Unlike client-server architecture, there is no central server for processing requests in a P2P architecture. The peers directly interact with one another without the requirement of a central server.

Now, when one peer makes a request, it is possible that multiple peers have the copy of that requested object. Now the problem is how to get the IP addresses of all those peers. This is decided by the underlying architecture supported by the P2P systems. By means of one of these methods, the client peer can get to know about all the peers which have the requested object/file and the file transfer takes place directly between these two peers.

\subsubsection{Types of P2P Architecture:}

There are roughly three such architectures:
\begin{itemize}
\itemsep0em

\item Centralized Directory

\item Query Flooding

\item Exploiting Heterogeneity

\end{itemize}

\paragraph{Centralized Directory:}

\begin{wrapfigure}{R}{0.5\textwidth}
\centering
\includegraphics[width=0.45\textwidth]{./img/p2p-1.png}
\caption{\label{fig:p2p-1} Centralized Directory}
\end{wrapfigure}

It maintains a huge central server to provide directory service. All the peers inform this central server of their IP address and the files they are making available for sharing. The server queries the peers at regular intervals to make sure if the peers are still connected or not. This server maintains a huge database regarding which file is present at which IP addresses.

Now whenever a requesting peer comes in, it sends its query to the server. Since the server has all the information of its peers, so it returns the IP addresses of all the peers having the requested file to the peer. Now the file transfer takes place between these two peers.

\paragraph{Query Flooding:}

\begin{wrapfigure}{L}{0.45\textwidth}
\centering
\includegraphics[width=0.42\textwidth]{./img/p2p-2.png}
\caption{\label{fig:p2p-2}Query Flooding}
\end{wrapfigure}

Unlike the centralized approach, this method makes use of distributed systems. In this, the peers are supposed to be connected into an overlay network. It means if a connection/path exists from one peer to other, it is a part of this overlay network. In this overlay network, peers are called as nodes and the connection between peers is called an edge between the nodes, thus resulting in a graph-like structure.

Now when one peer requests for some file, this request is sent to all its neighboring nodes i.e. to all nodes which are connected to this node. If those nodes don’t have the required file, they pass on the query to their neighbors and so on. This is called as query flooding. When the peer with requested file is found (referred to as query hit), the query flooding stops and it sends back the file name and file size to the client, thus following the reverse path. If there are multiple query hits, the client selects from one of these peers.

\paragraph{Exploiting Heterogeneity:}

\begin{wrapfigure}{R}{0.45\textwidth}
\centering
\includegraphics[width=0.4\textwidth]{./img/p2p-3.png}
\caption{\label{fig:p2p-3} Supernodes}
\end{wrapfigure}

This P2P architecture makes use of both the above discussed systems. It resembles a distributed system like Gnutella because there is no central server for query processing. But it does not treat all its peers equally. The peers with higher bandwidth and network connectivity are at a higher priority, called as group leaders/super nodes. The rest of the peers are assigned to these super nodes. These super nodes are interconnected and the peers under these super nodes inform their respective leaders about their connectivity, IP address and the files available for sharing.

This structure can process the queries in two ways. The first one is that the super nodes could contact other super nodes and merge their databases with its own database. Thus, this super node now has information of a large number of peers. Another approach is that when a query comes in, it is forwarded to the neighboring super nodes until a match is found. Thus query flooding exists but with limited scope as each super node has many child peers. Hence, such a system exploits the heterogeneity of the peers by designating some of them as group leaders/super nodes and others as their child peers.

\subsection{Distributed Hash Tables (DHTs):}

A distributed hash table (DHT) is a distributed system that provides a lookup service similar to a hash table: $\langle$key, value$\rangle$ pairs are stored in a DHT, and any participating node can efficiently retrieve the value associated with a given key. Nodes can be added/removed with minimum work around re-distributing keys. Keys are unique identifiers which map to particular values, which in turn can be anything from addresses, to documents, to arbitrary data. Responsibility for maintaining the mapping from keys to values is distributed among the nodes, in such a way that a change in the set of participants causes a minimal amount of disruption. This allows a DHT to scale to extremely large numbers of nodes and to handle continual node arrivals, departures, and failures.

DHTs characteristically emphasize the following properties:
\begin{itemize}
\itemsep0em

\item Autonomy and decentralization: the nodes collectively form the system without any central coordination.

\item Fault tolerance: the system should be reliable (in some sense) even with nodes continuously joining, leaving, and failing.

\item Scalability: the system should function efficiently even with thousands or millions of nodes.

\end{itemize}

\begin{wrapfigure}{L}{0.6\textwidth}
\centering
\includegraphics[width=0.55\textwidth]{./img/dht.png}
\caption{\label{fig:dht}Distributed Hash Tables}
\end{wrapfigure}

Any one node needs to coordinate with only a few other nodes in the system -- most commonly, $O(log n)$ of the $n$ participants -- so that only a limited amount of work needs to be done for each change in membership.

Some DHT designs seek to be secure against malicious participants and to allow participants to remain anonymous, though this is less common than in many other peer-to-peer (especially file sharing) systems.

Finally, DHTs must deal with more traditional distributed systems issues such as load balancing, data integrity, and performance (in particular, ensuring that operations such as routing and data storage or retrieval complete quickly).

\clearpage
\section{\large CHAPTER 2: LITERATURE SURVEY}

\subsection{BitTorrent Protocol:}

BitTorrent is a protocol for distributing files. It identifies content by URL and is designed to integrate seamlessly with the web. Its advantage over plain HTTP is that when multiple downloads of the same file happen concurrently, the downloaders upload to each other, making it possible for the file source to support very large numbers of downloaders with only a modest increase in its load. A BitTorrent file distribution consists of the following entites:

\begin{itemize}
\itemsep0em

\item An ordinary web server

\item A static `metainfo' server

\item A BitTorrent tracker

\item An `original' downloader

\item The end user downloaders

\end{itemize}

\subsubsection{Bencoding:}

Bencoding is the encoding used to store metadata in a .torrent file. Strings are length-prefixed base ten followed by a colon and the string. For example \texttt{4:spam} corresponds to `spam'. Integers are represented by an 'i' followed by the number in base 10 followed by an 'e'. For example \texttt{i3e} corresponds to 3 and \texttt{i-3e} corresponds to -3. Integers have no size limitation. \texttt{i-0e} is invalid. All encodings with a leading zero, such as \texttt{i03e}, are invalid, other than \texttt{i0e}, which of course corresponds to 0.

Lists are encoded as an 'l' followed by their elements (also bencoded) followed by an 'e'. For example \texttt{l4:spam4:eggse} corresponds to ['spam', 'eggs']. Dictionaries are encoded as a 'd' followed by a list of alternating keys and their corresponding values followed by an 'e'. For example, \texttt{d3:cow3:moo4:spam4:eggse} corresponds to \{'cow': 'moo', 'spam': 'eggs'\} and \texttt{d4:spaml1:a1:bee} corresponds to \{'spam': ['a', 'b']\}. Keys must be strings and appear in sorted order (sorted as raw strings, not alphanumerics).

\subsubsection{Peer Protocol:}

BitTorrent's peer protocol operates over TCP or uTP. Peer connections are symmetrical. Messages sent in both directions look the same, and data can flow in either direction. The peer protocol refers to pieces of the file by index as described in the metainfo file, starting at zero. When a peer finishes downloading a piece and checks that the hash matches, it announces that it has that piece to all of its peers. Connections contain two bits of state on either end: choked or not, and interested or not. Choking is a notification that no data will be sent until unchoking happens.

Data transfer takes place whenever one side is interested and the other side is not choking. Interest state must be kept up to date at all times - whenever a downloader doesn't have something they currently would ask a peer for in unchoked, they must express lack of interest, despite being choked. This makes it possible for downloaders to know which peers will start downloading immediately if unchoked. Connections start out choked and not interested. When data is being transferred, downloaders should keep several piece requests queued up at once in order to get good TCP performance.

On the other side, requests which can't be written out to the TCP buffer are immediately queued up in memory rather than kept in an application-level network buffer, so they can all be thrown out when a choke happens. The peer wire protocol consists of a handshake followed by a never-ending stream of length-prefixed messages. The handshake starts with character ninteen (decimal) followed by the string 'BitTorrent protocol'. The leading character is a length prefix, put there in the hope that other new protocols may do the same and thus be trivially distinguishable from each other. All later integers sent in the protocol are encoded as four bytes big-endian.

After the fixed headers come eight reserved bytes, which are all zero in all current implementations. If you wish to extend the protocol using these bytes, please coordinate with Bram Cohen to make sure all extensions are done compatibly. Next comes the 20 byte sha1 hash of the bencoded form of the info value from the metainfo file. (This is the same value which is announced as info{\_}hash to the tracker, only here it's raw instead of quoted here). If both sides don't send the same value, they sever the connection. After the download hash comes the 20-byte peer id which is reported in tracker requests and contained in peer lists in tracker responses. If the receiving side's peer id doesn't match the one the initiating side expects, it severs the connection.

\subsection{Kademlia and the XOR Metric:}

Kademlia minimizes the number of configuration messages nodes must send to learn about each other. It uses parallel, asynchronous queries to avoid timeout delays from failed nodes. While Kademlia takes the basic approach of many DHTs, like opaque, 160-bit keys, $\langle$key,value$\rangle$ pairs being stored in nodes with IDs ``close'' to the key, many of its benefits result from its use of a novel XOR metric for distance between points in the key space.

\subsubsection{System Description:}

\begin{figure}[H]
\centering
\includegraphics[width=0.75\textwidth]{./img/kadem-1.png}
\caption{\label{fig:kadem-1} Kademlia binary tree. The black dot shows the location of node 0011.... in the tree.}
\end{figure}

Kademlia effectively treats its nodes as leaves in a binary tree, with each node's position determined by the shortest unique prefix of its ID. For any given node, the binary tree is divided into a series of successively lower subtrees that don't contain the node. The highest subtree consists of the half of the binary tree not containing the node. The next subtree consists of the half of the remaining subtree not containing the node and so forth.

\subsubsection{XOR Metric:}

\begin{figure}[H]
\centering
\includegraphics[width=0.75\textwidth]{./img/kadem-2.png}
\caption{\label{fig:kadem-2} Locating a node $1110$ by its ID.}
\end{figure}

Every message a node transmits includes its node ID, permitting the recipient to record the sender's existence if necessary. Kademlia relies on a notion of distance between two identifiers. Given two identifiers, $x$ and $y$, Kademlia defines the distance between them as ther bitwise exclusive or (XOR) interpreted as an integer, $d(x,y)$ = $x \oplus y$.

XOR captures the notion of distance implicit in the binary-tree-based sketch of the system. In a fully-populated binary tree of 160 bit IDs, the magnitude of the distance between two IDs is the height of the smallest subtree containing them both. When a tree is not fully populated, the closest leaf to an ID $x$ is the leaf whose ID shares the longest common prefix of $x$. If there are empty branches in the tree, there might be more than one leaf with the longest common prefix. In that case, the closest leaf to $x$ will be the closest leaf to ID $x$ produced by flipping the bits in $x$ corresponding to the empty branches of the tree.

\clearpage
\section{\large CHAPTER 3: METHODS DEVELOPED}

Here we have presented our implementation of parsing the .torrent file, and piece and block management while fetching and merging bytes of file downloaded. We also check the integrity of the pieces downloaded, block by block. We fixed the block size at $2^{14}$. All implementations have been done in python3.

\subsection{Bencode parsing:}
File: bencoding.py
\lstinputlisting[showstringspaces=false]{/home/mouri/MTech/CS525/Project/bit-torrent-dht/bencoding.py}

\subsection{Blocks and Pieces Management:}
File: blocks.py
\lstinputlisting[showstringspaces=false]{/home/mouri/MTech/CS525/Project/bit-torrent-dht/blocks.py}
\vspace{2em}
File: pieces.py
\lstinputlisting[showstringspaces=false]{/home/mouri/MTech/CS525/Project/bit-torrent-dht/pieces.py}
\vspace{2em}
File: piece{\_}mgr.py
\lstinputlisting[showstringspaces=false]{/home/mouri/MTech/CS525/Project/bit-torrent-dht/piece_mgr.py}

\clearpage
\section{\large CHAPTER 4: RESULTS AND CONCLUSIONS}

Pending further implementation and metric monitoring.

\clearpage
\section{\large CHAPTER 5: FUTURE SCOPE}

We are yet to implement message passing to indicate choked/unchoked, interested/not interested, and mainly, the DHT.

\clearpage
\bibliographystyle{unsrt}
\bibliography{References}

\end{document}

### 2020-08-12 MTech/CS607/Abstract/Abstract_P1.tex
Adding Paper Review

\documentclass[12pt]{article}

\usepackage[hmarginratio=1:1,top=13mm,bottom=15mm,left=18mm,
right=18mm]{geometry} % Document margins

\pagenumbering{gobble} % turns off page numbering

\title{\textbf{IDSGAN: Generative Adversarial Networks for Attack Generation against Intrusion Detection}}
\author{Rohit Das}

\begin{document}

\maketitle

\begin{large}

Intrusion Detection Systems (IDS) have been implemented using various Machine Learning models over the years. However, their robustness in the face of an adversary is something that has been lacking research. While current IDSs can detect between normal and malicious traffic, they may fail if a malicious traffic is disguised as normal. This paper aims to evade current IDSs by generating adversarial malicious traffic using a Wasserstein Generative Adversarial Network (WGAN) and hence test their robustness.\\

The main idea here is that a black-box IDS will be used to classify half of the data set used (NSL-KDD) and the corresponding learning loss shall be recorded. Based on the predicted labels of the black-box IDS, the discriminator of our IDSGAN will learn those labels and mimic the black-box to a certain extent. The predicted labels of the discriminator will then be fed back to the generator, which will accordingly learn and add noise to reduce its own loss of evading detection by the IDS.\\

The scope of the paper is limited by the dirth of data on attacks of the categories User2Root (U2R) and Remote2Local (R2L) in the data set NSL-KDD. Hence, further data collection in this area shall be a definite improvement for IDSGAN. Future improvements will be headed towards evasion in distributed computing, cloud computing and edge computing. Our research shall be specifically focused on how IDSGAN can be used to evade IDS for an Internet-of-Things (IoT) network. Such a network may be consisting of homogeneous edge-computing devices or heterogeneous devices like mobile phones, printers, etc., which may have their own IDS models built-in or a single distributed IDS model. Given the data for IDSGAN in evading various black-box models individually, we can create a distributed IDSGAN for the devices in the network and train according to the IDS being used. The IDSGAN will be specifically targeting any network-based intrusion detection system (NIDS) present in the network as it is mainly trained on network data, and not on system/host information, on which a host-based intrusion detection system (HIDS) is based.

\end{large}

\end{document}

### 2020-08-12 MTech/CS607/Term Paper/CS607_P1_v1.tex
Adding Paper Review

\documentclass[10pt, conference, compsocconf]{IEEEtran}
\usepackage{color,graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{color}
%\usepackage{algorithm}
\usepackage[ruled]{algorithm2e}
%\usepackage{algorithmic}
\usepackage{enumerate}
%\usepackage{syntonly}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{array}
%\usepackage[tight,footnotesize]{subfigure}https://www.overleaf.com/project/5cfd43d4b41ca5117%63f7621
%\usepackage{stfloats}
\usepackage{url}
\usepackage{threeparttable}
\usepackage{cite}
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newtheorem{remark}{Remark}
\usepackage{svg}
\usepackage{nomencl}
\usepackage{tikz}
\usepackage{float}
\usepackage{etoolbox}
\makeatletter
\patchcmd{\@makecaption}
  {\scshape}
  {}
  {}
  {}
\makeatletter
\patchcmd{\@makecaption}
  {\\}
  {.\ }
  {}
  {}
\makeatother
\def\tablename{Table}

\usepackage{natbib}
\setlength{\bibsep}{1.0pt}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}

% End of preamble
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author{ \parbox{5 in}{\centering Rohit Das\\
         Dept. of Electrical Engg. and Computer Science (EECS),\\
         Indian Institute of Technology, Bhilai\\
         Sejbahar, Chhattisgarh - 492015.\\
         {\tt\small rohitd@iitbhilai.ac.in}} % <-this % stops a space
}

%\IEEEoverridecommandlockouts
%\IEEEpubid{\makebox[\columnwidth]{978-1-4799-6016-3/14/\$31.00~\copyright~2014 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}

\begin{document}

\bstctlcite{IEEEexample:BSTcontrol}
\title{Generative Adversarial Network for Intrusion Detection Evasion}
\maketitle

\begin{abstract}

Intrusion Detection Systems (IDS) have been implemented using various Machine Learning models over the years. However, their robustness in the face of an adversary is something that has been lacking research. While current IDSs can detect between normal and malicious traffic, they may fail if a malicious traffic is disguised as normal. This paper aims to evade current IDSs by generating adversarial malicious traffic using a Wasserstein Generative Adversarial Network (WGAN) and hence test their robustness.The main idea here is that a black-box IDS will be used to classify half of the data set used (NSL-KDD) and the corresponding learning loss shall be recorded. Based on the predicted labels of the black-box IDS, the discriminator of IDSGAN will learn those labels and mimic the black-box to a certain extent. The predicted labels of the discriminator will then be fed back to the generator, which will accordingly learn and add noise to reduce its own loss of evading detection by the IDS.\\

The scope of the paper is limited by the dirth of data on attacks of the categories User2Root (U2R) and Remote2Local (R2L) in the data set NSL-KDD. Hence, further data collection in this area shall be a definite improvement for IDSGAN. Future improvements will be headed towards evasion in distributed computing, cloud computing and edge computing. Our research shall be specifically focused on how IDSGAN can be used to evade IDS for an Internet-of-Things (IoT) network. Such a network may be consisting of homogeneous edge-computing devices or heterogeneous devices like mobile phones, printers, etc., which may have their own IDS models built-in or a single distributed IDS model. Given the data for IDSGAN in evading various black-box models individually, we can create a distributed IDSGAN for the devices in the network and train according to the IDS being used. The IDSGAN will be specifically targeting any network-based intrusion detection system (NIDS) present in the network as it is mainly trained on network data, and not on system/host information, on which a host-based intrusion detection system (HIDS) is based.

\end{abstract}

% keywords can be removed
\begin{IEEEkeywords}
Deep learning, black box attack, adversarial learning, perturbation, intrusion detection.
\end{IEEEkeywords}

\section {Introduction}

With greater threats to security and robustness of networks comes greater responsibility on intrusion detection systems to detect and defend a network from malicious activities. The IDS monitors network traffic and raises alerts if it detects some kind of unauthorized and/or malicious activity. Its main aim is to classify between normal and malicious traffic.

Machine learning has been actively taking over that responsibility and has been shown to be performing quite well. Models based on learning algorithms like K-Nearest neighbours or Support Vector Machines have been utilized in IDSs and have achieved good results {\cite{tsai2009intrusion}}. Rapid developments in deep learning led to further improvements in IDSs like Convolutional Neural Networks (CNN), Recurrent Neural Networks, Auto-Encoders, etc \cite{li2017intrusion} \cite{li2018character}.

However, it was soon noticed that the IDSs werent't as robust under adversarial examples; inputs similar to the original data but misclassified due to some indistinguishable perturbation introduced in the dataset \cite{carlini2017adv}. With the introduction of GAN (generative adversarial networks) by Goodfellow \cite{goodfellow2014gan}, where a model contained two competing networks, generating adversarial data became much more convenient, and hence making systems more robust through adversarial training \cite{kim2017malware}. Although much work has been done in intrusion detection systems and GAN, here the paper highlights the use of GAN in IDS, thereby producing IDSGAN \cite{lin2018idsgan}. The main aim of IDSGAN is to use a black-box based on some generic learning algorithm, which will predict classes based on some initial adversarial data generated by the GAN generator. The discriminator will train itself based on the black-box output to mimic it as closely as possible. The predicted classes will then be fed back to the generator to train it and generate better adversarial models which can successfully evade an IDS with a high probability. The design and improvements in the generator and discriminator is done on the basis of Wasserstein GAN\cite{arjovsky2017gan} for its superior characteristics. To summarize, the following are contributed by this paper:

\begin{itemize}

\item The malicious data is modified so as not to invalidate its attack characteristic, i.e., only non-functional features are modified or removed.

\item To be as close to real-life situations and applications as possible, the adversarial attacks will be performed on black-box IDSs based on commonly-used Machine Learning models.

\item Experimentally, IDSGAN has shown to have successfully evaded all the black-box models used, meaning that most adversarial attacks went undetected by the IDSs used.

\item Improvements on the current IDSGAN, such as a distributed IDSGAN for distributed clusters, or IoT networks have also been discussed later in the paper.

\end{itemize}

\begin{figure*}

\includegraphics[width=\textwidth]{./images/img1.jpeg}
\caption{The training of IDSGAN. The training dataset is divided into the normal traffic and the malicious traffic. After adding
noise, the malicious traffic is sent into the generator. The adversarial malicious traffic and the normal traffic are predicted by the black-box IDS. The predicted labels and the original labels are used in the discriminator to simulate the black-box IDS. The
loss of generator is calculated based on the result of the discriminator and the predicted labels of the black-box IDS.}

\end{figure*}

\section {Problem Definition and Background }

The improved NSL-KDD is used as a benchmark and state-of-the-art dataset to evaluate any IDS \cite{hu2015improv}. The dataset is internally divided into the training set KDDTrain+ and the test set KDDTest+. To emulate real-world network traffic, the dataset consists of normal as well as 4 kinds of malicious traffic: Probing (Probe), Denial of Service (DoS), User2Root (U2R) and Root2Local (R2L). The features of the dataset can be broadly classified into four classes: "intrinsic", "content", "time-based traffic" and "host-based traffic" \cite{davis2011data} \cite{lee2000frame}. The detailed description is listed below:

\begin{itemize}

\item "Intrinsic" features: These features contain information about metadata obtained from packet headers.

\item "Content" features: These features hold actual information that is contained within packets.

\item "Time-based" traffic: These features hold data over analysis of traffic input over a 2-second window and contains information like how many connections were attempted to the same host.

\item "Host-based" traffic: These features store information about analysis over a series of connections made (how many requests made to the same host over x-number of connections). These features are designed to access attacks, which span longer than the 2-second window span.

\end{itemize}

All in all, the dataset contains 4 categorical, 6 binary, 23 discrete and 10 continuous features, totalling to 43. The last two features show the type of attack and score based on attack intensity.

For pre-processing of data, the values are put through numerical conversion and normalization to be converted to input vectors for traffic examples of IDSGAN. For the non-numeric discrete features, the distinct values are mapped to numbers. E.g., "protocol$\_$type" has 3 distinct values: TCP, UDP and ICMP. Each value can be assigned a discrete number like 1,2 and 3. In later stages, to eliminate the dimensional impact among feature values in input vectors, a standard scalar is used to normalize the original and converted numeric features into a specific range. Min-max normalization method is implemented to transform data within the interval $[0,1]$, thus suitable for all discrete and continuous features. The min-max normalization is calculated as follows:

\begin{center}

$x' = \dfrac{x - x_{min}}{x_{max} - x_{min}}$

\end{center}

$x$ being the feature value before normalization and $x'$ is the value after normalization. $x_{max}$ and $x_{min}$ represent the max and min value of this feature in the dataset respectively.

\section {Methodology and result}
Although rapid development in GANs has led to its many versions for many specific requests, it is instable and and causes non-convergence. To avoid such situations, Wasserstein GAN will be used for IDSGAN. In our model, the generator modifies specific features to produce adversarial malicious traffic data. A black-box IDS takes in the adversarial input, and predicts the classes. The discriminator takes the predicted labels of the black-box as input and tries to imitate it. The black-box IDS is implemented using some machine learning algorithm trained for intrusion detection. The framework of IDSGAN is represented in Fig. 1.

While we are generating malicious traffic data to evade the IDS, the attack capability of the data should be unaltered. So, it is evident that each category of attacks have some functional features which should not be changed. For the other non-functional attacks, we can choose to either keep or kick them. The functional features for each attack is highlighted in the table below \cite{lee2000frame}:

\begin{table}[ht]

\caption{The functional features of each attack category}

\begin{tabular}{*{5}{|M{4.8em}}|}
\hline
\multirow{2}{*}{Attack} & \multicolumn{4}{c|}{Functional features}                                                           \\[1.5ex] \cline{2-5}
 & Intrinsic & Content  & Time-based Traffic  & Host-based traffic \\[1.5ex] \hline
Probe &  \checkmark  &  & \checkmark & \checkmark\\[1.5ex] \hline
DoS & \checkmark   & & \checkmark  & \\[1.5ex] \hline
U2R & \checkmark  & \checkmark  &  & \\[1.5ex] \hline
R2L & \checkmark  &  \checkmark  &  &\\[1.5ex] \hline
\end{tabular}

\end{table}

\subsection{Results}

IDSGAN is trained with the 64 batch size for 100 epochs. The learning rates of the generator and the discriminator are both 0.0001. The dimension of the noise vector is 9. The weight clipping threshold for the discriminator training is set as 0.01. The experimental results have been performed with various black-box IDS models based on algorithms like Support Vector Machines (SVM), Multilayer Perceptrons (MLP), etc. The IDSGAN generates adversarial traffic which successfully evades all the black-box IDS models tested against it. A graphical representation of the results is shown in Fig. 2 \cite{lin2018idsgan}.

\begin{center}

\begin{figure}
\includegraphics[width=0.47\textwidth]{./images/img2.png}
\caption{The comparisons of the adversarial detection rates and the original detection rates under different black-box IDS models with only the functional features unmodified. (a) is the results of DoS and (b) is results of U2R and R2L.}
\end{figure}

\end{center}

\section {Improvement Proposal}

While IDSGAN is seen to perform well for various black-box models, the research is mostly done for stand-alone devices like personal computers, connected to a network. An improvement for the current centralized IDSGAN would be a distributed network of generators, which can then be used to attack a distributed cluster system. The benefit of such a distributed GAN would be that each generator will be able to learn from its neighbouring devices, and in case of a heterogeneous network, learn from models based on very different algorithms as well, and train to create more robust adversarial network traffic.

\subsection {Methodology}

The procedure to be used here will be based on the fact that while by design of a GAN, the generator and discriminator are a tighty-coupled module, a set of workers can be used to train both of them separately. Federated learning \cite{konecny2016fed} is a method, where a machine learning model, and more specifically a deep-learning neural network, is trained on a set of workers. The workers will be performing numerous local iterations between each communication to the central server. The local resources of the workers will be leveraged to efficiently train IDSGAN over a distributed network.

\begin{center}

\begin{figure}

\includegraphics[width=0.49\textwidth]{./images/img3.jpeg}

\caption{FL-GAN (federated learning adapted to GAN)}

\end{figure}

\end{center}

\subsubsection{Experiment}

As we can see in Fig. 3 \cite{corentin2018gan}, a centralised GAN co-ordinates the workers to synchronize information and parameters. Each worker node has its own set of generator and discriminator, which train individually over different datasets, or different parts of the same dataset, and the aggregated results are sent back to the centralized generator, which will approximate and produce optimized adversarial perturbations for all the workers. The workers will be only concerned with recalculating the parameters for the localized generators, and their errors. To avoid overfitting, only a specific number of iterations over a batch will be allowed. These information on error and parameters are then relayed back to the central GAN, which then trains its own generator through its discriminator based on the data received.

The discriminators can each be individually trained over different black-box IDS models, or to attack the same black-box IDS model in a distributed manner. The output of each individual black-box at each worker will then be passed to the discriminator so that it can be emulated. The local generator will then train itself on a small batch of data, based on the output of its discriminator. This will help the distributed IDSGAN to be able to attack a distributed cluster of heterogeneous devices, in case each utilizes IDSs based on different learning models. The advantage here is that any kind of black-box can be plugged in and evaded by this model. Also, the attacking worker may be made to train on a black-box not present in that location. In this way, the actual attack location may be masked and make it difficult to track.

\subsection {Challenges}

Some of the potential challenges and problems of the above-mentioned improvements are as follows:

\begin{itemize}

\item Huge latency over a low-bandwidth network will cause the distributed IDSGAN to take a lot of time to train and generate adversarial network traffic as a lot of data will be transferred to and from workers and the central GAN.

\item If any worker is unavailable at any point of time, it will affect the training and generation of adversarial data, and may fail evasion for the black-box which the unavailable worker was targeting.

\end{itemize}

\subsection {Future work and conclusion}
Future applications for the distributed IDSGAN can be in IoT settings, where instead of a large-scale distribution, the IDSGAN will work in a relatively localized environment. Distributed IDSGAN can have applications in evading intrusion detection in real-time traffic camera networks, autonomous car navigation and update networks, OTA (Over-the-air) networks for mobile devices, distributed cloud resources and much more.

In current trends of cloud computing and fog computing, IDSGAN will have diverse applications in distributed environments, both large-scale and localized.

\section {Conclusion}
Here we have highlighted what IDSGAN is, and how it successfully had evaded most state-of-the-art IDS systems based on popular Machine Learning models. Distributed IDSGAN can even be more powerful in evasion techniques using generated adversarial traffic data. These GANs can then be used to create actually robust intrusion detection systems.

\bibliographystyle{unsrt}
\bibliography{references.bib}

\end{document}

### 2020-08-12 MTech/Thesis/Thesis.tex
Adding Thesis Report

\documentclass[conference]{IEEEtran}
% \IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmicx}
\usepackage{url}
\usepackage{setspace}
\usepackage{algorithm}
\usepackage{multicol}
% \usepackage{arevmath}
\usepackage{algpseudocode}
\algrenewcommand\Return{\State \algorithmicreturn{} }%
\algnewcommand{\LineComment}[1]{\State \(//\) #1}

\usepackage{dblfloatfix}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Dynamic Reconfiguration and Resource Provisioning in Pi Clusters % *\\
% {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
% should not be used}
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{Rohit Das}
\IEEEauthorblockA{\textit{Dept. of Electrical Engineering and Computer Science} \\
\textit{Indian Institute of Technology Bhilai}\\
Raipur, India \\
rohitd@iitbhilai.ac.in}
\and
\IEEEauthorblockN{Dr. Subhajit Sidhanta}
\IEEEauthorblockA{\textit{Dept. of Electrical Engineering and Computer Science} \\
\textit{Indian Institute of Technology Bhilai}\\
Raipur, India \\
subhajit@iitbhilai.ac.in}
% \and
% \IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
}

\maketitle
\thispagestyle{plain}
\pagestyle{plain}

\begin{abstract}
In a resource-constrained computing setup, efficient allocation of resources is essential. Edge clusters consisting of small, single-board computers are cheaper, easily deployable and re-configurable. During unavailability of cloud services or intermittent network coverage, edge clusters can be helpful. To enable feasible usage of such clusters, algorithms to manage failure and overloading are essential. Most of the related works lack  in the regard of using ARM devices for such clusters.
\end{abstract}

\begin{IEEEkeywords}
edge computing, raspberry pi, distributed systems, resource-constrained, resource provisioning
\end{IEEEkeywords}

\section{Introduction}

With the emergence of cloud computing, computational resources have become more flexible and easily available. Be it deep learning analytical models, online software subscriptions or data storage, cloud computing is the most popular choice. However, using cloud services require stable bandwidth, SLA's promising competitive low values of downtime and fast results. Where cloud fails, edge computing comes in. Using single-board computers to create an edge cluster, we can offload cloud services to the edge, speeding up data processing and lowering transmission latency. Such lightweight clusters need to have algorithms in place to manage node failures, overloading and reconfiguration and be in tandem with quality of cloud services.

Single-board computers like Raspberry Pi usually come with a quad-core processor and at most 4GB of RAM. Nowadays, in the advent of data analytics, the above-mentioned resources are too less for a single node to handle vast amounts of data. So, we are faced with the following problems:
\begin{itemize}
    \item To enable fast processing of a huge in-stream of data, either the rate of data fed into the cluster must be regulated, or the data stream must be parallelized amongst multiple nodes.
    \item Some nodes will be overburdened with processes taking up a lot of resources, like applications involving deep-learning or neural networks, object-recognition from a live video feed, so efficient load-balancing algorithms are essential.
    \item In case of failure of a node, container running on the failed node must be migrated before-hand to a standby node, and the new node must be up and running with as less downtime as possible.
\end{itemize}

\section{Related Works}

Live migration intends to transfer user control or a process from one node to another in a cluster in case of failures or crashes. While live migration is good and suitable for systems set up over LAN having bandwidths in the range of 1-40 Gbps, VM hand-off \cite{elephant} focuses mainly on the edge, having a WAN connection of bandwidth 5 to 25 Mbps.

The process of VM hand-off \cite{elephant} can be broken down into 3 parts: \textbf{delta encoding}, \textbf{deduplication} and \textbf{compression}. Each step of the optimizing process is a module in the VM Hand-off pipeline. The aim is to send only the difference between the modified data in the source VM and the base VM at the destination. The pipeline switches between algorithms to make the best use of both the CPU cores and the network bandwidth.

Redundancy live migration \cite{redun_mig} has been shown to be a significant improvement over the pre-copy, post-copy or the hybrid live migration algorithm. 
% It works as follows:
% \begin{itemize}
%     \item When migration is to start, packets from client are rerouted to the destination server, which buffers them and also sends them over to the source server.

%     \item Source server creates a checkpoint when migration starts, i.e. it creates a copy of the container at the current state, and them starts logging further changes in CPU state, memory state, etc. after the checkpoint is triggered.

%     \item Source server then sends over the copy of the container at checkpoint to the destination server, followed by the logs, when downtime occurs. The destination server replays the logs and syncs with the source server.

%     \item The destination server then plays back all the buffered packets from the client and starts serving the client, thus migration being complete.

% \end{itemize}

% \begin{figure}[htbp]
% \centerline{\includegraphics[width = 0.4 \textwidth]{./img/redun_mig.png}}
% \caption{\label{fig:redun_mig} Redundancy Migration High-Level Architecture. \cite{redun_mig}}
% \end{figure}

% The big takeaway here is that the algorithm is network, application or platform agnostic, but it still needs a fixed and minimum bandwidth to send over the container copy, and keep downtime to a specified minimum, as agreed in the SLA (Service-Level Agreement). Also, with ARM devices having low resources, implementing this algorithm will not feasible.

Service migration reduces service latency, and user applications are migrated to the closest MEC(Mobile Edge Clouds) only when it has benefits surpassing the negative effects of downtime. The migration is performed by sending files synchronously over the network. Meaning, only files which have changed significantly in comparison to the destination MEC are sent over. To optimize the amount of data sent out during migration, a three-layered approach \cite{migration_mec} is used. \textbf{Instance layer} migration consists of migrating only application-specific information like the running state of the application. \textbf{Application layer} is involved when the entire application is not found at the destination MEC, and the same is cloned from the source. The topmost \textbf{Base layer} is only involved when the container or VM used itself is not present in the destination, and needs to be packaged and sent from the source.

% \begin{itemize}
%     \item Instance layer: This consists of migrating only the application-specific information, like the running state of the application, metadata specific to the user, etc.

%     \item Application layer: If the application is not found in the destination MEC, the application is cloned from the source, all states and memory data are stores in one or multiple files, and migrated.

%     \item Base layer: The guest OS and kernel, etc. are packaged and sent over in this layer. Normally this level of migration is not required since all MECs contain a copy of the guest OS and kernel.
% \end{itemize}

% \begin{figure}[htbp]
% \centerline{\includegraphics[width = 0.4 \textwidth]{./img/migration1.png}}
% \caption{\label{fig:migr_mec} Flow chart of the migration mechanism for live- migrating with the three-layer model, where \textit{rsync} is used for incremental file synchronization. \cite{migration_mec}}
% \end{figure}

Dynamic Provisioning of resources \cite{dynamic} for a resource-constrained cluster will be helpful to deal with situations like flash crowds, when a sudden amount of huge traffic overwhelms the cluster and fast enough to rearrange the topography of the cluster nodes to accommodate for the sudden surge. The cluster nodes can be tiered to enable handling of the computations and requests at multiple stages. Predictive and Reactive provisioning \cite{daniel2011prediction} can handle flash crowds or deviations from predicted long-term behaviour. Analytical models to allocate servers to a tier based on the estimated workload and accounting for multiple requests that comprise a session and the stateful nature of session-based Internet applications will also help in handling surges.
% through the following ways:
% \begin{itemize}
%     \item Predictive and Reactive provisioning \cite{daniel2011prediction} to handle flash crowds or deviations from predicted long-term behaviour.
%     \item Analytical model to allocate servers to a tier based on the estimated workload.
%     \item Accounting for multiple requests that comprise a session and the stateful nature of session-based Internet applications.
% \end{itemize}

% \begin{figure}[htbp]
% \centerline{\includegraphics[width=0.4 \textwidth]{./img/load_bal.png}}
% \caption{\label{fig:load_bal} Architecture of Reactive-Predictive Load-Balancer \cite{daniel2011prediction}}
% \end{figure}

% Most of the works cited above involved implementations and system setup consisting of commomplace computer systems having adequate resources, except for MECs. Even then, edge clusters consisting of single-board chip computers have not been used to perform delta VM handoff, with containers running on each node.

% Monitoring the cluster for fault-tolerance and overloading will be essential. YourKit Java Profiler \cite{yourkit2010yourkit} can be used as it is lightweight and will be adequate for the resource-constrained cluster.

\section{Cluster Provisioning and Reconfiguration}

Using single-board chips with low resources make the cluster prone to overloading and failures. Reconfiguring the network in case of node failures, and optimal provisioning of nodes for more intensive computations, as well as scaling down when not needed, is essential for the edge cluster.

Linux Containers (LXC) will be running on each node in the cluster. VMs will not be suitable for single-chip boards that we will be using as VMs take up more resources than containers, and hence more bandwidth will be needed to exchange data among nodes.

There will be two parts to the algorithm: failure handling and overload management. The entire cluster will be segregated into two parts - master cluster, and worker cluster. The master cluster will consist of nodes which can be assigned as pseudo-masters, or super peers. The master node will be handling the worker cluster, consisting of worker nodes. Experiments have shown that having a master node with at least 4 GB RAM prevent the node from crashing due to overload.

\subsection{Node Failure Handling}

Any node may fail due to random crashes, overloading or environmental factors. Each worker node will have an associated standby node to fall back on in case of node failure. Frequent delta migration of data encapsulated by containers among nodes will prevent data loss and mitigate downtime.

The master cluster, containing the master nodes, as well as the worker cluster, containing the worker nodes, will be having a replication factor of $n + k$, $n$ being the cluster size of each type. Each worker node will be allocated a standy node from its respective cluster. Container information like current memory and disk state shall be sent over after every interval of $T$ seconds.

\begin{algorithm}
    \setstretch{1.15}
    \caption{Node Activation on Worker Node}
    \begin{algorithmic}[1]
        \Function{activate{\_}node}{standby{\_}node{\_}MAC}
            \LineComment Checks if active node is down
            \If {time.now() $>$ last{\_}seen + $T$ + $t$}
                \State {send msg(MAC,active{\_}node) to curr{\_}master}
                \LineComment Standby node takes over
                \State {restart container from last{\_}state{\_}recvd}
                \State {send container data to standby node}
                \While {true}
                    \State {send delta{\_}diff(curr{\_}lxc{\_}state, last{\_}state)}
                    \State {last{\_}state $\leftarrow$ curr{\_}lxc{\_}state}
                    \State {last{\_}seen $\leftarrow$ time.now()}
                    \State {sleep ($T$)}
                \EndWhile
            \EndIf
        \EndFunction
    \end{algorithmic}
\end{algorithm}

For the first time, entire container information will be sent over to the standby node. In consecutive intervals, only the delta difference in states of active and standby nodes will be sent over. That way, information sent over the network and overall bandwidth usage can be minimized.

Whena standby node does not receive any information after $T + t$ seconds, $t$ being the failure tolerance interval, it will inform the active master, take over from the failed active node and mark itself as an active node. The master will allocate a standby node from the pool and the new node will pick up from where the failed node left off.

\begin{algorithm}
    \setstretch{1.15}
    \caption{Node Activation on Master Node}
    \begin{algorithmic}[1]
        \Function{activate{\_}node}{standby{\_}node{\_}MAC}
            \LineComment Marks respective active node as down
            \State {active{\_}node $\leftarrow$ hash{\_}list [standby{\_}node{\_}MAC]}
            \State {hash{\_}list [active{\_}node].state = down}
            \For {node in hash{\_}list}
                \If {hash{\_}list [node] == NULL AND\\ hash{\_}list [node].state != down}
                    \State {standby{\_}node{\_}MAC.activate{\_}node (node)}
                    \State exit
                \EndIf
            \EndFor
        \EndFunction
    \end{algorithmic}
\end{algorithm}

For a master node, two nodes will be on standby, and will receive delta differences from the active master. When the active master node fails, a bully leader election will decide the new master node, which will then broadcast its own MAC to the worker cluster.

A list of available nodes with their hostname and MAC will be maintained at every node. It will also contain important information on the nodes like their status (dead or alive), if they are an active or standby node, their corresponding standby or active node, etc. When a worker node fails, only the active master can change its own record. It can broadcast the new node after every $T'$ interval. When a master node fails, the new master node will broadcast itself and the changes in the record, thus reducing bandwidth usage.

\subsection{Node Provisioning through Reconfiguration}

Monitoring the nodes in the cluster can prevent failure due to overloading. Any under-utilized nodes from the cluster can be removed to optimize resource usage. Using YourKit, memory and disk usage can be monitored on each node.

When resource usage is above a certain threshold, the active node can request the active master to add more nodes to the cluster to distribute the jobs and prevent overloading. If two free nodes are found in the pool, the master assigns one as the active node, and the other as a standby node, and adds them both to the cluster.
% Similarly, if resource utilization falls below a threshold, the active node can be put on standby, or taken out of the cluster, to be requisitioned when needed.

\begin{algorithm}
    \setstretch{1.15}
    \caption{Additional Node Allocation}
    % \begin{multicols}{2}
    \begin{algorithmic}[1]
        \Function{allocate{\_}node}{active{\_}node{\_}MAC,stats}
            \LineComment Checks if stats are above threshold
            \If {stats.memory $>$ $Mem_{thresh.}$ OR stats.disk{\_}usage $>$ $Disk_{thresh.}$}
                \State active{\_}node = NULL
                \State standby{\_}node = NULL
               \For {node in hash{\_}list}
                \If {hash{\_}list [node] == NULL AND\\ hash{\_}list [node].state != down}
                    \If {active{\_}node == NULL}
                        \State active{\_}node = node
                    \ElsIf {standby{\_}node == NULL AND node != active{\_}node}
                        \State standby{\_}node = node
                    \Else
                        \State exit
                    \EndIf
                \EndIf
            \EndFor
            \EndIf
        \EndFunction
    \end{algorithmic}
    % \end{multicols}
\end{algorithm}

If only one free node is found, the node will be assigned as an active node and added to the cluster. An existing standby node may be reassigned to this active node. If no free node is found, one of the standby nodes will be assigned as an active node, and a standby node will reassigned from the cluster.

Similarly, when resource usage falls below the lower threshold, nodes can be unassigned to scale-down the cluster. Important info on the node will be broadcast to all workers before taking it out. (How to scale down?)

\section{Experimental Setup and Implementation}

The experimental setup consists of creating a cluster using Raspberry Pi 3 Model B+ single-board computers. Each Pi consists of a 1.4GHz 64-bit quad-core processor, 1GB LPDDR2 SDRAM and 32GB micro-SD cards. Each node is running Raspbian OS based on Linux. The networking is done using wireless LAN, and each node has its own micro-USB charger. A file with the list of MACs of all nodes in the cluster will be maintained in each node. That way, we can easily find the IPs of each node when the cluster starts up.

\begin{figure*}[!b]
% \centerline{
\centering
\includegraphics[width = 0.5 \textwidth,]{./img/edge_cluster.png}
% }
\caption{\label{fig:edge_cluster} Edge Cluster Setup using Raspberry Pi}
\end{figure*}

Apache$\textsuperscript{\texttrademark}$ Hadoop$\textsuperscript{\textregistered}$ and Apache Spark$\textsuperscript{\texttrademark}$ are installed in each node to distribute jobs across the cluster. One node is chosen as the name node, which will be responsible for starting HDFS and Yarn across the cluster.

Python libraries like Tensorflow, Keras and Elephas help to distribute Deep Learning tasks across a Spark Cluster. However, since we are starting the cluster from the name node, due to low resources, the jobs start to lag.

% \section{Ease of Use}

% \subsection{Maintaining the Integrity of the Specifications}

% The IEEEtran class file is used to format your paper and style the text. All margins, 
% column widths, line spaces, and text fonts are prescribed; please do not 
% alter them. You may note peculiarities. For example, the head margin
% measures proportionately more than is customary. This measurement 
% and others are deliberate, using specifications that anticipate your paper 
% as one part of the entire proceedings, and not as an independent document. 
% Please do not revise any of the current designations.

% \section{Prepare Your Paper Before Styling}
% Before you begin to format your paper, first write and save the content as a 
% separate text file. Complete all content and organizational editing before 
% formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
% proofreading, spelling and grammar.

% Keep your text and graphic files separate until after the text has been 
% formatted and styled. Do not number text heads---{\LaTeX} will do that 
% for you.

% \subsection{Abbreviations and Acronyms}\label{AA}
% Define abbreviations and acronyms the first time they are used in the text, 
% even after they have been defined in the abstract. Abbreviations such as 
% IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
% abbreviations in the title or heads unless they are unavoidable.

% \subsection{Units}
% \begin{itemize}
% \item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
% \item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
% \item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
% \item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
% \end{itemize}

% \subsection{Equations}
% Number equations consecutively. To make your 
% equations more compact, you may use the solidus (~/~), the exp function, or 
% appropriate exponents. Italicize Roman symbols for quantities and variables, 
% but not Greek symbols. Use a long dash rather than a hyphen for a minus 
% sign. Punctuate equations with commas or periods when they are part of a 
% sentence, as in:
% \begin{equation}
% a+b=\gamma\label{eq}
% \end{equation}

% Be sure that the 
% symbols in your equation have been defined before or immediately following 
% the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
% the beginning of a sentence: ``Equation \eqref{eq} is . . .''

% \subsection{\LaTeX-Specific Advice}

% Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
% of ``hard'' references (e.g., \verb|(1)|). That will make it possible
% to combine sections, add equations, or change the order of figures or
% citations without having to go through the file line by line.

% Please don't use the \verb|{eqnarray}| equation environment. Use
% \verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
% environment leaves unsightly spaces around relation symbols.

% Please note that the \verb|{subequations}| environment in {\LaTeX}
% will increment the main equation counter even when there are no
% equation numbers displayed. If you forget that, you might write an
% article in which the equation numbers skip from (17) to (20), causing
% the copy editors to wonder if you've discovered a new method of
% counting.

% {\BibTeX} does not work by magic. It doesn't get the bibliographic
% data from thin air but from .bib files. If you use {\BibTeX} to produce a
% bibliography you must send the .bib files.

% {\LaTeX} can't read your mind. If you assign the same label to a
% subsubsection and a table, you might find that Table I has been cross
% referenced as Table IV-B3.

% {\LaTeX} does not have precognitive abilities. If you put a
% \verb|\label| command before the command that updates the counter it's
% supposed to be using, the label will pick up the last counter to be
% cross referenced instead. In particular, a \verb|\label| command
% should not go before the caption of a figure or a table.

% Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
% will not stop equation numbers inside \verb|{array}| (there won't be
% any anyway) and it might stop a wanted equation number in the
% surrounding equation.

% \subsection{Some Common Mistakes}\label{SCM}
% \begin{itemize}
% \item The word ``data'' is plural, not singular.
% \item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
% \item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
% \item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
% \item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
% \item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
% \item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
% \item Do not confuse ``imply'' and ``infer''.
% \item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
% \item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
% \item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
% \end{itemize}
% An excellent style manual for science writers is \cite{b7}.

% \subsection{Authors and Affiliations}
% \textbf{The class file is designed for, but not limited to, six authors.} A 
% minimum of one author is required for all conference articles. Author names 
% should be listed starting from left to right and then moving down to the 
% next line. This is the author sequence that will be used in future citations 
% and by indexing services. Names should not be listed in columns nor group by 
% affiliation. Please keep your affiliations as succinct as possible (for 
% example, do not differentiate among departments of the same organization).

% \subsection{Identify the Headings}
% Headings, or heads, are organizational devices that guide the reader through 
% your paper. There are two types: component heads and text heads.

% Component heads identify the different components of your paper and are not 
% topically subordinate to each other. Examples include Acknowledgments and 
% References and, for these, the correct style to use is ``Heading 5''. Use 
% ``figure caption'' for your Figure captions, and ``table head'' for your 
% table title. Run-in heads, such as ``Abstract'', will require you to apply a 
% style (in this case, italic) in addition to the style provided by the drop 
% down menu to differentiate the head from the text.

% Text heads organize the topics on a relational, hierarchical basis. For 
% example, the paper title is the primary text head because all subsequent 
% material relates and elaborates on this one topic. If there are two or more 
% sub-topics, the next level head (uppercase Roman numerals) should be used 
% and, conversely, if there are not at least two sub-topics, then no subheads 
% should be introduced.

% \subsection{Figures and Tables}
% \paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
% bottom of columns. Avoid placing them in the middle of columns. Large 
% figures and tables may span across both columns. Figure captions should be 
% below the figures; table heads should appear above the tables. Insert 
% figures and tables after they are cited in the text. Use the abbreviation 
% ``Fig.~\ref{fig}'', even at the beginning of a sentence.

% \begin{table}[htbp]
% \caption{Table Type Styles}
% \begin{center}
% \begin{tabular}{|c|c|c|c|}
% \hline
% \textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
% \cline{2-4} 
% \textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
% \hline
% copy& More table copy$^{\mathrm{a}}$& &  \\
% \hline
% \multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
% \end{tabular}
% \label{tab1}
% \end{center}
% \end{table}

% \begin{figure}[htbp]
% \centerline{\includegraphics{fig1.png}}
% \caption{Example of a figure caption.}
% \label{fig}
% \end{figure}

% Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
% rather than symbols or abbreviations when writing Figure axis labels to 
% avoid confusing the reader. As an example, write the quantity 
% ``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
% units in the label, present them within parentheses. Do not label axes only 
% with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
% \{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
% quantities and units. For example, write ``Temperature (K)'', not 
% ``Temperature/K''.

% \section*{Acknowledgment}

% The preferred spelling of the word ``acknowledgment'' in America is without 
% an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
% G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
% acknowledgments in the unnumbered footnote on the first page.

% \section*{References}

% Please number citations consecutively within brackets \cite{b1}. The 
% sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
% number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
% the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

% Number footnotes separately in superscripts. Place the actual footnote at 
% the bottom of the column in which it was cited. Do not put footnotes in the 
% abstract or reference list. Use letters for table footnotes.

% Unless there are six authors or more give all authors' names; do not use 
% ``et al.''. Papers that have not been published, even if they have been 
% submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
% that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
% Capitalize only the first word in a paper title, except for proper nouns and 
% element symbols.

% For papers published in translation journals, please give the English 
% citation first, followed by the original foreign-language citation \cite{b6}.

\bibliographystyle{ieeetr}
\bibliography{references}

% \begin{thebibliography}{00}
% \bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
% \bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
% \bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
% \bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
% \bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
% \bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
% \bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
% \end{thebibliography}
% \vspace{12pt}
% \color{red}
% IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}
